### 2023-10-26 Scripts/paper.Rmd
paper Obra Transparente

---
title: "Unlocking Accountability: A Mixed-Methods Analysis of Bottom-Up Approaches in Brazilian Public Policy"
date: "2023-10-26"
output: pdf_document
author:
- name: Manoel Galdino
  affiliation: Universidade de São Paulo
abstract: "This paper examines the role of accountability in democratic systems, focusing on its impact on public service delivery. Employing mixed methods, we differentiate between information-driven interventions and the mobilization and monitoring efforts of organized Civil Society Organizations (CSOs). We argue that well-organized CSOs, deeply embedded in society and politics, can drive significant policy change. The study evaluates the effectiveness of the Obra Transparente project by Transparência Brasil, engaging 21 local CSOs in South and Southeast Brazil. In contrast to information-centered approaches, this project establishes a network of local CSOs, providing technical support and training for monitoring public school and nursery construction projects. Our findings emphasize the importance of sustained, coordinated efforts by organized civil society. These efforts, involving direct engagement with municipal officials, persistent follow-ups, and on-site visits, lead to more substantial outcomes. This research contributes to understanding how organized civil society mobilization can achieve bottom-up accountability, a crucial aspect of democratic governance. However, contextual variations may limit the effectiveness of CSO interventions."
keywords: "Accountability, Brazil, mixed methods, state capacity, public policy"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r package loads, message=F, echo=FALSE}
library(data.table)
library(here)
library(janitor)
library(lubridate)
library(readxl)
library(tidyverse)
library(gt)
library(ipeadatar)
library(MatchIt)
library(marginaleffects)

```

```{r loading construction data,  message=FALSE, echo=FALSE}

lista_cidades_ot <- c("Araucária", "Caçador", "Campo Mourão", "Cascavel", "Chapecó",
                      "Foz do Iguaçu", "Goioerê", "Gravataí", "Guarapuava", "Imbituba", "Lajeado",
                      "Limeira", "Palhoça", "Paranaguá", "Pelotas", "Ponta Grossa", "Santa Maria",
                      "São Francisco do Sul", "São José dos Campos", "Taubaté", "Uberlândia")

df_cidades_ot <- data.frame(municipio = lista_cidades_ot, indicator_ot = 1)

load(here("obra_transparente", "Dados", "obras_inicio_projeto.Rdata"))
load(here("obra_transparente", "Dados", "obras_fim_seg_fase.Rdata"))

# load(here("Dados", "obras_inicio_projeto.Rdata"))
# load(here("Dados", "obras_fim_seg_fase.Rdata"))

simec23 <- fread(here("obra_transparente", "Dados", "simec 25-10-23 - simec.csv"), encoding = "UTF-8")
# simec23 <- fread(here("Dados", "simec 25-10-23 - simec.csv"), encoding = "UTF-8")

load(here("obra_transparente", "Dados", "obras_fim_seg_fase.Rdata"))
```

```{r loading-processing ipea data,  message=FALSE, echo=FALSE, cache=TRUE}
aux_muni <- geobr::lookup_muni(code_muni = "all") %>%
  dplyr::select(-c(name_state, name_intermediate))

ipea_idhm <- ipeadatar::ipeadata("ADH_IDHM") %>%
  dplyr::filter(date > "2001-01-1" & as.character(uname) == "Municipality") %>%
  rename(idhm = value)

ipea_pea18 <- ipeadatar::ipeadata("ADH_PEA18M")  %>%
  dplyr::filter(date > "2001-01-1" & as.character(uname) == "Municipality") %>%
  rename(pea18 = value)

ipea_ext_pobres <- ipeadatar::ipeadata("ADH_PIND")  %>%
  dplyr::filter(date > "2001-01-1" & as.character(uname) == "Municipality") %>%
  rename(ext_pobres = value)

ipea_ext_pobres_neg <- ipeadatar::ipeadata("ADH_PIND_NEG")  %>%
  dplyr::filter(date > "2001-01-1" & as.character(uname) == "Municipality") %>%
  rename(ext_pobres_negros = value)

ipea_rpc <- ipeadatar::ipeadata("ADH_RDPC")  %>%
  dplyr::filter(date > "2001-01-1" & as.character(uname) == "Municipality") %>%
  rename(rpc = value)

ipea_rpc_mulheres <- ipeadatar::ipeadata("ADH_RDPC_MUL")  %>%
  dplyr::filter(date > "2001-01-1" & as.character(uname) == "Municipality") %>%
  rename(rpc_mulheres = value)

ipea_rpc_negros <- ipeadatar::ipeadata("ADH_RDPC_NEG")  %>%
  dplyr::filter(date > "2001-01-1" & as.character(uname) == "Municipality") %>%
  rename(rpc_negros = value)

ipea_ext_prop_pobres <- ipeadatar::ipeadata("ADH_PMPOB")  %>%
  dplyr::filter(date > "2001-01-1" & as.character(uname) == "Municipality") %>%
  rename(ext_prop_pobres = value)

ipea_10p_ricos_desigualdade <- ipeadatar::ipeadata("ADH_PREN10RICOS")  %>%
  dplyr::filter(date > "2001-01-1" & as.character(uname) == "Municipality") %>%
  rename(p10_ricos_desigualdade = value)

ipea_freq_escola_15_17 <- ipeadatar::ipeadata("ADH_T_FREQ15A17")  %>%
  dplyr::filter(date > "2001-01-1" & as.character(uname) == "Municipality") %>%
  rename(freq_escola_15_1 = value)

ipea_analfabetismo <- ipeadatar::ipeadata("ADH_T_ANALF15M")  %>%
  dplyr::filter(date > "2001-01-1" & as.character(uname) == "Municipality") %>%
  rename(analfabetismo = value)

pop2010 <- ribge::habitantes2010 %>%
  mutate(tcode = as.integer(paste0(codigo_uf, codigo_munic)))

ipea_final <- ipea_idhm %>%
  inner_join(aux_muni, by = join_by(tcode == code_muni)) %>%
  inner_join(ipea_pea18, by = "tcode") %>%
  inner_join(ipea_ext_pobres, by = "tcode") %>%
  inner_join(ipea_rpc, by = "tcode") %>%
  inner_join(ipea_ext_prop_pobres, by = "tcode") %>%
  inner_join(ipea_10p_ricos_desigualdade, by = "tcode") %>%
  inner_join(ipea_freq_escola_15_17, by = "tcode") %>%
  inner_join(ipea_analfabetismo, by = "tcode") %>%
  inner_join(pop2010, by = "tcode") %>%
  dplyr::select(-contains("date")) %>%
  dplyr::select(-contains("uname")) %>%
  dplyr::select(-starts_with("code"))
```

```{r processing data, echo=FALSE,  message=FALSE}

obras_inicio_projeto_ot <- obras_inicio_projeto %>%
  left_join(df_cidades_ot, by="municipio")

obras_inicio_projeto_ot <- obras_inicio_projeto_ot %>%
  mutate(concluida = grepl("Concluída", situacao))

antes_projeto <- obras_inicio_projeto_ot %>%
  group_by(indicator_ot, concluida) %>%
  summarise(contagem = n()) %>%
  mutate(indicator_ot = ifelse(is.na(indicator_ot), 0, indicator_ot),
         total = sum(contagem),
         perc = round(contagem/total, 2))

antes_projeto <- antes_projeto %>%
  dplyr::filter(concluida == TRUE) %>%
  dplyr::select(-c(concluida, contagem, total)) %>%
  ungroup()

obras_fim_seg_fase <- obras_fim_seg_fase %>%
  mutate(concluida = as.numeric(grepl("Concluída", situacao))) %>%
  left_join(df_cidades_ot, by="municipio") %>%
  mutate(indicator_ot = ifelse(is.na(indicator_ot), 0, indicator_ot))

depois_projeto <- obras_fim_seg_fase %>%
  group_by(indicator_ot, concluida) %>%
  summarise(contagem = n()) %>%
  mutate(total = sum(contagem),
         perc = round(contagem/total, 2))

depois_projeto <- depois_projeto %>%
  dplyr::filter(concluida == TRUE) %>%
  dplyr::select(-c(concluida, contagem, total)) %>%
  ungroup()

```

## Introduction

Accountability is a vital component of democratic systems to ensure the efficient delivery of public services (Besley and Ghatak, 2003; Cameron, 2004;  O'Donnell, 1998). Traditionally defined as the process of holding authorities responsible for their actions (Finer, 1941; Mulgan, 2000; O'Loughlin, 1990), the literature has evolved to encompass a broader range of mechanisms for overseeing politicians and the bureaucracy.. While some authors focused on the study of formal institutions (O’Donnel, 2003, Kenney 2003) in what is known as horizontal accountability, other have analyzed responsiveness of politicians to voters (Relly, 2012) the media and civil society organizations at large (Fox e Brown, 1998; Paul, 2002); in what is known as vertical accountability.

Recent studies have highlighted the role of "bottom-up accountability" (also known as social accountability, Fox, 2015), in which citizens receive information about public policies and use it for social control. The pioneering study 'Power to the People' (Bjorkman and Svensson, 2009), which demonstrated the impact of local community engagement in monitoring the provision of health services, inspired subsequent literature that tested similar interventions in different contexts.

The mechanism would works like this: Constituents have firsthand information about the outcomes of local policies, giving citizens incentives to combat corruption that directly affects them. Since policymakers are sensitive to social feedback from their own communities (Serra, 2011: 570), bottom-up accountability could influence local public policies

However, a series of recent studies have raised doubts about the effectiveness of "bottom-up accountability" strategies based on interventions aimed at increasing the monitoring capacity of ordinary citizens regarding public policies (Freire, Mignozzetti & Galdino, 2020; Raffler, Posner & Parkinson, 2019, Fox, 2015).

Most of the interventions are tactical, in the sense that they involve providing information to non-organized citizens through technological means, such as sending SMS messages or delivering information via mobile apps. One key advantage of such interventions is that, if successful, they could rapidly reach thousands of people at a low cost, potentially having a significant impact when scaled to an entire country or even multiple countries.

The disappointing results have cast doubts on the effectiveness of the bottom-up accountability strategy for improving the delivery of public services, reducing corruption, and enhancing government efficiency. Some authors (Fox, 2015; Ankamah, 2019) have suggested that social accountability without "teeth," defined as the government's capacity to respond to citizens' voices, has limited impact.

While it has been consistently shown that tactical interventions have, at best, a small, limited impact, it doesn't mean that voice without "teeth" is an ineffective strategy. The argument in this study is that not all types of interventions that promote citizen's voices are the same.

We argue that we need to differentiate between information-led tactical interventions and active mobilization and monitoring by Civil Society Organizations (CSOs). By their very nature, established CSOs are embedded in society and politics and can have a substantial impact on policy change (Gong & Xiao, 2017. Joshi & Houtzager, 2012).

The paper argues that a missing feature in most of the literature is that these interventions should target CSOs instead of individual citizens, and ensure that the intervention enhances the ability of the CSOs to overcome their collective action problem  (Mattoni & Odilla, 2021; Odilla, 2023).

The present paper provides evidence supporting this argument. We reassess the evidence provided by Freire, Mignozzetti & Galdino (2020), considering a different intervention than the one they evaluated. They provided experimental evidence that a mobile app (Tá de Pé) made available to citizens did not improve the delivery of school and nursery construction works. Here, we assess the efficacy of a sister project, called "Obra Transparente," also developed by the Brazilian NGO Transparência Brasil. This project targeted 21 local Civil Society Organizations in 21 municipalities in the South and Southeast regions of Brazil, with the aim of improving access to education by addressing mismanagement and delays in the construction of public schools and nurseries. Both projects were developed in parallel, with similar goals but achieved strikingly different results.

The argument in the present study is that not all types of interventions that promote citizens' voice are the same. We argue that we need to differentiate between information-led tactical interventions and active mobilization and monitoring by Civil Society Organizations. By their very nature, established CSOs are embedded in society and politics and, as such, can have teeth of their own (Gong & Xiao, 2017. Joshi & Houtzager, 2012).  It may be only that we need mobilization by organized civil society, in a structured way, for civil society voices to be heard with “teeth”. Some studies have suggested that a key feature of successful change in public policies is the pressure of collectively organized agents (Mattoni & Odilla, 2021; Odilla, 2023). Collective action is a hard problem to be overcome and creating CSOs is one way to achieve this. We argue in this paper that a missing features of the tactical interventions assessed in most of the literature is that they should target CSOs instead of individual citizens, and make sure that the intervention increases the ability of the CSOs to attract and overcome their collective action problem.

The "Obra Transparente" project consisted of developing a network of local CSOs to share experiences and information on monitoring the construction works, providing a technical support system for monitoring the process of constructing public schools and nurseries, and training on monitoring biddings, contracts, and constructions of public schools and nurseries.

Our findings emphasize that it is the sustained and concerted efforts of organized civil society, such as repeated meetings with municipal officials, persistent follow-ups, and on-site visits, that lead to more significant outcomes, in contrast to interventions providing information and generating sporadic citizen actions.

## The project Obra Transparente

The project was initiated in May 2017 by Transparência Brasil (TB) to address delays in school and nursery construction projects funded by the federal government and carried out by municipal governments. TB partnered with Observatório Social do Brasil, an NGO coordinating a network of local (municipality-based) NGOs, to develop and disseminate a standardized methodology for local government oversight. The Obra Transparente project concluded on June 30, 2019.

During the project, TB monitored construction plans, resource allocation, procurement processes, and work execution. They also tracked the monitoring and accountability procedures conducted by government bodies to ensure adherence to technical and legal guidelines.

Transparência Brasil collaborated with the Controladoria Geral da União, a federal government agency responsible for overseeing federal public spending, to develop training materials and provide courses to a network of local CSOs. Courses reached 270 participants, with a mix of online and in-person modules over several weeks along the duration of the project. These modules covered topics related to public bidding, construction monitoring, and contracting procedures.

## Research Design and Methods

We employ an integrated inference approach (Humphreys & Jacobs, 2023) to analyze qualitative data within the framework of causal queries. As this approach is relatively innovative within qualitative research, we'll provide a comprehensive explanation.

The methodology outlined by Humphreys & Jacobs (2023) mandates the creation of a causal model encoded in Directed Acyclic Graphs (DAGs), a framework developed by Pearl (2009). Bayesian inference, recently promoted in qualitative data analysis (Fairfield & Charman, 2022), serves as the foundation for deriving quantitative estimates for causal queries constructed using the proposed DAG. 
In our current study, we investigate the impact of Civil Society Organization (CSO) monitoring on two aspects: the completion of construction works and the rectification of issues and irregularities found in construction facilities. Formally, the first research question relates to a causal relationship between monitoring (M) and completion (C), indicated by the DAG (M -> C). The second research query delves into whether monitoring (M) causes the fixing of issues (F), or the (DAG M -> F). To accommodate the qualitative nature of our variables, we treat them as binary.

Within this approach, a given DAG allows us to pose causal queries, which can yield estimands like the average treatment effect (ATE) or types, which we explain below. Types are the focal estimands in our study.

This approach hinges on the notion that each case can belong to a specific type, denoting different causal relationships. In our current investigation, let's focus on the (M -> C) DAG. To clarify what a type is, we'll employ the Potential Outcomes (PO) notation (Rubin, 2005; Imbens & Rubin, 2015). Within the PO framework, every case has two potential outcomes: one when the treatment (in this case, CSO monitoring, M) is absent and another when the treatment is present. In simplified notation, if a city only completes construction works in the absence of monitoring, we express this in PO notation as C(1) = 0. If there is no monitoring (M = 0) and no completion, then we write C(0) = 0. Conversely, if there is monitoring (M = 1) and completion, we write C(1) = 1, and C(0) = 1 if there is completion without monitoring.

We can categorize a city into one of four types based on what happens when they do or do not receive the treatment (monitoring):
Adverse (type "a"): A city that completes construction only if it doesn't receive the treatment (monitoring).
Beneficial (type "b"): A city that completes construction only if there is monitoring.
Chronic (type "c"): Cities that never complete construction, regardless of monitoring.
Destined (type "d"): Cities that always complete construction, regardless of monitoring.
The PO notation is instrumental here, as we can rewrite the types based on the following notation: Type "a" is one in which the potential outcome is 0 if M = 1 and 1 if M = 0. Therefore, we express it as $\theta_{10}$, where the first subscript denotes the outcome when the treatment is 0, and the second denotes the outcome when the treatment is 1. We employ analogous notation for all other types: $b = \theta_{01}$, $c = \theta_{00}$, and $d = \theta_{11}$.

When analyzing a case study of what happened in a given municipality, we can use the data to answer, for example, the following causal query: what is the probability that the city if type “b”, i.e, benefits from the monitoring and would have not completed the construction work if not for the monitoring of the local CSO?

The advantage of this approach is that all assumptions and restrictions imposed to identify the parameters of interest are transparent. It also allows the user to update posterior probabilities based on qualitative data. One reason for this is that with Bayesian inference, we do not need to rely on asymptotic theory to make inferences. Thus, there is no need for a large-n study. Formally speaking, one can make causal queries without any data, based only on prior probabilities for the parameters. Obviously the answer to such causal queries will be vague enough to be almost useless. But the point is that, once you have a prior and a causal model, encoded in a DAG, you can answer causal queries. As one collects data (any data, be it qualitative or quantitative), one can make assumptions about the nature of the data (such as the Data Generating Process), and then update the model and provide new answers to the causal queries, which hopefully will be informative enough to be useful for the task at hand. And even when the model or hypothesis is not completely identified, it can be partially identified (Manski, 2003), which is still a useful answer to causal queries.

## Data

The evidence gathered is primarily based on documented reports collected by Transparência Brasil over the course of the project. We also use evidence collected on semi-structured interviews and an online survey with representatives of the 21 CSOs conducted by an independent evaluator of the project. We also use administrative data about construction works data by municipalities and socio-demographic data on municipalities. The questions asked in the survey as well the aggregate answered are presented in annex A.

## Case Studies

### Delivery of the construction works

In our first case study, we highlight an impressive achievement in ensuring the completion of construction work. In Taubaté, four construction projects were underway, which the local OSB began monitoring as part of Obra Transparente. By the project's conclusion, their efforts played a crucial role in facilitating the successful delivery of these schools and nurseries to the city, ensuring they were ready for use in the field of education

To put in perspective what was accomplished regarding the completion of all four projects, by the end of the project, of all 135 construction works planned for all 21 municipalities, only 25 were effectively delivered, a 18.5% delivery rate. In Taubaté,  before the monitoring by the local CSO, the delivery rate was zero. After that, the delivery rate was 100% and one of the construction work was a previously paralyzed construction. According to a report by Transparência Brasil (Coelho, Galdino & Sakai., 2021), out of 771 stalled construction projects that were eventually completed, over 50% of them took more than two years to be delivered and 25% took three years or more. As we can see, the odds were against finishing the construction works.

The local CSO monitoring the construction work in Taubaté did one of  the best jobs among all 21 municipalities covered in the project. In fact, it was mostly the work of a single volunteer with support from the local OSB and Transparência Brazil throughout the project. She monitored four ongoing construction works on a periodic basis, she was very knowledgeable and insistent in demanding response from contractors and the local government. To give a single example of the quality of the social monitoring going on, in an email sent on 17th January of 2018 to the local government, the local OSB volunteer wrote: “Fazendinha Daycare: a. construction log verified. There have been a few more construction workers on the site since December 15, 2017, but not enough, especially considering the extensive amount of work to be completed by the new delivery date in April 2018. b. (...). c. Lack of roof sealing, leading to water entering the classrooms (a situation that already existed on November 14, 2017)...” . She was by far the most knowledgeable and zealous volunteer of the whole project.

All of the construction works were effectively finished and delivered by the end of the project, although overdue. One of them, a resumption of a then halted construction work, was delivered 2 months overdue. The remaining three were further delayed, but no amendments were made on prices, only deadlines.

From a causal perspective, we are interested in what is called case-level causal attribution (Humphreys & Jacobs, 2023), i.e, did the monitoring cause the delivery of the construction works?In other words, we are conditioning on the fact that M = 1 and C = 1, which constrains the possible types for Taubaté to be $\theta^C_{1,1}$ ou $\theta^C_{0,1}$. Assuming a simple model in which CSO monitoring causes the completion of works (M -> C), and with the eight within-case instances, we do the causal query. Our stimand of interest is the probability that Taubaté is a type $\theta^D_{10}$.

Assuming uniform priors, the probability that  Taubaté is a type $\theta^D_{10}$, i.e, it is a city in which the treatment has a positive effect is 65%, with 95% credibility interval around [23%, 95%]. As we can see, a wide interval, due to the low sample size, and yet, a positive effect nonetheless with 95% of certainty.

What are the assumptions behind such a result? The main one is that we modeled the monitoring (the treatment) as-if random, which is obviously not true. The mere passage of time causes an increased probability of delivery of a construction work. We can also imagine other possible confounds. The way to model it in a DAG is to add an arrow from M to C and vice-versa (M <-> C). Now, the estimand of interest depends on the probability of the treatment (monitoring) causing also the outcome (Average Treatment Effect, ATE). We will not detail the derivation of the new stimand here (you can consult annex B), but the idea is similar to before: we are interested in the type of city in which there is a causal effect of the monitoring on the completion of a construction works of school and/or nurseries. The mean probability of Taubaté being of this type, assuming the model is true is 43%, with 95% credibility intervals around [9%, 80%]. The interval is wider because we added the uncertainty of confounding. Nonetheless, it is unlikely that the positive effect found in the observational data is driven only due to the confounding variables.

### Preventing problems before projects started

The local OSB monitoring in Auraucária story is one when oversight arrives at the right moment to prevent a costly government procurement.

In 2017, the Brazilian municipality of Araucária conducted bidding processes seeking to hire companies to build three nurseries. The project sent technical experts to the 3 planned construction sites, together with volunteers from the local Observatório, to check whether plans were consistent with the physical conditions observed on site. The experts’ assessment was that high-cost contention walls included in the construction plans were unnecessary or could be replaced by low-cost solutions through adjustments. Originally, the contention walls would cost R$ 1,577,338.57 (US$ 419,504.9, at the nominal exchange rate in 2019). The analysis was first directed to the local administration, suggesting changes to the construction plans, which were rejected. The bidding processes went on as initially planned. Subsequently, the experts’ findings were submitted to the Brazilian Supreme Audit Institution, Tribunal de Contas da União (TCU), by Transparência Brasil and Observatório Social do Brazil (see annex 1). TCU recommended that the bidding process should be redone, and construction plans were to be redesigned, with more cost-effective solutions for the contention walls. In the new bidding process, their cost plummeted to R$ 416,883.17 (US$ 110,873.2), a reduction of US$ 308,631.7 — 74% less. To give a sense of the impact on the city budget, the amount saved on these three constructions alone represents about 3% of all capital investments of Araucária in 2018. In short, in a single municipality, the project resulted in savings higher than the cost of the entire project funded by the grantee UNDEF (US$ 220,000.00).

### Fixing defects in ongoing projects

Another impact of the project was the correction of the irregularities and construction failures, improving the quality of the delivered construction work. During their monitoring activities, the OSBs found defects and issues, promptly reported them to municipality administration, which then acted in order to fix them. The project partners ended up substituting government inspectors and making up for their shortcomings in ensuring contract compliance through supervision. This was the case in both the four constructions in Taubaté (SP) and three that were going on in Foz do Iguaçu (SC). In both cases volunteers performed monitoring activities very frequently, which allowed for a thorough investigation and revealed a series of defects in projects and execution.

### Fixing defects in finished projects

In Palhoça (SC), is an example when oversight came too late. One of the daycares completed before the monitoring period started was delivered with a wall of perforated elements without proper grouting, with pieces that were already coming loose. The daycare was put into operation without addressing the issue, which led the staff to isolate the area to minimize the risk of injuries to the children. In other words, part of the building cannot be used due to a failure for which a solution should have already been demanded from the responsible company.

In Goioerê, the story had a more happy ending. Volunteers visited an already delivered school building and noticed improperly installed windows, rendering them non-functional. A series of finishes were also lacking, such as grab bars and handles in accessible restrooms for persons with disabilities or reduced mobility. These shortcomings compromised adequate use of the building and exposed its users - mainly children - to potentially dangerous situations. These flaws were mostly corrected by the contractor after being reported by the local Observatório.

## Quantitative observational evidence

We have already observed qualitative evidence indicating that local OSB monitoring played a crucial role in expediting the completion of construction projects. Now, we present quantitative evidence regarding the impact of this monitoring on delivery rates.

To do so, we collected data on school and nursery construction projects across the entire country, encompassing over two thousand municipalities and more than 14 thousand construction projects, spanning all phases from planning to execution and completion. The table below provides descriptive statistics for these construction projects.

When comparing "treated" and "untreated" units, there is difference between the groups, as show below by the percentage of construction works within both groups before the project started.

```{r tables, echo=FALSE, message=FALSE, results='asis'}
antes_projeto %>%
  gt() %>%
  tab_header(
    title = "Percentage of finished fonstruction works before the project",
    subtitle = "Situation in August 2017") %>%
  cols_label(
    indicator_ot = "Obra Transparente Indicator",
    perc = "Percentage of finished constructions"
  )
```

Our primary objective is to compare the project's effects on the rate of delivery. To estimate the Average Treatment Effect on the Treated (ATT), we employed a matching strategy (Ho et al. (2007; Rubin, 1973). We also applied the same procedure to pre-project data to ensure that there were no substantial differences between the treated and control groups. The table below presents estimates for the causal effect on the treated units regarding the change in completion rates before and after the project.

```{r balancing process,  message=FALSE, echo=FALSE}

aux_muni1 <- aux_muni %>%
  mutate(name_muni1 = tolower(iconv(name_muni, "UTF-8",  "ASCII//TRANSLIT")))

df_balancing_aux <- obras_inicio_projeto_ot %>%
  mutate(municipio1 = tolower(iconv(municipio, "UTF-8",  "ASCII//TRANSLIT"))) %>%
  inner_join(aux_muni1, by = join_by(municipio1  == name_muni1, uf == abbrev_state)) %>%
  inner_join(ipea_final, by = join_by(code_muni == tcode)) %>%
  mutate(indicator_ot = ifelse(is.na(indicator_ot), 0, indicator_ot),
         perc_pea18 =pea18/populacao,
         log_pop = log(populacao),
         log_renda = log(rpc*populacao),
         log_rpc = log(rpc))
df_balancing <- df_balancing_aux %>%
  distinct(code_muni, .keep_all = TRUE)

## pós projeto
df_balancing_aux_post <- obras_inicio_projeto_ot %>%
  mutate(municipio1 = tolower(iconv(municipio, "UTF-8",  "ASCII//TRANSLIT"))) %>%
  inner_join(aux_muni1, by = join_by(municipio1  == name_muni1, uf == abbrev_state)) %>%
  inner_join(ipea_final, by = join_by(code_muni == tcode)) %>%
  mutate(indicator_ot = ifelse(is.na(indicator_ot), 0, indicator_ot),
         perc_pea18 =pea18/populacao,
         log_pop = log(populacao),
         log_renda = log(rpc*populacao),
         log_rpc = log(rpc))
```

```{r balancing check, message=FALSE, echo=FALSE}
m.out <- matchit(indicator_ot ~ perc_pea18  + ext_pobres  + log_rpc + 
                  p10_ricos_desigualdade + freq_escola_15_1 + analfabetismo +
                  log_renda + log_pop, data = df_balancing,
                 replace = TRUE, ratio = 3)

# summary(m.out)
# summary(m.out, un=FALSE)
# plot(m.out, type = "jitter", interactive = FALSE)
# 
# m.sum <- summary(m.out)
# 
# plot(m.sum, var.order = "unmatched")

# #eQQ plot
# plot(m.out, type = "qq", which.xs = ~ log_rpc + ext_pobres + p10_ricos_desigualdade)
# plot(m.out, type = "qq", which.xs = ~ perc_pea18 + log_pop + + freq_escola_15_1)
# 
# #eCDF plot - black line is treated, gray is control
# plot(m.out, type = "ecdf", which.xs = ~ log_rpc + ext_pobres + p10_ricos_desigualdade)
# plot(m.out, type = "ecdf", which.xs = ~  perc_pea18 + log_pop + + freq_escola_15_1)
# 
# #density plot - black line is treated, gray is control
# plot(m.out, type = "density", which.xs = ~ log_rpc + ext_pobres + p10_ricos_desigualdade)
# plot(m.out, type = "density", which.xs = ~  perc_pea18 + log_pop + + freq_escola_15_1)

# Full matching on a probit PS
m.out2 <- matchit(indicator_ot ~ perc_pea18  + ext_pobres  + log_rpc + 
                  p10_ricos_desigualdade + freq_escola_15_1 + analfabetismo +
                  log_renda + log_pop, data = df_balancing,
                 method = "full", distance = "glm", link = "probit")
# summary(m.out2, un = FALSE)
# m.sum2 <- summary(m.out2)
# plot(m.sum2, var.order = "unmatched")

## regression with matching

m.data <- match.data(m.out2) %>%
  dplyr::select(weights, code_muni, subclass ) %>%
  inner_join(df_balancing_aux, by = "code_muni") %>%
  mutate(indicator_ot = as.factor(indicator_ot))

fit <- lm(concluida ~ indicator_ot + perc_pea18  + ext_pobres  + log_rpc + 
                  p10_ricos_desigualdade + freq_escola_15_1 + analfabetismo +
                  log_renda + log_pop, data = m.data, weights = weights)

# avg_comparisons(fit,
#                 variables = "indicator_ot",
#                 vcov = ~ subclass,
#                 newdata = subset(m.data, indicator_ot == 1),
#                 wts = "weights") %>%
#   gt()
#

matching_data <- match.data(m.out2) %>%
  dplyr::select(weights, code_muni, subclass)

pre_dados <- df_balancing_aux %>%
  dplyr::select(id, concluida) %>%
  rename(concluida_pre = concluida) %>%
  mutate(id = as.character(id))

data_pos <- obras_fim_seg_fase %>%
  mutate(municipio1 = tolower(iconv(municipio, "UTF-8",  "ASCII//TRANSLIT"))) %>%
  inner_join(aux_muni1, by = join_by(municipio1  == name_muni1, uf == abbrev_state)) %>%
  inner_join(ipea_final, by = join_by(code_muni == tcode)) %>%
  mutate(indicator_ot = ifelse(is.na(indicator_ot), 0, indicator_ot),
         perc_pea18 =pea18/populacao,
         log_pop = log(populacao),
         log_renda = log(rpc*populacao),
         log_rpc = log(rpc)) %>%
  inner_join(matching_data, by = "code_muni") %>%
  inner_join(pre_dados, by = "id") %>%
  dplyr::filter(concluida_pre != concluida) %>%
  mutate(concluida = as.numeric(concluida))

fit1 <- lm(concluida ~ indicator_ot + perc_pea18  + ext_pobres  + log_rpc + 
                  p10_ricos_desigualdade + freq_escola_15_1 + analfabetismo +
                  log_renda + log_pop, data = data_pos, weights = weights)

```

```{r tables 2, echo=FALSE,  message=FALSE, results='asis'}
avg_comparisons(fit1,
                variables = "indicator_ot",
                vcov = ~ subclass,
                newdata = subset(data_pos, indicator_ot == 1),
                wts = "weights") %>%
  gt()
```

## Discussion of Results

One of the reasons identified for some of the problems with the construction works is lack of qualified personnel from the government to monitor the contractor work. As a result, the local government does not properly oversight the work of contractors. And this is a task that requires technical expertise and is time consuming, involving going multiple times to the construction site, comparing the construction log with the schedule to assess if there is potential delay and what is specified in the contract, to assess if the materials used are correct, if everything demanded is being done etc.

The fact that an intervention like Tá de Pé (Freite et. al. ,2020), which provided information to citizens about construction work, but did not produce a meaningful impact does not mean that bottom up accountability does not have any effect. The evidence we gathered here, assessed with multiple methods, clearly shows that costly and consistent oversight by civil society can produce results that are quite impactful, be it increased rate of project completion, improved quality of the construction works or decreasing in governmental spending.

The detection of evidence of procurement fraud cases also shows local administrations are not diligent enough in conducting procurement procedures, and the local partners of TB contributed to addressing that gap as well. Moreover, as federal audit agencies lack the capacity to adequately oversee and analyze the immense volume of contracting procedures conducted at the local level, the social monitoring resulted in the identification of high-risk cases that otherwise might not have been assessed by the competent bodies.

## Concluding Remarks

Accountability, as a fundamental element in democratic systems, plays a pivotal role in ensuring the efficient provision of public services. Recent studies have brought to light the concept of "bottom-up accountability," where citizens receive information about public policies and utilize it to exert social control.

While tactical interventions aimed at providing information to citizens have shown limited impact, it would be a mistake to dismiss the potential of citizen voices in governance entirely. Our research has differentiated between information-led tactical interventions and active mobilization and monitoring by Civil Society Organizations (CSOs). We argue that organized CSOs, deeply rooted in society and politics, hold the capacity to bring about substantial policy change.

This paper provides evidence in support of this argument. By assessing the effectiveness of the "Obra Transparente" project developed by Transparência Brasil, we illustrate the significant role that organized CSOs can play in shaping government behavior and improving public service delivery. Unlike interventions solely focused on providing information, this project aimed at creating a network of local CSOs, offering technical support, and providing training on monitoring public school and nursery construction projects.

Our findings underscore the importance of sustained, concerted efforts by organized civil society, including direct engagement with municipal officials, persistent follow-ups, and on-site visits. These endeavors yield more substantial outcomes compared to interventions that merely deliver information and generate sporadic citizen actions.

In a world where accountability mechanisms continue to evolve, the role of organized civil society remains paramount. The ability to foster collective action, create informed oversight, and influence policy change is an essential aspect of accountable and effective democratic governance. The journey toward enhancing bottom-up accountability is ongoing, and our research contributes to a more comprehensive understanding of how it can be achieved through the mobilization of organized civil society.

## References

Ankamah, S. S. (2019). Why do “teeth” need “voice”? The case of anti‐corruption agencies in three Australian states. Australian Journal of Public Administration, 78(4), 481-496.

Besley T and Ghatak M (2003) Incentives, choice, and accountability
in the provision of public services. Oxford Review of Economic Policy 19(2): 235–249.

Björkman, M., & Svensson, J. (2009). Power to the people: evidence from a randomized field experiment on community-based monitoring in Uganda. The Quarterly Journal of Economics, 124(2), 735-769.

Cameron W (2004) Public accountability: Effectiveness, equity, ethics. Australian Journal of Public Administration 63(4): 59–67.

Coelho, J., Galdino, M. Sakai, J. (2021) Levantamento: Obras federais paralisadas de creches e escolas com maiores chances de serem concluídas. Available at:
https://www.transparencia.org.br/downloads/publicacoes/levantamentoobrasfederaisparalisadascrechesescolasmaioreschancesseremconcluidas.pdf. Accessed on 10-25-2023.

Fairfield, T., & Charman, A. E. (2022). Social inquiry and Bayesian inference: Rethinking qualitative research. Cambridge University Press.

Fox, J. A. (2015). Social accountability: what does the evidence really say?. World Development, 72, 346-361.

Gong, T., & Xiao, H. (2017). Socially embedded anti‐corruption governance: Evidence from Hong Kong. Public Administration and Development, 37(3), 176-190.

Ho, Daniel E., Kosuke Imai, Gary King, and Elizabeth A. Stuart. 2007. “Matching as Nonparametric Preprocessing for Reducing Model Dependence in Parametric Causal Inference.” Political Analysis 15 (3): 199–236.

Humphreys, M., & Jacobs, A. (2023). Integrated Inferences: Causal Models for Qualitative and Mixed-Method Research (Strategies for Social Inquiry). Cambridge: Cambridge University Press.

Imbens, G. W., & Rubin, D. B. (2015). Causal inference in statistics, social, and biomedical sciences. Cambridge University Press.

Joshi, A., & Houtzager, P. P. (2012). Widgets or watchdogs? Conceptual explorations in social accountability. Public Management Review, 14(2), 145-162.

Kenney, C. D. (2003). Horizontal accountability: concepts and conflicts. in Democratic Accountability in Latin America. Mainwaring, S., & Welna, C. (Eds.). OUP Oxford.

Manski, C. F. (2003). Partial identification of probability distributions (Vol. 5). New York: Springer

Mattoni, A., & Odilla, F. (2021). Digital Media, Activism, and Social Movements' Outcomes in the Policy Arena. The Case of Two Anti-Corruption Mobilizations in Brazil. Partecipazione e conflitto, 14(3), 1127-1150.

Medeiros, Vanda. (2019). POST PROJECT EVALUATION FOR THE UNITED NATIONS DEMOCRACY FUND. Independent Report submitted to UNDEF.

Mulgan R (2000) ‘Accountability’: An ever-expanding concept? Public Administration 78(3): 555–573.

Mondo, B.; Galdino, M.; Voigt, J.; Sakai, J. Oliveira, C. (2018). Obra Transparente: Monitoramento de obras de escolas e creches financiadas pelo governo federal. Report by Transparência Brazil. Available at : https://www.transparencia.org.br/downloads/publicacoes/18082018_relatorioOT%20(1).pdf

Odilla, F. (2023). Bots against corruption: Exploring the benefits and limitations of AI-based anti-corruption technology. Crime, Law and Social Change, 1-44.

O’Donnell GA (1998) Horizontal accountability in new democracies.
Journal of Democracy 9(3): 112–126.

O’donnell, G. (2003). Horizontal accountability: The legal. Democratic Accountability in Latin America, 34.

O’Loughlin MG (1990) What is bureaucratic accountability and how
can we measure it? Administration & Society 22(3): 275–302.

PAUL, Samuel. Accountability in public services: exit, voice and control. World Development 29, 7 (julho) p. 1047 – 1060. 2002.

Pearl, Judea. 2009. Causality. Cambridge university press.

Raffler, P., Posner, D. N., & Parkerson, D. (2019). The weakness of bottom-up accountability: experimental evidence from the Ugandan health sector. Los Angeles: Innovations for Poverty Action.

Relly, J. E. (2012). Examining a model of vertical accountability: A cross-national study of the influence of information access on the control of corruption. Government Information Quarterly, 29(3), 335-345.
Rubin, Donald B. 1973. “Matching to Remove Bias in Observational Studies.” Biometrics 29 (1): 159.

Rubin, D. B. (2005). Causal inference using potential outcomes: Design, modeling, decisions. Journal of the American Statistical Association, 100(469), 322-331.

Serra D (2011) Combining top-down and bottom-up accountability: Evidence from a bribery experiment. The Journal of Law, Economics, & Organization 28(3): 569–587.

Tribunal de Contas da União. (2014). Recomendações Básicas para a Contratação e Fiscalização de Obras de Edificações Públicas.

### 2023-10-26 causal_query.R
Causal query + proj

@@ -1,0 +1,346 @@
+library(data.table)
+library(tidyverse)
+library(knitr)
+library(CausalQueries)
+
+imbituba <- fread("Dados/Servidores_efetivos_imbituba.csv", skip = 14)
+glimpse(imbituba)
+
+imbituba %>%
+  summarise(num_engenheiro = sum(grepl("[Ee]ngenheiro [Cc]ivil", V3)))
+# 21
+
+
+imbituba_eng <- imbituba %>%
+  filter(grepl("[Ee]ngenheiro [Cc]ivil", V3))
+
+
+lajeado <- fread("Dados/relacaoservidores-1697891422613.csv", skip = 14, encoding = "Latin-1")
+glimpse(lajeado)
+
+lajeado %>%
+  mutate(V2 = tolower(V2)) %>%
+  summarise(num_engenheiro = sum(grepl("engenheiro civil", 2)))
+View(lajeado)
+
+# pelotas
+
+pelotas <- fread("Dados/Pelotas_servidores2018.csv", encoding = "Latin-1")
+glimpse(pelotas)
+
+pelotas_cargo <- pelotas %>%
+  filter(MES == 9) %>%
+  filter(grepl("Engenheiro Civil", CARGO)) %>%
+  group_by(CARGO) %>%
+  summarise(total = n_distinct(MATRICULA), tot = n_distinct(ID_CONTRATO_RH))
+
+pelotas %>%
+  filter(MES == 9) %>%
+  filter(grepl("Engenheiro Civil", CARGO)) %>%
+  group_by(CARGO, LOTACAO) %>%
+  summarise(total = n_distinct(MATRICULA), tot = n_distinct(ID_CONTRATO_RH))
+
+pelotas_cargo1 <- pelotas %>%
+  filter(MES == 9) %>%
+  filter(grepl("Agente Fiscal", CARGO))
+
+
+model1 <- make_model("X->Y") %>% set_restrictions(decreasing("X", "Y"))
+get_parameter_matrix(model1)
+
+model1 %>%
+  query_model("Y[X=1] - Y[X=0]", n_draws = 10000) %>%
+  kable
+
+## Taubae causal model
+options(mc.cores = parallel::detectCores())
+# modelo nulo
+model_taubate <- make_model("M -> C") %>% set_restrictions(non_decreasing("M", "C"), keep=T)
+# model_taubate1 <- make_model("M -> C; M <-> C") %>% 
[…]

### 2023-10-27 Scripts/paper.Rmd
Correção em contagem de obras do OT e repercussões

@@
 
-lista_cidades_ot <- c("Araucária", "Caçador", "Campo Mourão", "Cascavel", "Chapecó",
-                      "Foz do Iguaçu", "Goioerê", "Gravataí", "Guarapuava", "Imbituba", "Lajeado",
-                      "Limeira", "Palhoça", "Paranaguá", "Pelotas", "Ponta Grossa", "Santa Maria",
-                      "São Francisco do Sul", "São José dos Campos", "Taubaté", "Uberlândia")
-
-df_cidades_ot <- data.frame(municipio = lista_cidades_ot, indicator_ot = 1)
+# lista_cidades_ot <- c("Araucária", "Caçador", "Campo Mourão", "Cascavel", "Chapecó",
+#                       "Foz do Iguaçu", "Goioerê", "Gravataí", "Guarapuava", "Imbituba", "Lajeado",
+#                       "Limeira", "Palhoça", "Paranaguá", "Pelotas", "Ponta Grossa", "Santa Maria",
+#                       "São Francisco do Sul", "São José dos Campos", "Taubaté", "Uberlândia")
+# 
+# df_cidades_ot <- data.frame(municipio = lista_cidades_ot, indicator_ot = 1)
 
@@
 load(here("obra_transparente", "Dados", "obras_fim_seg_fase.Rdata"))
+
+df_cidades_ot <- read_excel("Dados/181114 - Situação obras_atual.xlsx", 
+                                           sheet = "SIMEC-Mai17", skip = 1) %>%
+  clean_names() %>%
+  filter(!is.na(id)) %>%
+  dplyr::select(id, municipio, uf, situacao2, levant_os_jun_17) %>%
+  mutate(indicator_ot = 1)
 ```
@@
 obras_inicio_projeto_ot <- obras_inicio_projeto %>%
-  left_join(df_cidades_ot, by="municipio")
+  left_join(df_cidades_ot, by=join_by("municipio", "uf", "id"))
 
@@
 
+aux_indicator_ot <- df_cidades_ot %>%
+  distinct(municipio, uf) %>%
+  mutate(indicator_muni_ot = 1)
+
+obras_inicio_projeto_ot <- obras_inicio_projeto_ot %>%
+  mutate(indicator_ot = ifelse(is.na(indicator_ot), 0, indicator_ot)) %>%
+  left_join(aux_indicator_ot, by = join_by("municipio", "uf")) %>%
+  mutate(indicator_muni_ot = ifelse(is.na(indicator_muni_ot), 0, indicator_muni_ot))
+
 antes_projeto <- obras_inicio_projeto_ot %>%
-  group_by(indicator_ot, concluida) %>%
+  group_by(indicator_muni_ot, concluida) %>%
   summarise(contagem = n()) %>%
-  mutate(indicator_ot = ifelse(is.na(indicator_ot), 0, indicator_ot),
-         total = sum(contagem),
+  mutate(total = sum(contagem),
          perc = round(contagem/total, 2))
@@
 obras_fim_seg_fase <- obras_fim_seg_fase %>%
-  mutate(concluida = as.numeric(grepl("Concluída", situacao))) %>%
-  left_join(df_cidades_ot, by="municipio") %>%
-  mutate(indicator_ot = ifelse(is.na(indicator_ot), 0, indicator_ot))
+  mutate(concluida = as.numeric(grepl("Concluída", situacao)),
+         id = as.numeric(id)) %>%
+  left_join(df_cidades_ot, by=join_by("municipio", "uf", "id")) %>%
+  mutate(indicator_ot = ifelse(is.na(indicator_ot), 0, indicator_ot)) %>%
+  left_join(aux_indicator_ot, by = join_by("municipio", "uf")) %>%
+  mutate(indicator_muni_ot = ifelse(is.na(indicator_muni_ot), 0, indicator_muni_ot))
 
 depois_projeto <- obras_fim_seg_fase %>%
-  group_by(indicator_ot, concluida) %>%
+  group_by(indicator_muni_ot, concluida) %>%
   summarise(contagem = n()) %>%
@@
   cols_label(
-    indicator_ot = "Obra Transparente Indicator",
-    perc = "Percentage of finished constructions"
+    indicator_muni_ot = "Participating Municipalities in Obra Transparente ",
+    perc = "Percentage of Completed Constructions"
+  ) %>%
+    fmt_percent(
+    columns = perc,
+    decimals = 0
   )
@@
          log_renda = log(rpc*populacao),
-         log_rpc = log(rpc))
-df_balancing <- df_balancing_aux %>%
-  distinct(code_muni, .keep_all = TRUE)
+         log_rpc = log(rpc),
+         tipo_do_projeto = ifelse(grepl("Bloco Estrutural" ,tipo_do_projeto),
+                                  "Projeto Tipo B ou C - Bloco Estrutural", tipo_do_projeto))
+
+df_balancing_aux %>%
+  group_by(tipo_do_projeto) %>%
+  summarise(n())
 
@@
                   p10_ricos_desigualdade + freq_escola_15_1 + analfabetismo +
-                  log_renda + log_pop, data = df_balancing,
+                  log_renda + log_pop + percentual_de_execucao + rede_de_ensino_publico + tipo_do_projeto , data = df_balancing,
                  replace = TRUE, ratio = 3)
 
-# summary(m.out)
+summary(m.out)
 # summary(m.out, un=FALSE)

### 2023-10-27 Scripts/paper.Rmd
Propensity score, first attempt

@@
 
+[Insert Table]
+
 When comparing "treated" and "untreated" units, there is difference between the groups, as show below by the percentage of construction works within both groups before the project started.
@@
 antes_projeto %>%
+  inner_join(depois_projeto, by = "indicator_muni_ot") %>%
   gt() %>%
@@
     title = "Percentage of finished fonstruction works before the project",
-    subtitle = "Situation in August 2017") %>%
+    subtitle = "Situation in August 2017 and August 2019") %>%
   cols_label(
     indicator_muni_ot = "Participating Municipalities in Obra Transparente ",
-    perc = "Percentage of Completed Constructions"
+    perc.x = "Percentage of Completed Constructions Before Project",
+    perc.y = "Percentage of Completed Constructions After Project"
   ) %>%
     fmt_percent(
-    columns = perc,
+    columns = c(perc.x, perc.y),
     decimals = 0
@@
 We also applied the same procedure to pre-project data to ensure that there were no substantial differences between the treated and control groups.
+
+We estimate all models using the following regression equation:
+
+$$
+Y_i = \alpha + \beta_1 T_i + \gamma X_i + \theta Z_i + \epsilon_i
+$$
+where $i$ indexes the experiment units.
+$Y_i$ is $1$ if a construction work is finished, and $0$ otherwise, α is the intercept, β denotes the average treatment effect on the treated (ATT), and $T_i$ is a binary treatment indicator (municipality is part or not of Obra Transparent).
+$\gamma$ is a vector of fixed effects, $X_i$ is a matrix of Brazilian states’ fixed effects, $\theta$ is a vector of controls, and $Z_i$ an array of controls for the case $i$.
+The error term is denoted by $ε_i$.
+We cluster the standard errors at the municipality level as mayors are the main target of the local OSBs work.
+We fit a Bayesian model with rstanarm (Goodrich, 2023) with default weakly informative priors (Gelman et.
+al., 2008).
+
 The table below presents estimates for the causal effect on the treated units regarding the change in completion rates before and after the project.
@@
   inner_join(ipea_final, by = join_by(code_muni == tcode)) %>%
-  mutate(indicator_ot = ifelse(is.na(indicator_ot), 0, indicator_ot),
-         perc_pea18 =pea18/populacao,
+  mutate(perc_pea18 =pea18/populacao,
          log_pop = log(populacao),
@@
 ```
+Table (ref number) summarizes the main results of the regression.
 
@@
 
+Gelman, A., Jakulin, A., Pittau, M. G., & Su, Y. S. (2008). A weakly informative default prior distribution for logistic and other regression models.
+
+Goodrich B, Gabry J, Ali I, Brilleman S (2023). “rstanarm: Bayesian applied regression modeling via Stan.” R package version 2.26.1, https://mc-stan.org/rstanarm/.
+
 Gong, T., & Xiao, H. (2017). Socially embedded anti‐corruption governance: Evidence from Hong Kong. Public Administration and Development, 37(3), 176-190.

### 2023-10-27 Scripts/paper.Rmd
Bayesian fit + using gt to report results

@@
 
-[Insert Table]
-
 When comparing "treated" and "untreated" units, there is difference between the groups, as show below by the percentage of construction works within both groups before the project started.
@@
 
-We estimate all models using the following regression equation:
+We estimate all models using the a varying-intercept regression equation (Gelman & Hill, 2006):
 
@@
 $$
-where $i$ indexes the experiment units.
+where $i$ indexes the construction units.
 $Y_i$ is $1$ if a construction work is finished, and $0$ otherwise, α is the intercept, β denotes the average treatment effect on the treated (ATT), and $T_i$ is a binary treatment indicator (municipality is part or not of Obra Transparent).
-$\gamma$ is a vector of fixed effects, $X_i$ is a matrix of Brazilian states’ fixed effects, $\theta$ is a vector of controls, and $Z_i$ an array of controls for the case $i$.
+$\gamma$ is a vector of varying-intercept, $X_i$ is a matrix of Brazilian municipalities random effects, $\theta$ is a vector of controls, and $Z_i$ an array of control variables for the case $i$.
 The error term is denoted by $ε_i$.
-We cluster the standard errors at the municipality level as mayors are the main target of the local OSBs work.
-We fit a Bayesian model with rstanarm (Goodrich, 2023) with default weakly informative priors (Gelman et.
+We fit a Bayesian model with rstanarm (Goodrich, 2023) with default weakly informative priors on parameters (Gelman et.
 al., 2008).
@@
 
-```{r balancing process,  message=FALSE, echo=FALSE}
+```{r prep data matching,  message=FALSE, echo=FALSE}
 
@@
 
-df_balancing_aux %>%
-  group_by(tipo_do_projeto) %>%
-  summarise(n())
+df_balancing_aux1 <- df_balancing_aux %>%
+  mutate(concluida_num = as.numeric(concluida))
 
-## pós projeto
-df_balancing_aux_post <- obras_inicio_projeto_ot %>%
-  mutate(municipio1 = tolower(iconv(municipio, "UTF-8",  "ASCII//TRANSLIT"))) %>%
-  inner_join(aux_muni1, by = join_by(municipio1  == name_muni1, uf == abbrev_state)) %>%
-  inner_join(ipea_final, by = join_by(code_muni == tcode)) %>%
-  mutate(indicator_ot = ifelse(is.na(indicator_ot), 0, indicator_ot),
-         perc_pea18 =pea18/populacao,
-         log_pop = log(populacao),
-         log_renda = log(rpc*populacao),
-         log_rpc = log(rpc))
-```
-Table (ref number) summarizes the main results of the regression.
-
-```{r balancing check, message=FALSE, echo=FALSE}
-m.out <- matchit(indicator_ot ~ perc_pea18  + ext_pobres  + log_rpc + 
-                  p10_ricos_desigualdade + freq_escola_15_1 + analfabetismo +
-                  log_renda + log_pop + percentual_de_execucao + rede_de_ensino_publico + tipo_do_projeto , data = df_balancing,
-                 replace = TRUE, ratio = 3)
-
-summary(m.out)
-# summary(m.out, un=FALSE)
-# plot(m.out, type = "jitter", interactive = FALSE)
-# 
-# m.sum <- summary(m.out)
-# 
-# plot(m.sum, var.order = "unmatched")
-
-# #eQQ plot
-# plot(m.out, type = "qq", which.xs = ~ log_rpc + ext_pobres + p10_ricos_desigualdade)
-# plot(m.out, type = "qq", which.xs = ~ perc_pea18 + log_pop + + freq_escola_15_1)
-# 
-# #eCDF plot - black line is treated, gray is control
-# plot(m.out, type = "ecdf", which.xs = ~ log_rpc + ext_pobres + p10_ricos_desigualdade)
-# plot(m.out, type = "ecdf", which.xs = ~  perc_pea18 + log_pop + + freq_escola_15_1)
-# 
-# #density plot - black line is treated, gray is control
-# plot(m.out, type = "density", which.xs = ~ log_rpc + ext_pobres + p10_ricos_desigualdade)
-# plot(m.out, type = "density", which.xs = ~  perc_pea18 + log_pop + + freq_escola_15_1)
-
-# Full matching on a probit PS
-m.out2 <- matchit(indicator_ot ~ perc_pea18  + ext_pobres  + log_rpc + 
-                  p10_ricos_desigualdade + freq_escola_15_1 + analfabetismo +
-                  log_renda + log_pop, data = df_balancing,
-                 method = "full", distance = "glm", link = "probit")
-# summary(m.out2, un = FALSE)
-# m.sum2 <- summary(m.out2)
-# plot(m.sum2, var.order = "unmatched")
-
-## regression with matching
-
-m.data <- match.data(m.out2) %>%
-  dplyr::select(weights, code_muni, subclass ) %>%
-  inner_join(df_balancing_aux, by = "code_muni") %>%
-  mutate(indicator_ot = as.factor(indicator_ot))
-
-fit <- lm(concluida ~ indicator_ot + perc_pea18  + ext_pobres  + log_rpc + 
-                  p10_ricos_desigualdade + freq_escola_15_1 + analfabetismo +
-                  log_renda + log_pop, data = m.data, weights = weights)
-
-# avg_comparisons(fit,
-#                 variables = "indicator_ot",
-#                 vcov = ~ subclass,
-#                 newdata = subset(m.data, indicator_ot == 1),
-#                 wts = "weights") %>%
-#   gt()
-#
-
-matching_data <- match.data(m.out2) %>%
-  dplyr::select(weights, code_muni, subclass)
+df_balancing_aux_se <- df_balancing_aux1 %>%
+  filter(uf.x %in% c("SP", "PR", "SP", "SC", "RS", "MG"))
 
@@
   rename(concluida_pre = concluida) %>%
-  mutate(id = as.character(id))
+  mutate(id = as.numeric(id))
 
@@
          log_rpc = log(rpc)) %>%
-  inner_join(matching_data, by = "code_muni") %>%
   inner_join(pre_dados, by = "id") %>%
-  dplyr::filter(concluida_pre != concluida) %>%
-  mutate(concluida = as.numeric(concluida))
+  dplyr::filter(concluida_pre == FALSE) %>%
+  mutate(concluida_num = as.numeric(concluida))
 
-fit1 <- lm(concluida ~ indicator_ot + perc_pea18  + ext_pobres  + log_rpc + 
-                  p10_ricos_desigualdade + freq_escola_15_1 + analfabetismo +
-                  log_renda + log_pop, data = data_pos, weights = weights)
+df_balancing_aux_post_se <- data_pos %>%
+  filter(uf.x %in% c("SP", "PR", "SP", "SC", "RS", "MG"))
 
@@
 
-```{r tables 2, echo=FALSE,  message=FALSE, results='asis'}
-avg_comparisons(fit1,
-                variables = "indicator_ot",
-                vcov = ~ subclass,
-                newdata = subset(data_pos, indicator_ot == 1),
-                wts = "weights") %>%
-  gt()
+Table (ref number) summarizes the main results of the regression.
+
+```{r pscore, message=FALSE, echo=FALSE}
+
+# these are the no redundancy covariates
+covs.nr <- c('perc_pea18', 'ext_pobres', 'log_rpc', 'p10_ricos_desigualdade', 'freq_escola_15_1', 'analfabetismo',
+             'log_renda', 'log_pop', 'percentual_de_execucao', 'tipo_do_projeto')
+
+# pscore estimation formula with original covariates
+
+ps_spec <- formula(indicator_muni_ot ~ log_rpc  + ext_pobres + freq_escola_15_1 + analfabetismo +
+                     log_renda   +  p10_ricos_desigualdade +
+                       + percentual_de_execucao)
+
+# Estimation of pscores using stan_glm
+set.seed(1234)
+ps_fit_pre <- stan_glm(ps_spec, family=binomial(link='logit'), 
+                     data=df_balancing_aux_se, algorithm='optimizing', refresh=0, iter = 2000)
+
+set.seed(1234)
+ps_fit_pos <- stan_glm(ps_spec, family=binomial(link='logit'), 
+                     data=df_balancing_aux_post_se, algorithm='optimizing', refresh=0, iter = 2000)
+# extrqacting logit pscores
+pscores_pre <- apply(posterior_linpred(ps_fit_pre), 2, mean)
+
+pscores_pos <- apply(posterior_linpred(ps_fit_pos), 2, mean)
+
+# matching
+#matching without replacement, original formula
+
+matches_pre <- matching(z=df_balancing_aux_se$indicator_muni_ot, score=pscores_pre, replace=FALSE)
+matched_pre <- df_balancing_aux_se[matches$match.ind,]
+
+matches_pos <- matching(z=df_balancing_aux_post_se$indicator_muni_ot, score=pscores_pos, replace=FALSE)
+matched_pos <- df_balancing_aux_post_se[matches$match.ind,]
+
+```
+
+```{r fitting bayesian model, message=FALSE, echo=FALSE}
+
+te_spec_nr <- update(ps_spec, concluida_num ~ indicator_muni_ot + (1 | municipio) + .)
+
+#treatment effect without replacement
+
+set.seed(20)
+reg_ps_pre <- stan_lmer(te_spec_nr, data=df_balancing_aux_se[matches_pre$match.ind,])
+
+## After
+set.seed(20)
+reg_ps_pos <- stan_lmer(te_spec_nr, data=df_balancing_aux_post_se[matches_pos$match.ind,])
+
+summary(reg_ps_pre)['indicator_muni_ot', 1:5]
+summary(reg_ps_pos)['indicator_muni_ot', 1:5]
+
+```
+
+```{r table 2, echo=FALSE,  message=FALSE, results='asis'}
+# posterior draws
+
+##
+# Before
+##
+
+b1_pre_sims <- as.matrix(reg_ps_pre, 
+                     pars = "indicator_muni_ot")
+
+# Posterior mean and SD of treatment
+b1_mean_pre <- mean(b1_pre_sims) # posterior mean
+b1_sd_pre <- sd(b1_pre_sims)       # posterior SD
+
+# Posterior median and 95% credible interval
+b1_quant_pre <- quantile(b1_pre_sims,   probs = c(0.025, 0.50, 0.975))
+
+b1_quant_pre <- data.frame(t(b1_quant_pre))
+names(b1_quant_pre) <- c("Q2.5", "Q50", "Q97.5")
+
+# Combine summary statistics of posterior simulation draws
+b1_df_pre_cred <- data.frame(variables = "ATT before project",
+                             post_mean = b1_mean_pre,
+                             post_sd = b1_sd_pre,
+                             b1_quant_pre[2], 
+                             b1_quant_pre[1],
+                             b1_quant_pre[3])
+
+##
+# After
+##
+b1_sims_after <- as.matrix(reg_ps_pos, 
+                     pars = "indicator_muni_ot")
+
+# Compute mean, SD, median, and 95% credible interval of treatment
+
+# Posterior mean and SD of treatment
+b1_mean_after <- mean(b1_sims_after) # posterior mean
+b1_sd_after <- sd(b1_sims_after)       # posterior SD
+
+# Posterior median and 95% credible interval
+b1_quant_after <- quantile(b1_sims_after,   probs = c(0.025, 0.50, 0.975))
+
+b1_quant_after <- data.frame(t(b1_quant_after))
+names(b1_quant_after) <- c("Q2.5", "Q50", "Q97.5")
+
+# Combine summary statistics of posterior simulation draws
+b1_df_after_cred <- data.frame(variables = "ATT After project",
+                             post_mean = b1_mean_after,
+                             post_sd = b1_sd_after,
+                             b1_quant_after[2], 
+                             b1_quant_after[1],
+                             b1_quant_after[3])
+b1_df <- bind_rows(b1_df_pre_cred, b1_df_after_cred)
+
+b1_df %>% gt() %>%
+  tab_header(
+    title = "Effect of local OSB social monitoring on construction delivery rates") %>%
+  cols_label(
+    variables = "Variables",
+    post_mean = "Posterior mean",
+    post_sd = "Posterior sd",
+    Q50 = "Posterior median",
+    Q2.5 = "Posterior 2.5% CI",
+    Q97.5 = "Posterior 97.5% CI"
+  ) %>%
+  fmt_number(
+    columns = c(post_mean, post_sd, Q50, Q2.5, Q97.5 ),
+    decimals = 3,
+    use_seps = FALSE
+  ) %>%
+  tab_source_note(
+    source_note = "452 observations after matching, with municipalities of same states as participants of Obra Transparente."
+  ) 
 ```
@@
 Fox, J. A. (2015). Social accountability: what does the evidence really say?. World Development, 72, 346-361.
+
+Gelman, A., & Hill, J. (2006). Data analysis using regression and multilevel/hierarchical models. Cambridge university press.
 

### 2023-10-27 Scripts/paper.Rmd
added font and font size

@@
 output: pdf_document
+sansfont: Sans Serif
+fontsize: 12pt
 author:

### 2023-10-27 Scripts/paper.Rmd
fixing path issue

@@
 
-load(here("obra_transparente", "Dados", "obras_inicio_projeto.Rdata"))
-load(here("obra_transparente", "Dados", "obras_fim_seg_fase.Rdata"))
+# load(here("obra_transparente", "Dados", "obras_inicio_projeto.Rdata"))
+# load(here("obra_transparente", "Dados", "obras_fim_seg_fase.Rdata"))
 
-# load(here("Dados", "obras_inicio_projeto.Rdata"))
-# load(here("Dados", "obras_fim_seg_fase.Rdata"))
+load(here("Dados", "obras_inicio_projeto.Rdata"))
+load(here("Dados", "obras_fim_seg_fase.Rdata"))
 
-simec23 <- fread(here("obra_transparente", "Dados", "simec 25-10-23 - simec.csv"), encoding = "UTF-8")
-# simec23 <- fread(here("Dados", "simec 25-10-23 - simec.csv"), encoding = "UTF-8")
+# simec23 <- fread(here("obra_transparente", "Dados", "simec 25-10-23 - simec.csv"), encoding = "UTF-8")
+simec23 <- fread(here("Dados", "simec 25-10-23 - simec.csv"), encoding = "UTF-8")
 
-load(here("obra_transparente", "Dados", "obras_fim_seg_fase.Rdata"))
+# load(here("obra_transparente", "Dados", "obras_fim_seg_fase.Rdata"))
 
-df_cidades_ot <- read_excel("Dados/181114 - Situação obras_atual.xlsx", 
+load(here("Dados", "obras_fim_seg_fase.Rdata"))
+
+df_cidades_ot <- read_excel(here("Dados", "181114 - Situação obras_atual.xlsx"), 
                                            sheet = "SIMEC-Mai17", skip = 1) %>%

### 2023-10-27 Scripts/paper.Rmd
fixed package load issue

@@
 library(ipeadatar)
-library(MatchIt)
-library(marginaleffects)
+library(rstan)
+library(arm)
+library(rstanarm)
+library(survey)
+library(broom)
+library(broom.mixed)
+library(MetBrewer)
 

### 2023-11-02 Scripts/paper.Rmd
Referências bib etc.

--- 2023-10-27 Scripts/paper.Rmd
@@
 ---
-title: "Unlocking Accountability: A Mixed-Methods Analysis of Bottom-Up Approaches in Brazilian Public Policy"
+title: "The Civil Society Organizations effect: A mixed-Methods analysis of bottom-up approaches in Brazilian public policy"
 date: "2023-10-26"
-output: pdf_document
+output: bookdown::pdf_document2
 sansfont: Sans Serif
@@
   - name: Manoel Galdino
-  affiliation: Universidade de São Paulo
-abstract: "This paper examines the role of accountability in democratic systems, focusing on its impact on public service delivery.
-Employing mixed methods, we differentiate between information-driven interventions and the mobilization and monitoring efforts of organized Civil Society Organizations (CSOs).
-We argue that well-organized CSOs, deeply embedded in society and politics, can drive significant policy change.
-The study evaluates the effectiveness of the Obra Transparente project by Transparência Brasil, engaging 21 local CSOs in South and Southeast Brazil.
-In contrast to information-centered approaches, this project establishes a network of local CSOs, providing technical support and training for monitoring public school and nursery construction projects.
-Our findings emphasize the importance of sustained, coordinated efforts by organized civil society.
-These efforts, involving direct engagement with municipal officials, persistent follow-ups, and on-site visits, lead to more substantial outcomes.
-This research contributes to understanding how organized civil society mobilization can achieve bottom-up accountability, a crucial aspect of democratic governance.
-However, contextual variations may limit the effectiveness of CSO interventions."
-keywords: "Accountability, Brazil, mixed methods, state capacity, public policy"
+    affiliation: Universidade de São Paulo - Brazil.
+  - names: Juliana Sakai
+    affiliation: Transparência Brasil - Brazil
+  - names: Bianca Vaz Mondo
+    affiliation: Transparência Brasil - Brazil
+  - names: Natália Paiva
+    affiliation: Alandar Consulting - Brazil
+abstract: "This paper examines the effect of bottom-up accountability on public service delivery.
+We differentiate between information-driven interventions and the mobilization and monitoring efforts of organized Civil Society Organizations (CSOs), and argue that the latter type of interventions can can drive significant policy change.
+The study evaluates the effectiveness of the Obra Transparente project by Brazilian NGO Transparência Brasil, engaging 21 local CSOs in South and Southeast Brazil.
+Our findings emphasize the importance of sustained, coordinated efforts by socially embedded CSOS.
+These efforts, involving direct engagement with municipal officials and ensuring that their complains cannot be ignored lead to more substantial outcomes when compared with citizens information-driven."
+keywords: "accountability, Civil Society Organizations, mixed methods, community-driven development, public policy."
+bibliography: OT_paper.bib
 ---
@@
 library(ipeadatar)
-library(MatchIt)
-library(marginaleffects)
-
+library(rstan)
+library(arm)
+library(rstanarm)
+library(survey)
+library(broom)
+library(broom.mixed)
+library(MetBrewer)
 ```
@@
 ```{r loading construction data,  message=FALSE, echo=FALSE}
-
-# lista_cidades_ot <- c("Araucária", "Caçador", "Campo Mourão", "Cascavel", "Chapecó",
-#                       "Foz do Iguaçu", "Goioerê", "Gravataí", "Guarapuava", "Imbituba", "Lajeado",
-#                       "Limeira", "Palhoça", "Paranaguá", "Pelotas", "Ponta Grossa", "Santa Maria",
-#                       "São Francisco do Sul", "São José dos Campos", "Taubaté", "Uberlândia")
-# 
-# df_cidades_ot <- data.frame(municipio = lista_cidades_ot, indicator_ot = 1)
 
@@
 
-df_cidades_ot <- read_excel(here("Dados", "181114 - Situação obras_atual.xlsx"), 
+df_cidades_ot <- read_excel(here("Dados", "situacao obras_atual.xlsx"), 
                                            sheet = "SIMEC-Mai17", skip = 1) %>%
@@
 antes_projeto <- obras_inicio_projeto_ot %>%
+  dplyr::filter(uf %in% c("SP", "PR", "SP", "SC", "RS", "MG")) %>%
   group_by(indicator_muni_ot, concluida) %>%
@@
 depois_projeto <- obras_fim_seg_fase %>%
+  dplyr::filter(uf %in% c("SP", "PR", "SP", "SC", "RS", "MG")) %>%
   group_by(indicator_muni_ot, concluida) %>%
@@
 
-Accountability is a vital component of democratic systems to ensure the efficient delivery of public services (Besley and Ghatak, 2003; Cameron, 2004;  O'Donnell, 1998).
-Traditionally defined as the process of holding authorities responsible for their actions (Finer, 1941; Mulgan, 2000; O'Loughlin, 1990), the literature has evolved to encompass a broader range of mechanisms for overseeing politicians and the bureaucracy..
-While some authors focused on the study of formal institutions (O’Donnel, 2003, Kenney 2003) in what is known as horizontal accountability, other have analyzed responsiveness of politicians to voters (Relly, 2012) the media and civil society organizations at large (Fox e Brown, 1998; Paul, 2002); in what is known as vertical accountability.
+Accountability is a crucial element in democratic systems, ensuring the efficient delivery of public services [@besley_2003; @cameron_2004; @odonnell_1998].
+Initially defined as the process of holding authorities responsible for their actions [@mulgan_2000; @oloughlin_1990], the literature has since broadened to include various oversight mechanisms for politicians and the bureaucracy.
+Some authors focus on formal institutions [@odonnell_2003; @kenney_2003], known as horizontal accountability, while others examine how politicians respond to voters, the media, and civil society organizations [@bertelli_2020; @relly_2012; @paul_1992], referred to as vertical accountability.
 
 Recent studies have highlighted the role of "bottom-up accountability" (also known as social accountability, Fox, 2015), in which citizens receive information about public policies and use it for social control.
-The pioneering study 'Power to the People' (Bjorkman and Svensson, 2009), which demonstrated the impact of local community engagement in monitoring the provision of health services, inspired subsequent literature that tested similar interventions in different contexts.
+The pioneering study 'Power to the People' [@bjorkman_2009], which demonstrated the impact of local community engagement in monitoring the provision of health services, inspired subsequent literature that tested similar interventions in different contexts.
 
 The mechanism would works like this: Constituents have firsthand information about the outcomes of local policies, giving citizens incentives to combat corruption that directly affects them.
-Since policymakers are sensitive to social feedback from their own communities (Serra, 2011: 570), bottom-up accountability could influence local public policies
+Since policymakers are sensitive to social feedback from their own communities [@serra_2012], bottom-up accountability could influence local public policies
 
-However, a series of recent studies have raised doubts about the effectiveness of "bottom-up accountability" strategies based on interventions aimed at increasing the monitoring capacity of ordinary citizens regarding public policies (Freire, Mignozzetti & Galdino, 2020; Raffler, Posner & Parkinson, 2019, Fox, 2015).
+However, a series of recent studies have raised doubts about the effectiveness of "bottom-up accountability" strategies based on interventions aimed at increasing the monitoring capacity of ordinary citizens regarding public policies [@freire_etal2020; @raffler_etal2019; @fox_2015].
 
@@
 The disappointing results have cast doubts on the effectiveness of the bottom-up accountability strategy for improving the delivery of public services, reducing corruption, and enhancing government efficiency.
-Some authors (Fox, 2015; Ankamah, 2019) have suggested that social accountability without "teeth," defined as the government's capacity to respond to citizens' voices, has limited impact.
+Some authors [@fox_2015; @ankamah_2019] have suggested that social accountability without "teeth," defined as the government's capacity to respond to citizens' voices, has limited impact.
 
@@
 We argue that we need to differentiate between information-led tactical interventions and active mobilization and monitoring by Civil Society Organizations (CSOs).
-By their very nature, established CSOs are embedded in society and politics and can have a substantial impact on policy change (Gong & Xiao, 2017.
-Joshi & Houtzager, 2012).
+By their very nature, established CSOs are embedded in society and politics and can have a substantial impact on policy change [@gong_2017; @joshi_2012].
 
-The paper argues that a missing feature in most of the literature is that these interventions should target CSOs instead of individual citizens, and ensure that the intervention enhances the ability of the CSOs to overcome their collective action problem  (Mattoni & Odilla, 2021; Odilla, 2023).
+The paper argues that a missing feature in most of the literature is that these interventions should target CSOs instead of individual citizens, and ensure that the intervention enhances the ability of the CSOs to overcome their collective action problem [@mattoni_2021; @odilla_2023].
 
 The present paper provides evidence supporting this argument.
-We reassess the evidence provided by Freire, Mignozzetti & Galdino (2020), considering a different intervention than the one they evaluated.
+We reassess the evidence provided by @freire_etal2020, considering a different intervention than the one they evaluated.
 They provided experimental evidence that a mobile app (Tá de Pé) made available to citizens did not improve the delivery of school and nursery construction works.
@@
 We argue that we need to differentiate between information-led tactical interventions and active mobilization and monitoring by Civil Society Organizations.
-By their very nature, established CSOs are embedded in society and politics and, as such, can have teeth of their own (Gong & Xiao, 2017.
-Joshi & Houtzager, 2012).
+By their very nature, established CSOs are embedded in society and politics and, as such, can have teeth of their own [@gong_2017; @joshi_2012].
 It may be only that we need mobilization by organized civil society, in a structured way, for civil society voices to be heard with “teeth”.
-Some studies have suggested that a key feature of successful change in public policies is the pressure of collectively organized agents (Mattoni & Odilla, 2021; Odilla, 2023).
+Some studies have suggested that a key feature of successful change in public policies is the pressure of collectively organized agents [@mattoni_2021; @odilla_2023].
 Collective action is a hard problem to be overcome and creating CSOs is one way to achieve this.
@@
 
-We employ an integrated inference approach (Humphreys & Jacobs, 2023) to analyze qualitative data within the framework of causal queries.
+We employ an integrated inference approach [@humphreys_2023] to analyze qualitative data within the framework of causal queries.
 As this approach is relatively innovative within qualitative research, we'll provide a comprehensive explanation.
 
-The methodology outlined by Humphreys & Jacobs (2023) mandates the creation of a causal model encoded in Directed Acyclic Graphs (DAGs), a framework developed by Pearl (2009).
-Bayesian inference, recently promoted in qualitative data analysis (Fairfield & Charman, 2022), serves as the foundation for deriving quantitative estimates for causal queries constructed using the proposed DAG.
+The methodology outlined by [@humphreys_2023] mandates the creation of a causal model encoded in Directed Acyclic Graphs (DAGs), a framework developed by Pearl (2009).
+Bayesian inference, recently promoted in qualitative data analysis [@fairfield_2022], serves as the foundation for deriving quantitative estimates for causal queries constructed using the proposed DAG.
+
 In our current study, we investigate the impact of Civil Society Organization (CSO) monitoring on two aspects: the completion of construction works and the rectification of issues and irregularities found in construction facilities.
@@
 In our current investigation, let's focus on the (M -> C) DAG.
-To clarify what a type is, we'll employ the Potential Outcomes (PO) notation (Rubin, 2005; Imbens & Rubin, 2015).
+To clarify what a type is, we'll employ the Potential Outcomes (PO) notation [@rubin_2005; @imbens_2015].
 Within the PO framework, every case has two potential outcomes: one when the treatment (in this case, CSO monitoring, M) is absent and another when the treatment is present.
@@
 As one collects data (any data, be it qualitative or quantitative), one can make assumptions about the nature of the data (such as the Data Generating Process), and then update the model and provide new answers to the causal queries, which hopefully will be informative enough to be useful for the task at hand.
-And even when the model or hypothesis is not completely identified, it can be partially identified (Manski, 2003), which is still a useful answer to causal queries.
+And even when the model or hypothesis is not completely identified, it can be partially identified [@manski_2003], which is still a useful answer to causal queries.
 
@@
 
-The evidence gathered is primarily based on documented reports collected by Transparência Brasil over the course of the project.
+The evidence gathered is primarily based on documented reports collected by Transparência Brasil and produced by the local OSBs over the course of the project.
 We also use evidence collected on semi-structured interviews and an online survey with representatives of the 21 CSOs conducted by an independent evaluator of the project.
-We also use administrative data about construction works data by municipalities and socio-demographic data on municipalities.
+For the quantitative analysis, we use administrative data about construction works data by municipalities and socio-demographic data on municipalities.
 The questions asked in the survey as well the aggregate answered are presented in annex A.
@@
 After that, the delivery rate was 100% and one of the construction work was a previously paralyzed construction.
-According to a report by Transparência Brasil (Coelho, Galdino & Sakai., 2021), out of 771 stalled construction projects that were eventually completed, over 50% of them took more than two years to be delivered and 25% took three years or more.
+According to a report by Transparência Brasil [@coelho_etal2021], out of 771 stalled construction projects that were eventually completed, over 50% of them took more than two years to be delivered and 25% took three years or more.
 As we can see, the odds were against finishing the construction works.
@@
 
-From a causal perspective, we are interested in what is called case-level causal attribution (Humphreys & Jacobs, 2023), i.e, did the monitoring cause the delivery of the construction works?In other words, we are conditioning on the fact that M = 1 and C = 1, which constrains the possible types for Taubaté to be $\theta^C_{1,1}$ ou $\theta^C_{0,1}$.
+From a causal perspective, we are interested in what is called case-level causal attribution [@humphreys_2023], i.e, did the monitoring cause the delivery of the construction works?
+In other words, we are conditioning on the fact that M = 1 and C = 1, which constrains the possible types for Taubaté to be $\theta^C_{1,1}$ ou $\theta^C_{0,1}$.
 Assuming a simple model in which CSO monitoring causes the completion of works (M -> C), and with the eight within-case instances, we do the causal query.
@@
 TCU recommended that the bidding process should be redone, and construction plans were to be redesigned, with more cost-effective solutions for the contention walls.
-In the new bidding process, their cost plummeted to R$ 416,883.17 (US$ 110,873.2), a reduction of US$ 308,631.7 — 74% less.
+In the new bidding process, their cost plummeted to R\$ 416,883.17 (USD 110,873.2), a reduction of USD 308,631.7 — or 74% less.
 To give a sense of the impact on the city budget, the amount saved on these three constructions alone represents about 3% of all capital investments of Araucária in 2018.
@@
 To do so, we collected data on school and nursery construction projects across the entire country, encompassing over two thousand municipalities and more than 14 thousand construction projects, spanning all phases from planning to execution and completion.
-The table below provides descriptive statistics for these construction projects.
+The @ref(tab:table1) below provides descriptive statistics for these construction projects.
 
@@
 
-```{r tables, echo=FALSE, message=FALSE, results='asis'}
+```{r table1, echo=FALSE, message=FALSE, results='asis'}
 antes_projeto %>%
@@
   tab_header(
-    title = "Percentage of finished fonstruction works before the project",
+    title = "Percentage of finished construction works before the project",
     subtitle = "Situation in August 2017 and August 2019") %>%
+   opt_align_table_header(align = "left") %>%
   cols_label(
-    indicator_muni_ot = "Participating Municipalities in Obra Transparente ",
-    perc.x = "Percentage of Completed Constructions Before Project",
-    perc.y = "Percentage of Completed Constructions After Project"
+    indicator_muni_ot = "# of participating cities",
+    perc.x = "% (Before Project)",
+    perc.y = "% (After Project)"
   ) %>%
@@
     decimals = 0
-  )
+  ) %>%
+    tab_source_note(
+    source_note = "Construction projects in states SP, MG, SC, PR and RS."
+  ) %>%
+  tab_options(table.align='left')
 ```
@@
 Our primary objective is to compare the project's effects on the rate of delivery.
-To estimate the Average Treatment Effect on the Treated (ATT), we employed a matching strategy (Ho et al.
-(2007; Rubin, 1973).
+To estimate the Average Treatment Effect on the Treated (ATT), we employed a matching strategy [@ho_etal2007; @rubin_1973] with a Bayesian logistic regression to create the propensity scores.
+Balance was successful after matching.
 We also applied the same procedure to pre-project data to ensure that there were no substantial differences between the treated and control groups.
 
-We estimate all models using the a varying-intercept regression equation (Gelman & Hill, 2006):
+We estimate all models using the a varying-intercept regression equation [@gelman_2006]:
 
@@
 $$
-where $i$ indexes the construction units.
-$Y_i$ is $1$ if a construction work is finished, and $0$ otherwise, α is the intercept, β denotes the average treatment effect on the treated (ATT), and $T_i$ is a binary treatment indicator (municipality is part or not of Obra Transparent).
-$\gamma$ is a vector of varying-intercept, $X_i$ is a matrix of Brazilian municipalities random effects, $\theta$ is a vector of controls, and $Z_i$ an array of control variables for the case $i$.
-The error term is denoted by $ε_i$.
-We fit a Bayesian model with rstanarm (Goodrich, 2023) with default weakly informative priors on parameters (Gelman et.
-al., 2008).
+
+Where $i$ indexes the construction units, $Y_i$ is $1$ if a construction work is finished and $0$ otherwise.
+$\alpha$ represents the intercept, $\beta$ denotes the average treatment effect on the treated (ATT), and $T_i$ is a binary treatment indicator (whether the municipality is part of Obra Transparent or not).
+Symbol $\gamma$ is a vector of varying intercepts, $X_i$ is a matrix of random effects for Brazilian municipalities, $\theta$ is a vector of control variables, and $Z_i$ is an array of control variables for case $i$.
+The error term is represented by $\epsilon_i$.
+We employed a Bayesian model with rstanarm [@goodrich_etal2023] with default weakly informative priors on the parameters [@gelman_etal2008].
 
@@
 
-```{r prep data matching,  message=FALSE, echo=FALSE}
+```{r prep data matching,  message=FALSE, echo=FALSE, cache=TRUE}
 
@@
 
+save(df_balancing_aux1, file = here("Dados", "df_balancing_aux1.RData"))
+save(df_balancing_aux_se, file = here("Dados", "df_balancing_aux_se.RData"))
+save(df_balancing_aux_post_se, file = here("Dados", "df_balancing_aux_post_se.RData"))
+save(data_pos, file = here("Dados", "data_pos.RData"))
 ```
 
-Table (ref number) summarizes the main results of the regression.
+# these are the no redundancy covariates with and without state covariate
+covs.nr <- c('perc_pea18', 'ext_pobres', 'log_rpc', 'p10_ricos_desigualdade', 'freq_escola_15_1', 'analfabetismo',
+             'log_renda', 'log_pop', 'percentual_de_execucao', 'tipo_do_projeto')
+
+covs.nr.st <- c(covs.nr, "uf.x")
+
+Table (insert ref number) summarizes the main results of the regression.
+The first row presents the results for the regression before the project started, where we expect the effect of the project to be zero, since it didn't exist.
+The second row shows the effect after the end of the project, when we expect the impact to be positive.
+The first column is an estimate of the posterior mean of the impact of the project and the second one is the posterior standard deviation of the estimate.
+We also present posterior median and $2.5%$ and $97.5%$ quantiles, in order to quantify the uncertainty around the estimates with a 95% credibility interval.
+
+The hypothesis are corroborated, and we did not find an effect before the starting of the project, but found an effect aftet the end of the project.
+On average, a city that received the project Obra Transparente increases its delivery rate by almost 10%.
+These results support our argument and the qualitative evidence we presented that sustained and costly bottom-up accountability improve public policies.
 
@@
 covs.nr <- c('perc_pea18', 'ext_pobres', 'log_rpc', 'p10_ricos_desigualdade', 'freq_escola_15_1', 'analfabetismo',
-             'log_renda', 'log_pop', 'percentual_de_execucao', 'tipo_do_projeto')
+             'log_renda', 'log_pop', 'percentual_de_execucao')
 
@@
 ps_spec <- formula(indicator_muni_ot ~ log_rpc  + ext_pobres + freq_escola_15_1 + analfabetismo +
-                     log_renda   +  p10_ricos_desigualdade +
-                       + percentual_de_execucao)
+                     log_renda   +  p10_ricos_desigualdade + percentual_de_execucao)
 
@@
                      data=df_balancing_aux_post_se, algorithm='optimizing', refresh=0, iter = 2000)
-# extrqacting logit pscores
+
+# extracting logit pscores
 pscores_pre <- apply(posterior_linpred(ps_fit_pre), 2, mean)
@@
 #matching without replacement, original formula
-
 matches_pre <- matching(z=df_balancing_aux_se$indicator_muni_ot, score=pscores_pre, replace=FALSE)
-matched_pre <- df_balancing_aux_se[matches$match.ind,]
+matched_pre <- df_balancing_aux_se[matches_pre$match.ind,]
 
 matches_pos <- matching(z=df_balancing_aux_post_se$indicator_muni_ot, score=pscores_pos, replace=FALSE)
-matched_pos <- df_balancing_aux_post_se[matches$match.ind,]
+matched_pos <- df_balancing_aux_post_se[matches_pos$match.ind,]
 
@@
 
-```{r fitting bayesian model, message=FALSE, echo=FALSE}
+```{r fitting bayesian model, message=FALSE, echo=FALSE, cache = TRUE}
 
-te_spec_nr <- update(ps_spec, concluida_num ~ indicator_muni_ot + (1 | municipio) + .)
+df_balancing_aux_se <- df_balancing_aux_se %>%
+  dplyr::select(concluida_num , indicator_muni_ot, code_muni, log_rpc, ext_pobres, freq_escola_15_1,analfabetismo,
+                log_renda, p10_ricos_desigualdade, percentual_de_execucao, municipio)
+
+te_spec_nr <- update(ps_spec, concluida_num ~ indicator_muni_ot + (1 | code_muni) + .)
 
@@
 
-set.seed(20)
-reg_ps_pre <- stan_lmer(te_spec_nr, data=df_balancing_aux_se[matches_pre$match.ind,])
+set.seed(120)
+reg_ps_pre <- stan_lmer(te_spec_nr, data=df_balancing_aux_se[matches_pre$match.ind,], iter = 4000, refresh=0)
 
 ## After
-set.seed(20)
-reg_ps_pos <- stan_lmer(te_spec_nr, data=df_balancing_aux_post_se[matches_pos$match.ind,])
-
-summary(reg_ps_pre)['indicator_muni_ot', 1:5]
-summary(reg_ps_pos)['indicator_muni_ot', 1:5]
+set.seed(120)
+reg_ps_pos <- stan_lmer(te_spec_nr, data=df_balancing_aux_post_se[matches_pos$match.ind,], iter = 4000, refresh=0)
 
@@
 
-```{r table 2, echo=FALSE,  message=FALSE, results='asis'}
+```{r processing bayes fit, echo=FALSE,  message=FALSE}
 # posterior draws
@@
 b1_df <- bind_rows(b1_df_pre_cred, b1_df_after_cred)
+```
+
+```{r table2, echo=FALSE,  message=FALSE, results='asis'}
 
@@
   tab_header(
-    title = "Effect of local OSB social monitoring on construction delivery rates") %>%
+    title = "Effect of local OSB social monitoring on construction delivery rates",
+    subtitle = "Posterior probabilities") %>%
   cols_label(
     variables = "Variables",
-    post_mean = "Posterior mean",
-    post_sd = "Posterior sd",
-    Q50 = "Posterior median",
-    Q2.5 = "Posterior 2.5% CI",
-    Q97.5 = "Posterior 97.5% CI"
+    post_mean = "Mean",
+    post_sd = "Sd",
+    Q50 = "Median",
+    Q2.5 = "2.5% CI",
+    Q97.5 = "97.5% CI"
   ) %>%
@@
   tab_source_note(
-    source_note = "452 observations after matching, with municipalities of same states as participants of Obra Transparente."
-  ) 
+    source_note = "452 observations for the pre-treatment period and 320 observations for the post-treatment period, resulting from the matching procedure, and encompassing municipalities in the same states as municipalities of Obra Transparente"
+  ) %>%
+  tab_options(., container.width = 500, container.height =     500)
 ```
@@
 
-The fact that an intervention like Tá de Pé (Freite et.
-al.
-,2020), which provided information to citizens about construction work, but did not produce a meaningful impact does not mean that bottom up accountability does not have any effect.
+The fact that an intervention like Tá de Pé [@freire_etal2020], which provided information to citizens about construction work, but did not produce a meaningful impact does not mean that bottom up accountability does not have any effect.
 The evidence we gathered here, assessed with multiple methods, clearly shows that costly and consistent oversight by civil society can produce results that are quite impactful, be it increased rate of project completion, improved quality of the construction works or decreasing in governmental spending.
@@
 ## References
-
-Ankamah, S. S. (2019). Why do “teeth” need “voice”? The case of anti‐corruption agencies in three Australian states. Australian Journal of Public Administration, 78(4), 481-496.
-
-Besley T and Ghatak M (2003) Incentives, choice, and accountability
-in the provision of public services. Oxford Review of Economic Policy 19(2): 235–249.
-
-Björkman, M., & Svensson, J. (2009). Power to the people: evidence from a randomized field experiment on community-based monitoring in Uganda. The Quarterly Journal of Economics, 124(2), 735-769.
-
-Cameron W (2004) Public accountability: Effectiveness, equity, ethics. Australian Journal of Public Administration 63(4): 59–67.
-
-Coelho, J., Galdino, M. Sakai, J. (2021) Levantamento: Obras federais paralisadas de creches e escolas com maiores chances de serem concluídas. Available at:
-https://www.transparencia.org.br/downloads/publicacoes/levantamentoobrasfederaisparalisadascrechesescolasmaioreschancesseremconcluidas.pdf. Accessed on 10-25-2023.
-
-Fairfield, T., & Charman, A. E. (2022). Social inquiry and Bayesian inference: Rethinking qualitative research. Cambridge University Press.
-
-Fox, J. A. (2015). Social accountability: what does the evidence really say?. World Development, 72, 346-361.
-
-Gelman, A., & Hill, J. (2006). Data analysis using regression and multilevel/hierarchical models. Cambridge university press.
-
-Gelman, A., Jakulin, A., Pittau, M. G., & Su, Y. S. (2008). A weakly informative default prior distribution for logistic and other regression models.
-
-Goodrich B, Gabry J, Ali I, Brilleman S (2023). “rstanarm: Bayesian applied regression modeling via Stan.” R package version 2.26.1, https://mc-stan.org/rstanarm/.
-
-Gong, T., & Xiao, H. (2017). Socially embedded anti‐corruption governance: Evidence from Hong Kong. Public Administration and Development, 37(3), 176-190.
-
-Ho, Daniel E., Kosuke Imai, Gary King, and Elizabeth A.
-Stuart.
-2007.
-“Matching as Nonparametric Preprocessing for Reducing Model Dependence in Parametric Causal Inference.” Political Analysis 15 (3): 199–236.
-
-Humphreys, M., & Jacobs, A. (2023). Integrated Inferences: Causal Models for Qualitative and Mixed-Method Research (Strategies for Social Inquiry). Cambridge: Cambridge University Press.
-
-Imbens, G. W., & Rubin, D. B. (2015). Causal inference in statistics, social, and biomedical sciences. Cambridge University Press.
-
-Joshi, A., & Houtzager, P. P. (2012). Widgets or watchdogs? Conceptual explorations in social accountability. Public Management Review, 14(2), 145-162.
-
-Kenney, C. D. (2003). Horizontal accountability: concepts and conflicts. in Democratic Accountability in Latin America. Mainwaring, S., & Welna, C. (Eds.). OUP Oxford.
-
-Manski, C. F. (2003). Partial identification of probability distributions (Vol. 5). New York: Springer
-
-Mattoni, A., & Odilla, F.
-(2021).
-Digital Media, Activism, and Social Movements' Outcomes in the Policy Arena.
-The Case of Two Anti-Corruption Mobilizations in Brazil.
-Partecipazione e conflitto, 14(3), 1127-1150.
-
-Medeiros, Vanda. (2019). POST PROJECT EVALUATION FOR THE UNITED NATIONS DEMOCRACY FUND. Independent Report submitted to UNDEF.
-
-Mulgan R (2000) ‘Accountability’: An ever-expanding concept? Public Administration 78(3): 555–573.
-
-Mondo, B.; Galdino, M.; Voigt, J.; Sakai, J.
-Oliveira, C.
-(2018).
-Obra Transparente: Monitoramento de obras de escolas e creches financiadas pelo governo federal.
-Report by Transparência Brazil.
-Available at : https://www.transparencia.org.br/downloads/publicacoes/18082018_relatorioOT%20(1).pdf
-
-Odilla, F. (2023). Bots against corruption: Exploring the benefits and limitations of AI-based anti-corruption technology. Crime, Law and Social Change, 1-44.
-
-O’Donnell GA (1998) Horizontal accountability in new democracies.
-Journal of Democracy 9(3): 112–126.
-
-O’donnell, G. (2003). Horizontal accountability: The legal. Democratic Accountability in Latin America, 34.
-
-O’Loughlin MG (1990) What is bureaucratic accountability and how
-can we measure it? Administration & Society 22(3): 275–302.
-
-PAUL, Samuel. Accountability in public services: exit, voice and control. World Development 29, 7 (julho) p. 1047 – 1060. 2002.
-
-Pearl, Judea. 2009. Causality. Cambridge university press.
-
-Raffler, P., Posner, D. N., & Parkerson, D. (2019). The weakness of bottom-up accountability: experimental evidence from the Ugandan health sector. Los Angeles: Innovations for Poverty Action.
-
-Relly, J.
-E.
-(2012).
-Examining a model of vertical accountability: A cross-national study of the influence of information access on the control of corruption.
-Government Information Quarterly, 29(3), 335-345.
-Rubin, Donald B. 1973. “Matching to Remove Bias in Observational Studies.” Biometrics 29 (1): 159.
-
-Rubin, D. B. (2005). Causal inference using potential outcomes: Design, modeling, decisions. Journal of the American Statistical Association, 100(469), 322-331.
-
-Serra D (2011) Combining top-down and bottom-up accountability: Evidence from a bribery experiment. The Journal of Law, Economics, & Organization 28(3): 569–587.
-
-Tribunal de Contas da União. (2014). Recomendações Básicas para a Contratação e Fiscalização de Obras de Edificações Públicas.

### 2023-11-02 matching.Rmd
Appendix matching

---
title: "Appendix"
author: "Manoel Galdino"
date: "2023-11-01"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

One of the key objectives of using matching is to achieve balance among treated and untreated. We provide evidence that our matching strategy was successful in achieving balancing. In the process, we explain how we performed balancing and our choice of restricting the comparison group of municipalities to the same states as the one involved in project Obra Transparente.

```{r packege load appendix}
library(rstan)
library(arm)
library(rstanarm)
library(survey)
library(broom)
library(broom.mixed)
library(MetBrewer)
```

## Including Plots

You can also embed plots, for example:

```{r matching-loading-data, echo=FALSE, message=FALSE}
load(here("Dados", "df_balancing_aux1.RData"))
load(here("Dados", "df_balancing_aux_se.RData"))
load(here("Dados", "df_balancing_aux_post_se.RData"))
load(here("Dados", "data_pos.RData"))
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2023-11-06 matching.Rmd
matching scripts

@@
 date: "2023-11-01"
-output: pdf_document
+output: bookdown::pdf_document2
 ---
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-```
+One of the key objectives of using matching is to achieve balance among treated and untreated. We provide evidence that our matching strategy was successful in achieving balancing.
 
-One of the key objectives of using matching is to achieve balance among treated and untreated.
-We provide evidence that our matching strategy was successful in achieving balancing.
-In the process, we explain how we performed balancing and our choice of restricting the comparison group of municipalities to the same states as the one involved in project Obra Transparente.
+Since project Obra Transparente happened in five states in the South and Southeast of Brazil (São Paulo, Minas Gerais, Paraná, Santa Catarina and Rio Grande do Sul), re restricted the sample of projects to these states.
 
-```{r packege load appendix}
+We performed nearest neighbor propensity score matching, based on propensity scores computed with Bayesian logistic regression with weakly informative priors.
+
+The pre-treatment variables used are percentage of poor people in the city (2010 census data), the logarithm of per capita income (2010 census data), percentage of income appropriated by the 10% households with higher per capita income (2010 census data), rate of school frequency among youth (between 15 and 17 years old, 2010 census data), illiteracy rate (2010 census data), log of GDP (2010 census data), log of population (2010 census data), and percentage of construction execution (Minister of Education - FNDE data, collected in may 2017).
+
+```{r package load appendix, echo=FALSE, message=FALSE}
 library(rstan)
@@
 library(MetBrewer)
+library(here)
+library(tidyverse)
 ```
-
-## Including Plots
-
-You can also embed plots, for example:
 
@@
 
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+```{r matching-processing, echo=FALSE, message=FALSE, cache = TRUE}
+
+# pscore estimation
+
+ps_spec <- formula(indicator_muni_ot ~ log_rpc  + ext_pobres + freq_escola_15_1 + analfabetismo + log_renda   +  p10_ricos_desigualdade + percentual_de_execucao)
+
+######
+# pre project
+#####
+
+# Estimation of pscores using stan_glm
+set.seed(1234)
+ps_fit_pre <- stan_glm(ps_spec, family=binomial(link='logit'), 
+                     data=df_balancing_aux_se, algorithm='optimizing', refresh=0, iter = 2000)
+
+# extracting logit pscores
+pscores_pre <- apply(posterior_linpred(ps_fit_pre), 2, mean)
+
+df_balancing_aux_se <- df_balancing_aux_se %>%
+  mutate(pscores_pre = pscores_pre)
+
+# visualization
+isfahan <- MetBrewer::met.brewer("Isfahan1")
+
+# pre-matching
+pre_project_pre_matching_plot <- ggplot() +
+  geom_histogram(data = filter(df_balancing_aux_se, indicator_muni_ot == 1),
+                 bins = 50, aes(x = pscores_pre ),
+                 fill = isfahan[2]) +
+  geom_histogram(data = filter(df_balancing_aux_se, indicator_muni_ot == 0),
+                 bins = 50, aes(x = pscores_pre, y = -after_stat(count)),
+                 fill = isfahan[6]) +
+  geom_hline(yintercept = 0) +
+  annotate(geom = "label", x = -15, y = 40, label = "Treated",
+           fill = isfahan[2], color = "white", hjust = 0) +
+  annotate(geom = "label", x = -15, y = -100, label = "Untreated",
+           fill = isfahan[6], color = "white", hjust = 0) +
+  coord_cartesian(xlim = c(-20, 0), ylim = c(-700, 80)) +
+  labs(x = "Propensity", y = "Relative Freq.")
+
+#matching without replacement, original formula
+matches_pre <- matching(z=df_balancing_aux_se$indicator_muni_ot, score=pscores_pre, replace=FALSE)
+
+matched_pre <- df_balancing_aux_se[matches_pre$match.ind,]
+
+# matched_pre <- matched_pre %>%
+#   mutate(pscores_pre = pscores_pre[matches_pre$match.ind])
+
+# post-matching
+pre_project_post_matching_plot <- ggplot() +
+  geom_histogram(data = filter(matched_pre, indicator_muni_ot == 1),
+                 bins = 50, aes(x = pscores_pre ),
+                 fill = isfahan[2]) +
+  geom_histogram(data = filter(matched_pre, indicator_muni_ot == 0),
+                 bins = 50, aes(x = pscores_pre, y = -after_stat(count)),
+                 fill = isfahan[6]) +
+  geom_hline(yintercept = 0) +
+  annotate(geom = "label", x = -5, y = 20, label = "Treated",
+           fill = isfahan[2], color = "white", hjust = 0) +
+  annotate(geom = "label", x = -5, y = -25, label = "Untreated",
+           fill = isfahan[6], color = "white", hjust = 0) +
+  coord_cartesian(xlim = c(-6, 0), ylim = c(-50, 60)) +
+  labs(x = "Propensity", y = "Relative Freq.")
+
+######
+# Post project
+#####
+
+set.seed(1234)
+ps_fit_pos <- stan_glm(ps_spec, family=binomial(link='logit'), 
+                     data=df_balancing_aux_post_se, algorithm='optimizing', refresh=0, iter = 2000)
+
+# extracting logit pscores
+pscores_pos <- apply(posterior_linpred(ps_fit_pos), 2, mean)
+
+df_balancing_aux_post_se <- df_balancing_aux_post_se %>%
+  mutate(pscores_pos = pscores_pos)
+
+# pre-matching
+post_project_pre_matching_plot <- ggplot() +
+  geom_histogram(data = filter(df_balancing_aux_post_se,
+                               indicator_muni_ot == 1),
+                 bins = 50, aes(x = pscores_pos ),
+                 fill = isfahan[2]) +
+  geom_histogram(data = filter(df_balancing_aux_post_se,
+                               indicator_muni_ot == 0),
+                 bins = 50, aes(x = pscores_pos, y = -after_stat(count)),
+                 fill = isfahan[6]) +
+  geom_hline(yintercept = 0) +
+  annotate(geom = "label", x = -15, y = 20, label = "Treated",
+           fill = isfahan[2], color = "white", hjust = 0) +
+  annotate(geom = "label", x = -15, y = -40, label = "Untreated",
+           fill = isfahan[6], color = "white", hjust = 0) +
+  coord_cartesian(xlim = c(-20, 0), ylim = c(-350, 70)) +
+  labs(x = "Propensity", y = "Relative Freq.")
+
+#matching without replacement, original formula
+matches_post <- matching(z=df_balancing_aux_post_se$indicator_muni_ot, score=pscores_pos, replace=FALSE)
+
+matched_post <- df_balancing_aux_post_se[matches_post$match.ind,]
+
+# matched_post <- matched_post %>%
+#   mutate(pscores_pos1 = pscores_pos[matches_post$match.ind])
+
+# visualization
+
+# balance after matching
+post_project_post_matching_plot <- ggplot() +
+  geom_histogram(data = filter(matched_post, indicator_muni_ot == 1),
+                 bins = 50, aes(x = pscores_pos ),
+                 fill = isfahan[2]) +
+  geom_histogram(data = filter(matched_post, indicator_muni_ot == 0),
+                 bins = 50, aes(x = pscores_pos, y = -after_stat(count)),
+                 fill = isfahan[6]) +
+  geom_hline(yintercept = 0) +
+  annotate(geom = "label", x = -5, y = 10, label = "Treated",
+           fill = isfahan[2], color = "white", hjust = 0) +
+  annotate(geom = "label", x = -5, y = -10, label = "Untreated",
+           fill = isfahan[6], color = "white", hjust = 0) +
+ # scale_y_continuous(label = abs) +
+  coord_cartesian(xlim = c(-6, 0), ylim = c(-25, 25)) +
+  labs(x = "Propensity", y = "Relative Freq.")
+
+```
+
+## Balance
+
+We performed two analysis in the main document, firstly, a regression with data before the proejct started, as a placebo test.
+
+```{r balance-table1, fig.cap="Imbalance before matching", echo=FALSE, message=FALSE}
+# covs_nr <- c('ext_pobres', 'log_rpc', 'p10_ricos_desigualdade', 'freq_escola_15_1', 'analfabetismo', 'log_renda', 'log_pop', 'percentual_de_execucao')
+# 
+# df_balance_check <- df_balancing_aux_se %>%
+#   dplyr::select(all_of(c(covs_nr, "indicator_muni_ot")))
+# 
+# matched_pre_check <- matched_pre %>%
+#   dplyr::select(all_of(c(covs_nr, "indicator_muni_ot")))
+#   
+# b_stats <- balance(df_balance_check, df_balance_check$indicator_muni_ot , matches_pre$cnts)
+# 
+# b_stats %>%
+#   gt()
+
+```
+
+```{r balance-plot1, fig.cap="Balance pre-matching before the project started.", echo=FALSE}
+print(pre_project_pre_matching_plot)
+```
+
+Figure \@ref(fig:balance-plot1) shows the huge imbalance before the matching strategy for the period before the project started and figure \@ref(fig:balance-plot2) shows the improvement in balance after the matching strategy.
+
+```{r balance-plot2, fig.cap="Balance post-matching before the project started.", echo=FALSE,}
+print(pre_project_post_matching_plot)
+```
+
+Next we show that balance was improved after the end of the project as well.Figure \@ref(fig:balance-plot3) and \@ref(fig:balance-plot4) presents balance before and after match for the data when treatment occurred.
+
+```{r balance-plot3, fig.cap="Balance pre-matching after the project started.", echo=FALSE}
+print(post_project_pre_matching_plot)
+```
+
+```{r balance-plot4, fig.cap="Balance post-matching after the project started.", echo=FALSE}
+print(post_project_post_matching_plot)
+```

### 2023-11-06 simec_analysis.R
failed analysis

@@ -1,0 +1,204 @@
+library(data.table)
+library(here)
+library(janitor)
+library(lubridate)
+library(readxl)
+library(tidyverse)
+library(gt)
+library(ipeadatar)
+library(munifacil)
+library(ribge)
+
+list.files(here("Dados"))
+simec <- fread(here("Dados", "simec 25-10-23 - simec.csv"), encoding = "UTF-8")
+glimpse(simec)
+
+# foz <- simec %>%
+#   clean_names() %>%
+#   dplyr::filter(grepl("Foz", municipio)) %>%
+#   mutate(data_da_ultima_vistoria_do_estado_ou_municipio  = ymd(data_da_ultima_vistoria_do_estado_ou_municipio))
+
+
+ot <- simec %>%
+  clean_names() %>%
+  dplyr::filter(!grepl("quadra", tolower(tipo_do_projeto)))
+                
+foz <- ot %>%
+  dplyr::filter(grepl("Foz", municipio)) %>%
+  mutate(data_da_ultima_vistoria_do_estado_ou_municipio  = ymd(data_da_ultima_vistoria_do_estado_ou_municipio))
+
+lista_cidades_ot <- c("Araucária", "Caçador", "Campo Mourão", "Cascavel", "Chapecó",
+                      "Foz do Iguaçu", "Goioerê", "Gravataí", "Guarapuava", "Imbituba", "Lajeado",
+                      "Limeira", "Palhoça", "Paranaguá", "Pelotas", "Ponta Grossa", "Santa Maria", 
+                      "São Francisco do Sul", "São José dos Campos", "Taubaté", "Uberlândia")
+
+df_cidades_ot <- data.frame(municipio = lista_cidades_ot, indicator_ot = 1)
+
+ot_cidades <- ot %>%
+  left_join(df_cidades_ot, by = "municipio")
+# tcu
+
+load(here("Dados","tcu_creches.RData"))
+load(here("Dados", "sit_obras_final.RData"))
+
+tdp <- fread(here("Dados", "sit_obras_final.csv"), encoding = "Latin-1")
+glimpse(tdp)
+
+tdp1 <- tdp %>%
+  dplyr::select(id, nome, municipio, uf, responsabilidade, logradouro,percentual_de_execucao, cancelada,
[…]

### 2023-11-06 bayesian_analysis.R
bayes

@@ -1,0 +1,246 @@
+## Bayesian propensity score
+
+library("rstan")
+library("arm")
+library("rstanarm")
+library("survey")
+library(broom)
+library(broom.mixed)
+# library(ggdag)
+library(MetBrewer)
+
+df_balancing_aux %>%
+  group_by(indicator_muni_ot,tipo_do_projeto ) %>%
+  summarise(n()) %>% View()
+
+df_balancing_aux1 <- df_balancing_aux %>%
+  mutate(tipo_do_projeto = ifelse(grepl("Espaço Educativo", tipo_do_projeto), 
+                                  "Espaço Educativo - x salas", tipo_do_projeto),
+         concluida_num = as.numeric(concluida))
+
+df_balancing_aux_se <- df_balancing_aux1 %>%
+  filter(uf.x %in% c("SP", "PR", "SP", "SC", "RS", "MG"))
+
+pre_dados <- df_balancing_aux %>%
+  dplyr::select(id, concluida) %>%
+  rename(concluida_pre = concluida) %>%
+  mutate(id = as.numeric(id))
+
+
+data_pos <- obras_fim_seg_fase %>%
+  mutate(municipio1 = tolower(iconv(municipio, "UTF-8",  "ASCII//TRANSLIT"))) %>%
+  inner_join(aux_muni1, by = join_by(municipio1  == name_muni1, uf == abbrev_state)) %>%
+  inner_join(ipea_final, by = join_by(code_muni == tcode)) %>%
+  mutate(perc_pea18 =pea18/populacao,
+         log_pop = log(populacao),
+         log_renda = log(rpc*populacao),
+         log_rpc = log(rpc)) %>%
+  inner_join(pre_dados, by = "id") %>%
+  dplyr::filter(concluida_pre == FALSE) %>%
+  mutate(concluida_num = as.numeric(concluida))
+
+
+df_balancing_aux_post_se <- data_pos %>%
+  filter(uf.x %in% c("SP", "PR", "SP", "SC", "RS", "MG"))
+  
+# these are the no redundancy covariates with and without state covariate
+covs.nr <- c('perc_pea18', 'ext_pobres', 'log_rpc', 'p10_ricos_desigualdade', 'freq_escola_15_1', 'analfabetismo',
+             'log_renda', 'log_pop', 'percentual_de_execucao', 'tipo_do_projeto')
+
+covs.nr.st <- c(covs.nr, "uf.x")
+
[…]

### 2023-11-06 Untitled/Untitled.Rmd
paper R&P

--- 2023-11-02 Scripts/paper.Rmd
@@
 ---
-title: "The Civil Society Organizations effect: A mixed-Methods analysis of bottom-up approaches in Brazilian public policy"
-date: "2023-10-26"
-output: bookdown::pdf_document2
-sansfont: Sans Serif
-fontsize: 12pt
+title: "The Civil Society Organizations effect: A mixed-Methods analysis of bottom-up approaches in Brazilian public policy."
+short: "The Civil Society Organizations effect"
+month: "`r format(Sys.Date(), '%m')`"
+year: "`r format(Sys.Date(), '%Y')`"
+keywords:
+  - accountability
+  - Civil Society Organizations
+  - mixed methods
+  - community-driven development
+  - public policy.
 author:
   - name: Manoel Galdino
-    affiliation: Universidade de São Paulo - Brazil.
-  - names: Juliana Sakai
+    firstname: Manoel
+    surname: Galdino
+    email: mgaldino@usp.br
+    affiliation: Universidade de São Paulo, Brazil
+  - name: Bianca Vaz Mondo
+    firstname: Bianca
+    surname: Mondo
+    affiliation: Government Transparency Institute - Germany
+  - name: Juliana Mari Sakai
+    firstname: Juliana
+    surname: Sakai
     affiliation: Transparência Brasil - Brazil
-  - names: Bianca Vaz Mondo
-    affiliation: Transparência Brasil - Brazil
-  - names: Natália Paiva
-    affiliation: Alandar Consulting - Brazil
-abstract: "This paper examines the effect of bottom-up accountability on public service delivery.
+  - name: Natália Paiva
+    firstname: Natália
+    surname: Paiva
+    affiliation: Alandar Consulting - Germany
+acknowledgements: |
+  We would like to thank all participants of project Obra Transparente, Vanda Medeiros and the team of Transparência Brasil who worked in the project or in evaluations of the project.
+The project was funded by an UNDEF grant, which we also thank.
+abstract: |
+  This paper examines the effect of bottom-up accountability on public service delivery.
 We differentiate between information-driven interventions and the mobilization and monitoring efforts of organized Civil Society Organizations (CSOs), and argue that the latter type of interventions can can drive significant policy change.
@@
 Our findings emphasize the importance of sustained, coordinated efforts by socially embedded CSOS.
-These efforts, involving direct engagement with municipal officials and ensuring that their complains cannot be ignored lead to more substantial outcomes when compared with citizens information-driven."
-keywords: "accountability, Civil Society Organizations, mixed methods, community-driven development, public policy."
+These efforts, involving direct engagement with municipal officials and ensuring that their complains cannot be ignored lead to more substantial outcomes when compared with citizens information-driven.
 bibliography: OT_paper.bib
+output: rticles::aea_article
 ---
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-```
 
@@
 ## Introduction
-
 Accountability is a crucial element in democratic systems, ensuring the efficient delivery of public services [@besley_2003; @cameron_2004; @odonnell_1998].
@@
 For the quantitative analysis, we use administrative data about construction works data by municipalities and socio-demographic data on municipalities.
-The questions asked in the survey as well the aggregate answered are presented in annex A.
+The questions asked in the survey as well the aggregate answered are presented in annex B.
 
@@
 
-# these are the no redundancy covariates with and without state covariate
-covs.nr <- c('perc_pea18', 'ext_pobres', 'log_rpc', 'p10_ricos_desigualdade', 'freq_escola_15_1', 'analfabetismo',
-             'log_renda', 'log_pop', 'percentual_de_execucao', 'tipo_do_projeto')
-
-covs.nr.st <- c(covs.nr, "uf.x")
-
 Table (insert ref number) summarizes the main results of the regression.

### 2023-11-06 Untitled/Untitled.tex
paper R&P

--- 2023-11-06 Untitled/Untitled.Rmd
@@
----
-title: "The Civil Society Organizations effect: A mixed-Methods analysis of bottom-up approaches in Brazilian public policy."
-short: "The Civil Society Organizations effect"
-month: "`r format(Sys.Date(), '%m')`"
-year: "`r format(Sys.Date(), '%Y')`"
-keywords:
-  - accountability
-  - Civil Society Organizations
-  - mixed methods
-  - community-driven development
-  - public policy.
-author:
-  - name: Manoel Galdino
-    firstname: Manoel
-    surname: Galdino
-    email: mgaldino@usp.br
-    affiliation: Universidade de São Paulo, Brazil
-  - name: Bianca Vaz Mondo
-    firstname: Bianca
-    surname: Mondo
-    affiliation: Government Transparency Institute - Germany
-  - name: Juliana Mari Sakai
-    firstname: Juliana
-    surname: Sakai
-    affiliation: Transparência Brasil - Brazil
-  - name: Natália Paiva
-    firstname: Natália
-    surname: Paiva
-    affiliation: Alandar Consulting - Germany
-acknowledgements: |
-  We would like to thank all participants of project Obra Transparente, Vanda Medeiros and the team of Transparência Brasil who worked in the project or in evaluations of the project.
-The project was funded by an UNDEF grant, which we also thank.
-abstract: |
-  This paper examines the effect of bottom-up accountability on public service delivery.
-We differentiate between information-driven interventions and the mobilization and monitoring efforts of organized Civil Society Organizations (CSOs), and argue that the latter type of interventions can can drive significant policy change.
-The study evaluates the effectiveness of the Obra Transparente project by Brazilian NGO Transparência Brasil, engaging 21 local CSOs in South and Southeast Brazil.
-Our findings emphasize the importance of sustained, coordinated efforts by socially embedded CSOS.
-These efforts, involving direct engagement with municipal officials and ensuring that their complains cannot be ignored lead to more substantial outcomes when compared with citizens information-driven.
-bibliography: OT_paper.bib
-output: rticles::aea_article
----
+% AER-Article.tex for AEA last revised 22 June 2011
+\documentclass[]{AEA}
 
-```{r package loads, message=F, echo=FALSE}
-library(data.table)
-library(here)
-library(janitor)
-library(lubridate)
-library(readxl)
-library(tidyverse)
-library(gt)
-library(ipeadatar)
-library(rstan)
-library(arm)
-library(rstanarm)
-library(survey)
-library(broom)
-library(broom.mixed)
-library(MetBrewer)
-```
+% The mathtime package uses a Times font instead of Computer Modern.
+% Uncomment the line below if you wish to use the mathtime package:
+%\usepackage[cmbold]{mathtime}
+% Note that miktex, by default, configures the mathtime package to use commercial fonts
+% which you may not have. If you would like to use mathtime but you are seeing error
+% messages about missing fonts (mtex.pfb, mtsy.pfb, or rmtmi.pfb) then please see
+% the technical support document at http://www.aeaweb.org/templates/technical_support.pdf
+% for instructions on fixing this problem.
 
-```{r loading construction data,  message=FALSE, echo=FALSE}
+% Note: you may use either harvard or natbib (but not both) to provide a wider
+% variety of citation commands than latex supports natively. See below.
 
-# load(here("obra_transparente", "Dados", "obras_inicio_projeto.Rdata"))
-# load(here("obra_transparente", "Dados", "obras_fim_seg_fase.Rdata"))
+% Uncomment the next line to use the natbib package with bibtex
+\usepackage{natbib}
 
-load(here("Dados", "obras_inicio_projeto.Rdata"))
-load(here("Dados", "obras_fim_seg_fase.Rdata"))
+% Uncomment the next line to use the harvard package with bibtex
+%\usepackage[abbr]{harvard}
 
-# simec23 <- fread(here("obra_transparente", "Dados", "simec 25-10-23 - simec.csv"), encoding = "UTF-8")
-simec23 <- fread(here("Dados", "simec 25-10-23 - simec.csv"), encoding = "UTF-8")
+% This command determines the leading (vertical space between lines) in draft mode
+% with 1.5 corresponding to "double" spacing.
+\draftSpacing{1.5}
 
-# load(here("obra_transparente", "Dados", "obras_fim_seg_fase.Rdata"))
+% tightlist command for lists without linebreak
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
 
-load(here("Dados", "obras_fim_seg_fase.Rdata"))
+% Pandoc citation processing
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newlength{\cslentryspacingunit} % times entry-spacing
+\setlength{\cslentryspacingunit}{\parskip}
+% for Pandoc 2.8 to 2.10.1
+\newenvironment{cslreferences}%
+  {}%
+  {\par}
+% For Pandoc 2.11+
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+  \let\oldpar\par
+  \def\par{\hangindent=\cslhangindent\oldpar}
+  \fi
+  % set entry spacing
+  \setlength{\parskip}{#2\cslentryspacingunit}
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
-df_cidades_ot <- read_excel(here("Dados", "situacao obras_atual.xlsx"), 
-                                           sheet = "SIMEC-Mai17", skip = 1) %>%
-  clean_names() %>%
-  filter(!is.na(id)) %>%
-  dplyr::select(id, municipio, uf, situacao2, levant_os_jun_17) %>%
-  mutate(indicator_ot = 1)
-```
+\usepackage{booktabs}
+\usepackage{caption}
+\usepackage{longtable}
+\usepackage{colortbl}
+\usepackage{array}
 
-```{r loading-processing ipea data,  message=FALSE, echo=FALSE, cache=TRUE}
-aux_muni <- geobr::lookup_muni(code_muni = "all") %>%
-  dplyr::select(-c(name_state, name_intermediate))
+\usepackage{hyperref}
 
-ipea_idhm <- ipeadatar::ipeadata("ADH_IDHM") %>%
-  dplyr::filter(date > "2001-01-1" & as.character(uname) == "Municipality") %>%
-  rename(idhm = value)
+\begin{document}
 
-ipea_pea18 <- ipeadatar::ipeadata("ADH_PEA18M")  %>%
-  dplyr::filter(date > "2001-01-1" & as.character(uname) == "Municipality") %>%
-  rename(pea18 = value)
+\title{The Civil Society Organizations effect: A mixed-Methods analysis
+of bottom-up approaches in Brazilian public policy.}
+\shortTitle{The Civil Society Organizations effect}
+% \author{Author1 and Author2\thanks{Surname1: affiliation1, address1, email1.
+% Surname2: affiliation2, address2, email2. Acknowledgements}}
 
-ipea_ext_pobres <- ipeadatar::ipeadata("ADH_PIND")  %>%
-  dplyr::filter(date > "2001-01-1" & as.character(uname) == "Municipality") %>%
-  rename(ext_pobres = value)
+\author{
+  Manoel Galdino\\
+  Bianca Vaz Mondo\\
+  Juliana Mari Sakai\\
+  Natália Paiva\thanks{
+  Galdino: Universidade de São Paulo,
+Brazil, \href{mailto:mgaldino@usp.br}{mgaldino@usp.br}.
+  Mondo: Government Transparency Institute - Germany, \href{mailto:}{}.
+  Sakai: Transparência Brasil - Brazil, \href{mailto:}{}.
+  Paiva: Alandar Consulting - Germany, \href{mailto:}{}.
+  We would like to thank all participants of project Obra Transparente,
+  Vanda Medeiros and the team of Transparência Brasil who worked in the
+  project or in evaluations of the project. The project was funded by an
+  UNDEF grant, which we also thank.
+}
+}
 
-ipea_ext_pobres_neg <- ipeadatar::ipeadata("ADH_PIND_NEG")  %>%
-  dplyr::filter(date > "2001-01-1" & as.character(uname) == "Municipality") %>%
-  rename(ext_pobres_negros = value)
+\date{\today}
+\pubMonth{11}
+\pubYear{2023}
+\pubVolume{}
+\pubIssue{}
+\JEL{}
+\Keywords{accountability, Civil Society Organizations, mixed
+methods, community-driven development, public policy.}
 
-ipea_rpc <- ipeadatar::ipeadata("ADH_RDPC")  %>%
-  dplyr::filter(date > "2001-01-1" & as.character(uname) == "Municipality") %>%
-  rename(rpc = value)
+\begin{abstract}
+This paper examines the effect of bottom-up accountability on public
+service delivery. We differentiate between information-driven
+interventions and the mobilization and monitoring efforts of organized
+Civil Society Organizations (CSOs), and argue that the latter type of
+interventions can can drive significant policy change. The study
+evaluates the effectiveness of the Obra Transparente project by
+Brazilian NGO Transparência Brasil, engaging 21 local CSOs in South and
+Southeast Brazil. Our findings emphasize the importance of sustained,
+coordinated efforts by socially embedded CSOS. These efforts, involving
+direct engagement with municipal officials and ensuring that their
+complains cannot be ignored lead to more substantial outcomes when
+compared with citizens information-driven.
+\end{abstract}
 
-ipea_rpc_mulheres <- ipeadatar::ipeadata("ADH_RDPC_MUL")  %>%
-  dplyr::filter(date > "2001-01-1" & as.character(uname) == "Municipality") %>%
-  rename(rpc_mulheres = value)
+\maketitle
 
-ipea_rpc_negros <- ipeadatar::ipeadata("ADH_RDPC_NEG")  %>%
-  dplyr::filter(date > "2001-01-1" & as.character(uname) == "Municipality") %>%
-  rename(rpc_negros = value)
+\hypertarget{introduction}{%
+\subsection{Introduction}\label{introduction}}
 
-ipea_ext_prop_pobres <- ipeadatar::ipeadata("ADH_PMPOB")  %>%
-  dplyr::filter(date > "2001-01-1" & as.character(uname) == "Municipality") %>%
-  rename(ext_prop_pobres = value)
+Accountability is a crucial element in democratic systems, ensuring the
+efficient delivery of public services (Besley and Ghatak 2003; Cameron
+2004; O'donnell 1998). Initially defined as the process of holding
+authorities responsible for their actions (Mulgan 2000; O'Loughlin
+1990), the literature has since broadened to include various oversight
+mechanisms for politicians and the bureaucracy. Some authors focus on
+formal institutions (O'donnell 2003; Kenney 2003), known as horizontal
+accountability, while others examine how politicians respond to voters,
+the media, and civil society organizations (Bertelli and Van Ryzin 2020;
+Relly 2012; Paul 1992), referred to as vertical accountability.
 
-ipea_10p_ricos_desigualdade <- ipeadatar::ipeadata("ADH_PREN10RICOS")  %>%
-  dplyr::filter(date > "2001-01-1" & as.character(uname) == "Municipality") %>%
-  rename(p10_ricos_desigualdade = value)
+Recent studies have highlighted the role of ``bottom-up accountability''
+(also known as social accountability, Fox, 2015), in which citizens
+receive information about public policies and use it for social control.
+The pioneering study `Power to the People' (Björkman and Svensson 2009),
+which demonstrated the impact of local community engagement in
+monitoring the provision of health services, inspired subsequent
+literature that tested similar interventions in different contexts.
 
-ipea_freq_escola_15_17 <- ipeadatar::ipeadata("ADH_T_FREQ15A17")  %>%
-  dplyr::filter(date > "2001-01-1" & as.character(uname) == "Municipality") %>%
-  rename(freq_escola_15_1 = value)
+The mechanism would works like this: Constituents have firsthand
+information about the outcomes of local policies, giving citizens
+incentives to combat corruption that directly affects them. Since
+policymakers are sensitive to social feedback from their own communities
+(Serra 2012), bottom-up accountability could influence local public
+policies
 
-ipea_analfabetismo <- ipeadatar::ipeadata("ADH_T_ANALF15M")  %>%
-  dplyr::filter(date > "2001-01-1" & as.character(uname) == "Municipality") %>%
-  rename(analfabetismo = value)
+However, a series of recent studies have raised doubts about the
+effectiveness of ``bottom-up accountability'' strategies based on
+interventions aimed at increasing the monitoring capacity of ordinary
+citizens regarding public policies (Freire, Galdino, and Mignozzetti
+2020; Raffler, Posner, and Parkerson 2019; Fox 2015).
 
-pop2010 <- ribge::habitantes2010 %>%
-  mutate(tcode = as.integer(paste0(codigo_uf, codigo_munic)))
+Most of the interventions are tactical, in the sense that they involve
+providing information to non-organized citizens through technological
+means, such as sending SMS messages or delivering information via mobile
+apps. One key advantage of such interventions is that, if successful,
+they could rapidly reach thousands of people at a low cost, potentially
+having a significant impact when scaled to an entire country or even
+multiple countries.
 
-ipea_final <- ipea_idhm %>%
-  inner_join(aux_muni, by = join_by(tcode == code_muni)) %>%
-  inner_join(ipea_pea18, by = "tcode") %>%
-  inner_join(ipea_ext_pobres, by = "tcode") %>%
-  inner_join(ipea_rpc, by = "tcode") %>%
-  inner_join(ipea_ext_prop_pobres, by = "tcode") %>%
-  inner_join(ipea_10p_ricos_desigualdade, by = "tcode") %>%
-  inner_join(ipea_freq_escola_15_17, by = "tcode") %>%
-  inner_join(ipea_analfabetismo, by = "tcode") %>%
-  inner_join(pop2010, by = "tcode") %>%
-  dplyr::select(-contains("date")) %>%
-  dplyr::select(-contains("uname")) %>%
-  dplyr::select(-starts_with("code"))
-```
+The disappointing results have cast doubts on the effectiveness of the
+bottom-up accountability strategy for improving the delivery of public
+services, reducing corruption, and enhancing government efficiency. Some
+authors (Fox 2015; Ankamah 2019) have suggested that social
+accountability without ``teeth,'' defined as the government's capacity
+to respond to citizens' voices, has limited impact.
 
-```{r processing data, echo=FALSE,  message=FALSE}
+While it has been consistently shown that tactical interventions have,
+at best, a small, limited impact, it doesn't mean that voice without
+``teeth'' is an ineffective strategy. The argument in this study is that
+not all types of interventions that promote citizen's voices are the
+same.
 
-obras_inicio_projeto_ot <- obras_inicio_projeto %>%
-  left_join(df_cidades_ot, by=join_by("municipio", "uf", "id"))
+We argue that we need to differentiate between information-led tactical
+interventions and active mobilization and monitoring by Civil Society
+Organizations (CSOs). By their very nature, established CSOs are
+embedded in society and politics and can have a substantial impact on
+policy change (Gong and Xiao 2017; Joshi and Houtzager 2012).
 
-obras_inicio_projeto_ot <- obras_inicio_projeto_ot %>%
-  mutate(concluida = grepl("Concluída", situacao))
+The paper argues that a missing feature in most of the literature is
+that these interventions should target CSOs instead of individual
+citizens, and ensure that the intervention enhances the ability of the
+CSOs to overcome their collective action problem (Mattoni and Odilla
+2021; Odilla 2023).
 
-aux_indicator_ot <- df_cidades_ot %>%
-  distinct(municipio, uf) %>%
-  mutate(indicator_muni_ot = 1)
+The present paper provides evidence supporting this argument. We
+reassess the evidence provided by Freire, Galdino, and Mignozzetti
+(2020), considering a different intervention than the one they
+evaluated. They provided experimental evidence that a mobile app (Tá de
+Pé) made available to citizens did not improve the delivery of school
+and nursery construction works. Here, we assess the efficacy of a sister
+project, called ``Obra Transparente,'' also developed by the Brazilian
+NGO Transparência Brasil. This project targeted 21 local Civil Society
+Organizations in 21 municipalities in the South and Southeast regions of
+Brazil, with the aim of improving access to education by addressing
+mismanagement and delays in the construction of public schools and
+nurseries. Both projects were developed in parallel, with similar goals
+but achieved strikingly different results.
 
-obras_inicio_projeto_ot <- obras_inicio_projeto_ot %>%
-  mutate(indicator_ot = ifelse(is.na(indicator_ot), 0, indicator_ot)) %>%
-  left_join(aux_indicator_ot, by = join_by("municipio", "uf")) %>%
-  mutate(indicator_muni_ot = ifelse(is.na(indicator_muni_ot), 0, indicator_muni_ot))
+The argument in the present study is that not all types of interventions
+that promote citizens' voice are the same. We argue that we need to
+differentiate between information-led tactical interventions and active
+mobilization and monitoring by Civil Society Organizations. By their
+very nature, established CSOs are embedded in society and politics and,
+as such, can have teeth of their own (Gong and Xiao 2017; Joshi and
+Houtzager 2012). It may be only that we need mobilization by organized
+civil society, in a structured way, for civil society voices to be heard
+with ``teeth''. Some studies have suggested that a key feature of
+successful change in public policies is the pressure of collectively
+organized agents (Mattoni and Odilla 2021; Odilla 2023). Collective
+action is a hard problem to be overcome and creating CSOs is one way to
+achieve this. We argue in this paper that a missing features of the
+tactical interventions assessed in most of the literature is that they
+should target CSOs instead of individual citizens, and make sure that
+the intervention increases the ability of the CSOs to attract and
+overcome their collective action problem.
 
-antes_projeto <- obras_inicio_projeto_ot %>%
-  dplyr::filter(uf %in% c("SP", "PR", "SP", "SC", "RS", "MG")) %>%
-  group_by(indicator_muni_ot, concluida) %>%
-  summarise(contagem = n()) %>%
-  mutate(total = sum(contagem),
-         perc = round(contagem/total, 2))
+The ``Obra Transparente'' project consisted of developing a network of
+local CSOs to share experiences and information on monitoring the
+construction works, providing a technical support system for monitoring
+the process of constructing public schools and nurseries, and training
+on monitoring biddings, contracts, and constructions of public schools
+and nurseries.
 
-antes_projeto <- antes_projeto %>%
-  dplyr::filter(concluida == TRUE) %>%
-  dplyr::select(-c(concluida, contagem, total)) %>%
-  ungroup()
+Our findings emphasize that it is the sustained and concerted efforts of
+organized civil society, such as repeated meetings with municipal
+officials, persistent follow-ups, and on-site visits, that lead to more
+significant outcomes, in contrast to interventions providing information
+and generating sporadic citizen actions.
 
-obras_fim_seg_fase <- obras_fim_seg_fase %>%
-  mutate(concluida = as.numeric(grepl("Concluída", situacao)),
-         id = as.numeric(id)) %>%
-  left_join(df_cidades_ot, by=join_by("municipio", "uf", "id")) %>%
-  mutate(indicator_ot = ifelse(is.na(indicator_ot), 0, indicator_ot)) %>%
-  left_join(aux_indicator_ot, by = join_by("municipio", "uf")) %>%
-  mutate(indicator_muni_ot = ifelse(is.na(indicator_muni_ot), 0, indicator_muni_ot))
+\hypertarget{the-project-obra-transparente}{%
+\subsection{The project Obra
+Transparente}\label{the-project-obra-transparente}}
 
-depois_projeto <- obras_fim_seg_fase %>%
-  dplyr::filter(uf %in% c("SP", "PR", "SP", "SC", "RS", "MG")) %>%
-  group_by(indicator_muni_ot, concluida) %>%
-  summarise(contagem = n()) %>%
-  mutate(total = sum(contagem),
-         perc = round(contagem/total, 2))
+The project was initiated in May 2017 by Transparência Brasil (TB) to
+address delays in school and nursery construction projects funded by the
+federal government and carried out by municipal governments. TB
+partnered with Observatório Social do Brasil, an NGO coordinating a
+network of local (municipality-based) NGOs, to develop and disseminate a
+standardized methodology for local government oversight. The Obra
+Transparente project concluded on June 30, 2019.
 
-depois_projeto <- depois_projeto %>%
-  dplyr::filter(concluida == TRUE) %>%
-  dplyr::select(-c(concluida, contagem, total)) %>%
-  ungroup()
+During the project, TB monitored construction plans, resource
+allocation, procurement processes, and work execution. They also tracked
+the monitoring and accountability procedures conducted by government
+bodies to ensure adherence to technical and legal guidelines.
 
-```
+Transparência Brasil collaborated with the Controladoria Geral da União,
+a federal government agency responsible for overseeing federal public
+spending, to develop training materials and provide courses to a network
+of local CSOs. Courses reached 270 participants, with a mix of online
+and in-person modules over several weeks along the duration of the
+project. These modules covered topics related to public bidding,
+construction monitoring, and contracting procedures.
 
-## Introduction
-Accountability is a crucial element in democratic systems, ensuring the efficient delivery of public services [@besley_2003; @cameron_2004; @odonnell_1998].
-Initially defined as the process of holding authorities responsible for their actions [@mulgan_2000; @oloughlin_1990], the literature has since broadened to include various oversight mechanisms for politicians and the bureaucracy.
-Some authors focus on formal institutions [@odonnell_2003; @kenney_2003], known as horizontal accountability, while others examine how politicians respond to voters, the media, and civil society organizations [@bertelli_2020; @relly_2012; @paul_1992], referred to as vertical accountability.
+\hypertarget{research-design-and-methods}{%
+\subsection{Research Design and
+Methods}\label{research-design-and-methods}}
 
-Recent studies have highlighted the role of "bottom-up accountability" (also known as social accountability, Fox, 2015), in which citizens receive information about public policies and use it for social control.
-The pioneering study 'Power to the People' [@bjorkman_2009], which demonstrated the impact of local community engagement in monitoring the provision of health services, inspired subsequent literature that tested similar interventions in different contexts.
+We employ an integrated inference approach (Humphreys and Jacobs 2023)
+to analyze qualitative data within the framework of causal queries. As
+this approach is relatively innovative within qualitative research,
+we'll provide a comprehensive explanation.
 
-The mechanism would works like this: Constituents have firsthand information about the outcomes of local policies, giving citizens incentives to combat corruption that directly affects them.
-Since policymakers are sensitive to social feedback from their own communities [@serra_2012], bottom-up accountability could influence local public policies
+The methodology outlined by (Humphreys and Jacobs 2023) mandates the
+creation of a causal model encoded in Directed Acyclic Graphs (DAGs), a
+framework developed by Pearl (2009). Bayesian inference, recently
+promoted in qualitative data analysis (Fairfield and Charman 2022),
+serves as the foundation for deriving quantitative estimates for causal
+queries constructed using the proposed DAG.
 
-However, a series of recent studies have raised doubts about the effectiveness of "bottom-up accountability" strategies based on interventions aimed at increasing the monitoring capacity of ordinary citizens regarding public policies [@freire_etal2020; @raffler_etal2019; @fox_2015].
+In our current study, we investigate the impact of Civil Society
+Organization (CSO) monitoring on two aspects: the completion of
+construction works and the rectification of issues and irregularities
+found in construction facilities. Formally, the first research question
+relates to a causal relationship between monitoring (M) and completion
+(C), indicated by the DAG (M -\textgreater{} C). The second research
+query delves into whether monitoring (M) causes the fixing of issues
+(F), or the (DAG M -\textgreater{} F). To accommodate the qualitative
+nature of our variables, we treat them as binary.
 
-Most of the interventions are tactical, in the sense that they involve providing information to non-organized citizens through technological means, such as sending SMS messages or delivering information via mobile apps.
-One key advantage of such interventions is that, if successful, they could rapidly reach thousands of people at a low cost, potentially having a significant impact when scaled to an entire country or even multiple countries.
+Within this approach, a given DAG allows us to pose causal queries,
+which can yield estimands like the average treatment effect (ATE) or
+types, which we explain below. Types are the focal estimands in our
+study.
 
-The disappointing results have cast doubts on the effectiveness of the bottom-up accountability strategy for improving the delivery of public services, reducing corruption, and enhancing government efficiency.
-Some authors [@fox_2015; @ankamah_2019] have suggested that social accountability without "teeth," defined as the government's capacity to respond to citizens' voices, has limited impact.
+This approach hinges on the notion that each case can belong to a
+specific type, denoting different causal relationships. In our current
+investigation, let's focus on the (M -\textgreater{} C) DAG. To clarify
+what a type is, we'll employ the Potential Outcomes (PO) notation (Rubin
+2005; Imbens and Rubin 2015). Within the PO framework, every case has
+two potential outcomes: one when the treatment (in this case, CSO
+monitoring, M) is absent and another when the treatment is present. In
+simplified notation, if a city only completes construction works in the
+absence of monitoring, we express this in PO notation as C(1) = 0. If
+there is no monitoring (M = 0) and no completion, then we write C(0) =
+0. Conversely, if there is monitoring (M = 1) and completion, we write
+C(1) = 1, and C(0) = 1 if there is completion without monitoring.
 
-While it has been consistently shown that tactical interventions have, at best, a small, limited impact, it doesn't mean that voice without "teeth" is an ineffective strategy.
-The argument in this study is that not all types of interventions that promote citizen's voices are the same.
+We can categorize a city into one of four types based on what happens
+when they do or do not receive the treatment (monitoring): Adverse (type
+``a''): A city that completes construction only if it doesn't receive
+the treatment (monitoring). Beneficial (type ``b''): A city that
+completes construction only if there is monitoring. Chronic (type
+``c''): Cities that never complete construction, regardless of
+monitoring. Destined (type ``d''): Cities that always complete
+construction, regardless of monitoring. The PO notation is instrumental
+here, as we can rewrite the types based on the following notation: Type
+``a'' is one in which the potential outcome is 0 if M = 1 and 1 if M =
+0. Therefore, we express it as \(\theta_{10}\), where the first
+subscript denotes the outcome when the treatment is 0, and the second
+denotes the outcome when the treatment is 1. We employ analogous
+notation for all other types: \(b = \theta_{01}\), \(c = \theta_{00}\),
+and \(d = \theta_{11}\).
 
-We argue that we need to differentiate between information-led tactical interventions and active mobilization and monitoring by Civil Society Organizations (CSOs).
-By their very nature, established CSOs are embedded in society and politics and can have a substantial impact on policy change [@gong_2017; @joshi_2012].
+When analyzing a case study of what happened in a given municipality, we
+can use the data to answer, for example, the following causal query:
+what is the probability that the city if type ``b'', i.e, benefits from
+the monitoring and would have not completed the construction work if not
+for the monitoring of the local CSO?
 
-The paper argues that a missing feature in most of the literature is that these interventions should target CSOs instead of individual citizens, and ensure that the intervention enhances the ability of the CSOs to overcome their collective action problem [@mattoni_2021; @odilla_2023].
+The advantage of this approach is that all assumptions and restrictions
+imposed to identify the parameters of interest are transparent. It also
+allows the user to update posterior probabilities based on qualitative
+data. One reason for this is that with Bayesian inference, we do not
+need to rely on asymptotic theory to make inferences. Thus, there is no
+need for a large-n study. Formally speaking, one can make causal queries
+without any data, based only on prior probabilities for the parameters.
+Obviously the answer to such causal queries will be vague enough to be
+almost useless. But the point is that, once you have a prior and a
+causal model, encoded in a DAG, you can answer causal queries. As one
+collects data (any data, be it qualitative or quantitative), one can
+make assumptions about the nature of the data (such as the Data
+Generating Process), and then update the model and provide new answers
+to the causal queries, which hopefully will be informative enough to be
+useful for the task at hand. And even when the model or hypothesis is
+not completely identified, it can be partially identified (Manski 2003),
+which is still a useful answer to causal queries.
 
-The present paper provides evidence supporting this argument.
-We reassess the evidence provided by @freire_etal2020, considering a different intervention than the one they evaluated.
-They provided experimental evidence that a mobile app (Tá de Pé) made available to citizens did not improve the delivery of school and nursery construction works.
-Here, we assess the efficacy of a sister project, called "Obra Transparente," also developed by the Brazilian NGO Transparência Brasil.
-This project targeted 21 local Civil Society Organizations in 21 municipalities in the South and Southeast regions of Brazil, with the aim of improving access to education by addressing mismanagement and delays in the construction of public schools and nurseries.
-Both projects were developed in parallel, with similar goals but achieved strikingly different results.
+\hypertarget{data}{%
+\subsection{Data}\label{data}}
 
-The argument in the present study is that not all types of interventions that promote citizens' voice are the same.
-We argue that we need to differentiate between information-led tactical interventions and active mobilization and monitoring by Civil Society Organizations.
-By their very nature, established CSOs are embedded in society and politics and, as such, can have teeth of their own [@gong_2017; @joshi_2012].
-It may be only that we need mobilization by organized civil society, in a structured way, for civil society voices to be heard with “teeth”.
-Some studies have suggested that a key feature of successful change in public policies is the pressure of collectively organized agents [@mattoni_2021; @odilla_2023].
-Collective action is a hard problem to be overcome and creating CSOs is one way to achieve this.
-We argue in this paper that a missing features of the tactical interventions assessed in most of the literature is that they should target CSOs instead of individual citizens, and make sure that the intervention increases the ability of the CSOs to attract and overcome their collective action problem.
+The evidence gathered is primarily based on documented reports collected
+by Transparência Brasil and produced by the local OSBs over the course
+of the project. We also use evidence collected on semi-structured
+interviews and an online survey with representatives of the 21 CSOs
+conducted by an independent evaluator of the project. For the
+quantitative analysis, we use administrative data about construction
+works data by municipalities and socio-demographic data on
+municipalities. The questions asked in the survey as well the aggregate
+answered are presented in annex B.
 
-The "Obra Transparente" project consisted of developing a network of local CSOs to share experiences and information on monitoring the construction works, providing a technical support system for monitoring the process of constructing public schools and nurseries, and training on monitoring biddings, contracts, and constructions of public schools and nurseries.
+\hypertarget{case-studies}{%
+\subsection{Case Studies}\label{case-studies}}
 
-Our findings emphasize that it is the sustained and concerted efforts of organized civil society, such as repeated meetings with municipal officials, persistent follow-ups, and on-site visits, that lead to more significant outcomes, in contrast to interventions providing information and generating sporadic citizen actions.
+\hypertarget{delivery-of-the-construction-works}{%
+\subsubsection{Delivery of the construction
+works}\label{delivery-of-the-construction-works}}
 
-## The project Obra Transparente
+In our first case study, we highlight an impressive achievement in
+ensuring the completion of construction work. In Taubaté, four
+construction projects were underway, which the local OSB began
+monitoring as part of Obra Transparente. By the project's conclusion,
+their efforts played a crucial role in facilitating the successful
+delivery of these schools and nurseries to the city, ensuring they were
+ready for use in the field of education
 
-The project was initiated in May 2017 by Transparência Brasil (TB) to address delays in school and nursery construction projects funded by the federal government and carried out by municipal governments.
-TB partnered with Observatório Social do Brasil, an NGO coordinating a network of local (municipality-based) NGOs, to develop and disseminate a standardized methodology for local government oversight.
-The Obra Transparente project concluded on June 30, 2019.
+To put in perspective what was accomplished regarding the completion of
+all four projects, by the end of the project, of all 135 construction
+works planned for all 21 municipalities, only 25 were effectively
+delivered, a 18.5\% delivery rate. In Taubaté, before the monitoring by
+the local CSO, the delivery rate was zero. After that, the delivery rate
+was 100\% and one of the construction work was a previously paralyzed
+construction. According to a report by Transparência Brasil (Coelho,
+Galdino, and Sakai 2021), out of 771 stalled construction projects that
+were eventually completed, over 50\% of them took more than two years to
+be delivered and 25\% took three years or more. As we can see, the odds
+were against finishing the construction works.
 
-During the project, TB monitored construction plans, resource allocation, procurement processes, and work execution.
-They also tracked the monitoring and accountability procedures conducted by government bodies to ensure adherence to technical and legal guidelines.
+The local CSO monitoring the construction work in Taubaté did one of the
+best jobs among all 21 municipalities covered in the project. In fact,
+it was mostly the work of a single volunteer with support from the local
+OSB and Transparência Brazil throughout the project. She monitored four
+ongoing construction works on a periodic basis, she was very
+knowledgeable and insistent in demanding response from contractors and
+the local government. To give a single example of the quality of the
+social monitoring going on, in an email sent on 17th January of 2018 to
+the local government, the local OSB volunteer wrote: ``Fazendinha
+Daycare: a. construction log verified. There have been a few more
+construction workers on the site since December 15, 2017, but not
+enough, especially considering the extensive amount of work to be
+completed by the new delivery date in April 2018. b. (\ldots). c.~Lack
+of roof sealing, leading to water entering the classrooms (a situation
+that already existed on November 14, 2017)\ldots{}'' . She was by far
+the most knowledgeable and zealous volunteer of the whole project.
 
-Transparência Brasil collaborated with the Controladoria Geral da União, a federal government agency responsible for overseeing federal public spending, to develop training materials and provide courses to a network of local CSOs.
-Courses reached 270 participants, with a mix of online and in-person modules over several weeks along the duration of the project.
-These modules covered topics related to public bidding, construction monitoring, and contracting procedures.
+All of the construction works were effectively finished and delivered by
+the end of the project, although overdue. One of them, a resumption of a
+then halted construction work, was delivered 2 months overdue. The
+remaining three were further delayed, but no amendments were made on
+prices, only deadlines.
 
-## Research Design and Methods
+From a causal perspective, we are interested in what is called
+case-level causal attribution (Humphreys and Jacobs 2023), i.e, did the
+monitoring cause the delivery of the construction works? In other words,
+we are conditioning on the fact that M = 1 and C = 1, which constrains
+the possible types for Taubaté to be \(\theta^C_{1,1}\) ou
+\(\theta^C_{0,1}\). Assuming a simple model in which CSO monitoring
+causes the completion of works (M -\textgreater{} C), and with the eight
+within-case instances, we do the causal query. Our stimand of interest
+is the probability that Taubaté is a type \(\theta^D_{10}\).
 
-We employ an integrated inference approach [@humphreys_2023] to analyze qualitative data within the framework of causal queries.
-As this approach is relatively innovative within qualitative research, we'll provide a comprehensive explanation.
+Assuming uniform priors, the probability that Taubaté is a type
+\(\theta^D_{10}\), i.e, it is a city in which the treatment has a
+positive effect is 65\%, with 95\% credibility interval around {[}23\%,
+95\%{]}. As we can see, a wide interval, due to the low sample size, and
+yet, a positive effect nonetheless with 95\% of certainty.
 
-The methodology outlined by [@humphreys_2023] mandates the creation of a causal model encoded in Directed Acyclic Graphs (DAGs), a framework developed by Pearl (2009).
-Bayesian inference, recently promoted in qualitative data analysis [@fairfield_2022], serves as the foundation for deriving quantitative estimates for causal queries constructed using the proposed DAG.
+What are the assumptions behind such a result? The main one is that we
+modeled the monitoring (the treatment) as-if random, which is obviously
+not true. The mere passage of time causes an increased probability of
+delivery of a construction work. We can also imagine other possible
+confounds. The way to model it in a DAG is to add an arrow from M to C
+and vice-versa (M \textless-\textgreater{} C). Now, the estimand of
+interest depends on the probability of the treatment (monitoring)
+causing also the outcome (Average Treatment Effect, ATE). We will not
+detail the derivation of the new stimand here (you can consult annex B),
+but the idea is similar to before: we are interested in the type of city
+in which there is a causal effect of the monitoring on the completion of
+a construction works of school and/or nurseries. The mean probability of
+Taubaté being of this type, assuming the model is true is 43\%, with
+95\% credibility intervals around {[}9\%, 80\%{]}. The interval is wider
+because we added the uncertainty of confounding. Nonetheless, it is
+unlikely that the positive effect found in the observational data is
+driven only due to the confounding variables.
 
-In our current study, we investigate the impact of Civil Society Organization (CSO) monitoring on two aspects: the completion of construction works and the rectification of issues and irregularities found in construction facilities.
-Formally, the first research question relates to a causal relationship between monitoring (M) and completion (C), indicated by the DAG (M -> C).
-The second research query delves into whether monitoring (M) causes the fixing of issues (F), or the (DAG M -> F).
-To accommodate the qualitative nature of our variables, we treat them as binary.
+\hypertarget{preventing-problems-before-projects-started}{%
+\subsubsection{Preventing problems before projects
+started}\label{preventing-problems-before-projects-started}}
 
-Within this approach, a given DAG allows us to pose causal queries, which can yield estimands like the average treatment effect (ATE) or types, which we explain below.
-Types are the focal estimands in our study.
+The local OSB monitoring in Auraucária story is one when oversight
+arrives at the right moment to prevent a costly government procurement.
 
-This approach hinges on the notion that each case can belong to a specific type, denoting different causal relationships.
-In our current investigation, let's focus on the (M -> C) DAG.
-To clarify what a type is, we'll employ the Potential Outcomes (PO) notation [@rubin_2005; @imbens_2015].
-Within the PO framework, every case has two potential outcomes: one when the treatment (in this case, CSO monitoring, M) is absent and another when the treatment is present.
-In simplified notation, if a city only completes construction works in the absence of monitoring, we express this in PO notation as C(1) = 0.
-If there is no monitoring (M = 0) and no completion, then we write C(0) = 0.
-Conversely, if there is monitoring (M = 1) and completion, we write C(1) = 1, and C(0) = 1 if there is completion without monitoring.
+In 2017, the Brazilian municipality of Araucária conducted bidding
+processes seeking to hire companies to build three nurseries. The
+project sent technical experts to the 3 planned construction sites,
+together with volunteers from the local Observatório, to check whether
+plans were consistent with the physical conditions observed on site. The
+experts' assessment was that high-cost contention walls included in the
+construction plans were unnecessary or could be replaced by low-cost
+solutions through adjustments. Originally, the contention walls would
+cost R\$ 1,577,338.57 (US\$ 419,504.9, at the nominal exchange rate in
+2019). The analysis was first directed to the local administration,
+suggesting changes to the construction plans, which were rejected. The
+bidding processes went on as initially planned. Subsequently, the
+experts' findings were submitted to the Brazilian Supreme Audit
+Institution, Tribunal de Contas da União (TCU), by Transparência Brasil
+and Observatório Social do Brazil (see annex 1). TCU recommended that
+the bidding process should be redone, and construction plans were to be
+redesigned, with more cost-effective solutions for the contention walls.
+In the new bidding process, their cost plummeted to R\$ 416,883.17 (USD
+110,873.2), a reduction of USD 308,631.7 --- or 74\% less. To give a
+sense of the impact on the city budget, the amount saved on these three
+constructions alone represents about 3\% of all capital investments of
+Araucária in 2018. In short, in a single municipality, the project
+resulted in savings higher than the cost of the entire project funded by
+the grantee UNDEF (US\$ 220,000.00).
 
-We can categorize a city into one of four types based on what happens when they do or do not receive the treatment (monitoring):
-Adverse (type "a"): A city that completes construction only if it doesn't receive the treatment (monitoring).
-Beneficial (type "b"): A city that completes construction only if there is monitoring.
-Chronic (type "c"): Cities that never complete construction, regardless of monitoring.
-Destined (type "d"): Cities that always complete construction, regardless of monitoring.
-The PO notation is instrumental here, as we can rewrite the types based on the following notation: Type "a" is one in which the potential outcome is 0 if M = 1 and 1 if M = 0.
-Therefore, we express it as $\theta_{10}$, where the first subscript denotes the outcome when the treatment is 0, and the second denotes the outcome when the treatment is 1.
-We employ analogous notation for all other types: $b = \theta_{01}$, $c = \theta_{00}$, and $d = \theta_{11}$.
+\hypertarget{fixing-defects-in-ongoing-projects}{%
+\subsubsection{Fixing defects in ongoing
+projects}\label{fixing-defects-in-ongoing-projects}}
 
-When analyzing a case study of what happened in a given municipality, we can use the data to answer, for example, the following causal query: what is the probability that the city if type “b”, i.e, benefits from the monitoring and would have not completed the construction work if not for the monitoring of the local CSO?
+Another impact of the project was the correction of the irregularities
+and construction failures, improving the quality of the delivered
+construction work. During their monitoring activities, the OSBs found
+defects and issues, promptly reported them to municipality
+administration, which then acted in order to fix them. The project
+partners ended up substituting government inspectors and making up for
+their shortcomings in ensuring contract compliance through supervision.
+This was the case in both the four constructions in Taubaté (SP) and
+three that were going on in Foz do Iguaçu (SC). In both cases volunteers
+performed monitoring activities very frequently, which allowed for a
+thorough investigation and revealed a series of defects in projects and
+execution.
 
-The advantage of this approach is that all assumptions and restrictions imposed to identify the parameters of interest are transparent.
-It also allows the user to update posterior probabilities based on qualitative data.
-One reason for this is that with Bayesian inference, we do not need to rely on asymptotic theory to make inferences.
-Thus, there is no need for a large-n study.
-Formally speaking, one can make causal queries without any data, based only on prior probabilities for the parameters.
-Obviously the answer to such causal queries will be vague enough to be almost useless.
-But the point is that, once you have a prior and a causal model, encoded in a DAG, you can answer causal queries.
-As one collects data (any data, be it qualitative or quantitative), one can make assumptions about the nature of the data (such as the Data Generating Process), and then update the model and provide new answers to the causal queries, which hopefully will be informative enough to be useful for the task at hand.
-And even when the model or hypothesis is not completely identified, it can be partially identified [@manski_2003], which is still a useful answer to causal queries.
+\hypertarget{fixing-defects-in-finished-projects}{%
+\subsubsection{Fixing defects in finished
+projects}\label{fixing-defects-in-finished-projects}}
 
-## Data
+In Palhoça (SC), is an example when oversight came too late. One of the
+daycares completed before the monitoring period started was delivered
+with a wall of perforated elements without proper grouting, with pieces
+that were already coming loose. The daycare was put into operation
+without addressing the issue, which led the staff to isolate the area to
+minimize the risk of injuries to the children. In other words, part of
+the building cannot be used due to a failure for which a solution should
+have already been demanded from the responsible company.
 
-The evidence gathered is primarily based on documented reports collected by Transparência Brasil and produced by the local OSBs over the course of the project.
-We also use evidence collected on semi-structured interviews and an online survey with representatives of the 21 CSOs conducted by an independent evaluator of the project.
-For the quantitative analysis, we use administrative data about construction works data by municipalities and socio-demographic data on municipalities.
-The questions asked in the survey as well the aggregate answered are presented in annex B.
+In Goioerê, the story had a more happy ending. Volunteers visited an
+already delivered school building and noticed improperly installed
+windows, rendering them non-functional. A series of finishes were also
+lacking, such as grab bars and handles in accessible restrooms for
+persons with disabilities or reduced mobility. These shortcomings
+compromised adequate use of the building and exposed its users - mainly
+children - to potentially dangerous situations. These flaws were mostly
+corrected by the contractor after being reported by the local
+Observatório.
 
-## Case Studies
+\hypertarget{quantitative-observational-evidence}{%
+\subsection{Quantitative observational
+evidence}\label{quantitative-observational-evidence}}
 
-### Delivery of the construction works
+We have already observed qualitative evidence indicating that local OSB
+monitoring played a crucial role in expediting the completion of
+construction projects. Now, we present quantitative evidence regarding
+the impact of this monitoring on delivery rates.
 
-In our first case study, we highlight an impressive achievement in ensuring the completion of construction work.
-In Taubaté, four construction projects were underway, which the local OSB began monitoring as part of Obra Transparente.
-By the project's conclusion, their efforts played a crucial role in facilitating the successful delivery of these schools and nurseries to the city, ensuring they were ready for use in the field of education
+To do so, we collected data on school and nursery construction projects
+across the entire country, encompassing over two thousand municipalities
+and more than 14 thousand construction projects, spanning all phases
+from planning to execution and completion. The
+(\textbf{ref?})(tab:table1) below provides descriptive statistics for
+these construction projects.
 
-To put in perspective what was accomplished regarding the completion of all four projects, by the end of the project, of all 135 construction works planned for all 21 municipalities, only 25 were effectively delivered, a 18.5% delivery rate.
-In Taubaté,  before the monitoring by the local CSO, the delivery rate was zero.
-After that, the delivery rate was 100% and one of the construction work was a previously paralyzed construction.
-According to a report by Transparência Brasil [@coelho_etal2021], out of 771 stalled construction projects that were eventually completed, over 50% of them took more than two years to be delivered and 25% took three years or more.
-As we can see, the odds were against finishing the construction works.
+When comparing ``treated'' and ``untreated'' units, there is difference
+between the groups, as show below by the percentage of construction
+works within both groups before the project started.
 
-The local CSO monitoring the construction work in Taubaté did one of  the best jobs among all 21 municipalities covered in the project.
-In fact, it was mostly the work of a single volunteer with support from the local OSB and Transparência Brazil throughout the project.
-She monitored four ongoing construction works on a periodic basis, she was very knowledgeable and insistent in demanding response from contractors and the local government.
-To give a single example of the quality of the social monitoring going on, in an email sent on 17th January of 2018 to the local government, the local OSB volunteer wrote: “Fazendinha Daycare: a.
-construction log verified.
-There have been a few more construction workers on the site since December 15, 2017, but not enough, especially considering the extensive amount of work to be completed by the new delivery date in April 2018.
-b.
-(...).
-c.
-Lack of roof sealing, leading to water entering the classrooms (a situation that already existed on November 14, 2017)...” .
-She was by far the most knowledgeable and zealous volunteer of the whole project.
+\setlength{\LTpost}{0mm}
+\begin{longtable}{rrr}
+\caption*{
+{\large Percentage of finished construction works before the project} \\ 
+{\small Situation in August 2017 and August 2019}
+} \\ 
+\toprule
+\# of participating cities & \% (Before Project) & \% (After Project) \\ 
+\midrule\addlinespace[2.5pt]
+0 & $49\%$ & $59\%$ \\ 
+1 & $29\%$ & $42\%$ \\ 
+\bottomrule
+\end{longtable}
+\begin{minipage}{\linewidth}
+Construction projects in states SP, MG, SC, PR and RS.\\
+\end{minipage}
 
-All of the construction works were effectively finished and delivered by the end of the project, although overdue.
-One of them, a resumption of a then halted construction work, was delivered 2 months overdue.
-The remaining three were further delayed, but no amendments were made on prices, only deadlines.
+Our primary objective is to compare the project's effects on the rate of
+delivery. To estimate the Average Treatment Effect on the Treated (ATT),
+we employed a matching strategy (Ho et al. 2007; Rubin 1973) with a
+Bayesian logistic regression to create the propensity scores. Balance
+was successful after matching. We also applied the same procedure to
+pre-project data to ensure that there were no substantial differences
+between the treated and control groups.
 
-From a causal perspective, we are interested in what is called case-level causal attribution [@humphreys_2023], i.e, did the monitoring cause the delivery of the construction works?
-In other words, we are conditioning on the fact that M = 1 and C = 1, which constrains the possible types for Taubaté to be $\theta^C_{1,1}$ ou $\theta^C_{0,1}$.
-Assuming a simple model in which CSO monitoring causes the completion of works (M -> C), and with the eight within-case instances, we do the causal query.
-Our stimand of interest is the probability that Taubaté is a type $\theta^D_{10}$.
+We estimate all models using the a varying-intercept regression equation
+(Gelman and Hill 2006):
 
-Assuming uniform priors, the probability that  Taubaté is a type $\theta^D_{10}$, i.e, it is a city in which the treatment has a positive effect is 65%, with 95% credibility interval around [23%, 95%].
-As we can see, a wide interval, due to the low sample size, and yet, a positive effect nonetheless with 95% of certainty.
+\[
+Y_i = \alpha + \beta_1 T_i + \gamma X_i + \theta Z_i + \epsilon_i
+\]
 
-What are the assumptions behind such a result?
-The main one is that we modeled the monitoring (the treatment) as-if random, which is obviously not true.
-The mere passage of time causes an increased probability of delivery of a construction work.
-We can also imagine other possible confounds.
-The way to model it in a DAG is to add an arrow from M to C and vice-versa (M <-> C).
-Now, the estimand of interest depends on the probability of the treatment (monitoring) causing also the outcome (Average Treatment Effect, ATE).
-We will not detail the derivation of the new stimand here (you can consult annex B), but the idea is similar to before: we are interested in the type of city in which there is a causal effect of the monitoring on the completion of a construction works of school and/or nurseries.
-The mean probability of Taubaté being of this type, assuming the model is true is 43%, with 95% credibility intervals around [9%, 80%].
-The interval is wider because we added the uncertainty of confounding.
-Nonetheless, it is unlikely that the positive effect found in the observational data is driven only due to the confounding variables.
+Where \(i\) indexes the construction units, \(Y_i\) is \(1\) if a
+construction work is finished and \(0\) otherwise. \(\alpha\) represents
+the intercept, \(\beta\) denotes the average treatment effect on the
+treated (ATT), and \(T_i\) is a binary treatment indicator (whether the
+municipality is part of Obra Transparent or not). Symbol \(\gamma\) is a
+vector of varying intercepts, \(X_i\) is a matrix of random effects for
+Brazilian municipalities, \(\theta\) is a vector of control variables,
+and \(Z_i\) is an array of control variables for case \(i\). The error
+term is represented by \(\epsilon_i\). We employed a Bayesian model with
+rstanarm (Goodrich et al. 2023) with default weakly informative priors
+on the parameters (Gelman et al. 2008).
 
-### Preventing problems before projects started
-
-The local OSB monitoring in Auraucária story is one when oversight arrives at the right moment to prevent a costly government procurement.
-
-In 2017, the Brazilian municipality of Araucária conducted bidding processes seeking to hire companies to build three nurseries.
-The project sent technical experts to the 3 planned construction sites, together with volunteers from the local Observatório, to check whether plans were consistent with the physical conditions observed on site.
-The experts’ assessment was that high-cost contention walls included in the construction plans were unnecessary or could be replaced by low-cost solutions through adjustments.
-Originally, the contention walls would cost R$ 1,577,338.57 (US$ 419,504.9, at the nominal exchange rate in 2019).
-The analysis was first directed to the local administration, suggesting changes to the construction plans, which were rejected.
-The bidding processes went on as initially planned.
-Subsequently, the experts’ findings were submitted to the Brazilian Supreme Audit Institution, Tribunal de Contas da União (TCU), by Transparência Brasil and Observatório Social do Brazil (see annex 1).
-TCU recommended that the bidding process should be redone, and construction plans were to be redesigned, with more cost-effective solutions for the contention walls.
-In the new bidding process, their cost plummeted to R\$ 416,883.17 (USD 110,873.2), a reduction of USD 308,631.7 — or 74% less.
-To give a sense of the impact on the city budget, the amount saved on these three constructions alone represents about 3% of all capital investments of Araucária in 2018.
-In short, in a single municipality, the project resulted in savings higher than the cost of the entire project funded by the grantee UNDEF (US$ 220,000.00).
-
-### Fixing defects in ongoing projects
-
-Another impact of the project was the correction of the irregularities and construction failures, improving the quality of the delivered construction work.
-During their monitoring activities, the OSBs found defects and issues, promptly reported them to municipality administration, which then acted in order to fix them.
-The project partners ended up substituting government inspectors and making up for their shortcomings in ensuring contract compliance through supervision.
-This was the case in both the four constructions in Taubaté (SP) and three that were going on in Foz do Iguaçu (SC).
-In both cases volunteers performed monitoring activities very frequently, which allowed for a thorough investigation and revealed a series of defects in projects and execution.
-
-### Fixing defects in finished projects
-
-In Palhoça (SC), is an example when oversight came too late.
-One of the daycares completed before the monitoring period started was delivered with a wall of perforated elements without proper grouting, with pieces that were already coming loose.
-The daycare was put into operation without addressing the issue, which led the staff to isolate the area to minimize the risk of injuries to the children.
-In other words, part of the building cannot be used due to a failure for which a solution should have already been demanded from the responsible company.
-
-In Goioerê, the story had a more happy ending.
-Volunteers visited an already delivered school building and noticed improperly installed windows, rendering them non-functional.
-A series of finishes were also lacking, such as grab bars and handles in accessible restrooms for persons with disabilities or reduced mobility.
-These shortcomings compromised adequate use of the building and exposed its users - mainly children - to potentially dangerous situations.
-These flaws were mostly corrected by the contractor after being reported by the local Observatório.
-
-## Quantitative observational evidence
-
-We have already observed qualitative evidence indicating that local OSB monitoring played a crucial role in expediting the completion of construction projects.
-Now, we present quantitative evidence regarding the impact of this monitoring on delivery rates.
-
-To do so, we collected data on school and nursery construction projects across the entire country, encompassing over two thousand municipalities and more than 14 thousand construction projects, spanning all phases from planning to execution and completion.
-The @ref(tab:table1) below provides descriptive statistics for these construction projects.
-
-When comparing "treated" and "untreated" units, there is difference between the groups, as show below by the percentage of construction works within both groups before the project started.
-
-```{r table1, echo=FALSE, message=FALSE, results='asis'}
-antes_projeto %>%
-  inner_join(depois_projeto, by = "indicator_muni_ot") %>%
-  gt() %>%
-  tab_header(
-    title = "Percentage of finished construction works before the project",
-    subtitle = "Situation in August 2017 and August 2019") %>%
-   opt_align_table_header(align = "left") %>%
-  cols_label(
-    indicator_muni_ot = "# of participating cities",
-    perc.x = "% (Before Project)",
-    perc.y = "% (After Project)"
-  ) %>%
-    fmt_percent(
-    columns = c(perc.x, perc.y),
-    decimals = 0
-  ) %>%
-    tab_source_note(
-    source_note = "Construction projects in states SP, MG, SC, PR and RS."
-  ) %>%
-  tab_options(table.align='left')
-```
-
-Our primary objective is to compare the project's effects on the rate of delivery.
-To estimate the Average Treatment Effect on the Treated (ATT), we employed a matching strategy [@ho_etal2007; @rubin_1973] with a Bayesian logistic regression to create the propensity scores.
-Balance was successful after matching.
-We also applied the same procedure to pre-project data to ensure that there were no substantial differences between the treated and control groups.
-
-We estimate all models using the a varying-intercept regression equation [@gelman_2006]:
-
-$$
-Y_i = \alpha + \beta_1 T_i + \gamma X_i + \theta Z_i + \epsilon_i
-$$
-
-Where $i$ indexes the construction units, $Y_i$ is $1$ if a construction work is finished and $0$ otherwise.
-$\alpha$ represents the intercept, $\beta$ denotes the average treatment effect on the treated (ATT), and $T_i$ is a binary treatment indicator (whether the municipality is part of Obra Transparent or not).
-Symbol $\gamma$ is a vector of varying intercepts, $X_i$ is a matrix of random effects for Brazilian municipalities, $\theta$ is a vector of control variables, and $Z_i$ is an array of control variables for case $i$.
-The error term is represented by $\epsilon_i$.
-We employed a Bayesian model with rstanarm [@goodrich_etal2023] with default weakly informative priors on the parameters [@gelman_etal2008].
-
-The table below presents estimates for the causal effect on the treated units regarding the change in completion rates before and after the project.
-
-```{r prep data matching,  message=FALSE, echo=FALSE, cache=TRUE}
-
-aux_muni1 <- aux_muni %>%
-  mutate(name_muni1 = tolower(iconv(name_muni, "UTF-8",  "ASCII//TRANSLIT")))
-
-df_balancing_aux <- obras_inicio_projeto_ot %>%
-  mutate(municipio1 = tolower(iconv(municipio, "UTF-8",  "ASCII//TRANSLIT"))) %>%
-  inner_join(aux_muni1, by = join_by(municipio1  == name_muni1, uf == abbrev_state)) %>%
-  inner_join(ipea_final, by = join_by(code_muni == tcode)) %>%
-  mutate(perc_pea18 =pea18/populacao,
-         log_pop = log(populacao),
-         log_renda = log(rpc*populacao),
-         log_rpc = log(rpc),
-         tipo_do_projeto = ifelse(grepl("Bloco Estrutural" ,tipo_do_projeto),
-                                  "Projeto Tipo B ou C - Bloco Estrutural", tipo_do_projeto))
-
-df_balancing_aux1 <- df_balancing_aux %>%
-  mutate(concluida_num = as.numeric(concluida))
-
-df_balancing_aux_se <- df_balancing_aux1 %>%
-  filter(uf.x %in% c("SP", "PR", "SP", "SC", "RS", "MG"))
-
-pre_dados <- df_balancing_aux %>%
-  dplyr::select(id, concluida) %>%
-  rename(concluida_pre = concluida) %>%
-  mutate(id = as.numeric(id))
-
-data_pos <- obras_fim_seg_fase %>%
-  mutate(municipio1 = tolower(iconv(municipio, "UTF-8",  "ASCII//TRANSLIT"))) %>%
-  inner_join(aux_muni1, by = join_by(municipio1  == name_muni1, uf == abbrev_state)) %>%
-  inner_join(ipea_final, by = join_by(code_muni == tcode)) %>%
-  mutate(perc_pea18 =pea18/populacao,
-         log_pop = log(populacao),
-         log_renda = log(rpc*populacao),
-         log_rpc = log(rpc)) %>%
-  inner_join(pre_dados, by = "id") %>%
-  dplyr::filter(concluida_pre == FALSE) %>%
-  mutate(concluida_num = as.numeric(concluida))
-
-df_balancing_aux_post_se <- data_pos %>%
-  filter(uf.x %in% c("SP", "PR", "SP", "SC", "RS", "MG"))
-
-save(df_balancing_aux1, file = here("Dados", "df_balancing_aux1.RData"))
-save(df_balancing_aux_se, file = here("Dados", "df_balancing_aux_se.RData"))
-save(df_balancing_aux_post_se, file = here("Dados", "df_balancing_aux_post_se.RData"))
-save(data_pos, file = here("Dados", "data_pos.RData"))
-```
+The table below presents estimates for the causal effect on the treated
+units regarding the change in completion rates before and after the
+project.
 
 Table (insert ref number) summarizes the main results of the regression.
-The first row presents the results for the regression before the project started, where we expect the effect of the project to be zero, since it didn't exist.
-The second row shows the effect after the end of the project, when we expect the impact to be positive.
-The first column is an estimate of the posterior mean of the impact of the project and the second one is the posterior standard deviation of the estimate.
-We also present posterior median and $2.5%$ and $97.5%$ quantiles, in order to quantify the uncertainty around the estimates with a 95% credibility interval.
+The first row presents the results for the regression before the project
+started, where we expect the effect of the project to be zero, since it
+didn't exist. The second row shows the effect after the end of the
+project, when we expect the impact to be positive. The first column is
+an estimate of the posterior mean of the impact of the project and the
+second one is the posterior standard deviation of the estimate. We also
+present posterior median and \(2.5%
+\) and \(97.5%
+\) quantiles, in order to quantify the uncertainty around the estimates
+with a 95\% credibility interval.
 
-The hypothesis are corroborated, and we did not find an effect before the starting of the project, but found an effect aftet the end of the project.
-On average, a city that received the project Obra Transparente increases its delivery rate by almost 10%.
-These results support our argument and the qualitative evidence we presented that sustained and costly bottom-up accountability improve public policies.
+The hypothesis are corroborated, and we did not find an effect before
+the starting of the project, but found an effect aftet the end of the
+project. On average, a city that received the project Obra Transparente
+increases its delivery rate by almost 10\%. These results support our
+argument and the qualitative evidence we presented that sustained and
+costly bottom-up accountability improve public policies.
 
-```{r pscore, message=FALSE, echo=FALSE}
+\setlength{\LTpost}{0mm}
+\begin{longtable}{lrrrrr}
+\caption*{
+{\large Effect of local OSB social monitoring on construction delivery rates} \\ 
+{\small Posterior probabilities}
+} \\ 
+\toprule
+Variables & Mean & Sd & Median & 2.5\% CI & 97.5\% CI \\ 
+\midrule\addlinespace[2.5pt]
+ATT before project & $0.025$ & $0.042$ & $0.026$ & $-0.059$ & $0.108$ \\ 
+ATT After project & $0.099$ & $0.049$ & $0.099$ & $0.001$ & $0.194$ \\ 
+\bottomrule
+\end{longtable}
+\begin{minipage}{\linewidth}
+452 observations for the pre-treatment period and 320 observations for the post-treatment period, resulting from the matching procedure, and encompassing municipalities in the same states as municipalities of Obra Transparente\\
+\end{minipage}
 
-# these are the no redundancy covariates
-covs.nr <- c('perc_pea18', 'ext_pobres', 'log_rpc', 'p10_ricos_desigualdade', 'freq_escola_15_1', 'analfabetismo',
-             'log_renda', 'log_pop', 'percentual_de_execucao')
+\hypertarget{discussion-of-results}{%
+\subsection{Discussion of Results}\label{discussion-of-results}}
 
-# pscore estimation formula with original covariates
+One of the reasons identified for some of the problems with the
+construction works is lack of qualified personnel from the government to
+monitor the contractor work. As a result, the local government does not
+properly oversight the work of contractors. And this is a task that
+requires technical expertise and is time consuming, involving going
+multiple times to the construction site, comparing the construction log
+with the schedule to assess if there is potential delay and what is
+specified in the contract, to assess if the materials used are correct,
+if everything demanded is being done etc.
 
-ps_spec <- formula(indicator_muni_ot ~ log_rpc  + ext_pobres + freq_escola_15_1 + analfabetismo +
-                     log_renda   +  p10_ricos_desigualdade + percentual_de_execucao)
+The fact that an intervention like Tá de Pé (Freire, Galdino, and
+Mignozzetti 2020), which provided information to citizens about
+construction work, but did not produce a meaningful impact does not mean
+that bottom up accountability does not have any effect. The evidence we
+gathered here, assessed with multiple methods, clearly shows that costly
+and consistent oversight by civil society can produce results that are
+quite impactful, be it increased rate of project completion, improved
+quality of the construction works or decreasing in governmental
+spending.
 
-# Estimation of pscores using stan_glm
-set.seed(1234)
-ps_fit_pre <- stan_glm(ps_spec, family=binomial(link='logit'), 
-                     data=df_balancing_aux_se, algorithm='optimizing', refresh=0, iter = 2000)
+The detection of evidence of procurement fraud cases also shows local
+administrations are not diligent enough in conducting procurement
+procedures, and the local partners of TB contributed to addressing that
+gap as well. Moreover, as federal audit agencies lack the capacity to
+adequately oversee and analyze the immense volume of contracting
+procedures conducted at the local level, the social monitoring resulted
+in the identification of high-risk cases that otherwise might not have
+been assessed by the competent bodies.
 
-set.seed(1234)
-ps_fit_pos <- stan_glm(ps_spec, family=binomial(link='logit'), 
-                     data=df_balancing_aux_post_se, algorithm='optimizing', refresh=0, iter = 2000)
+\hypertarget{concluding-remarks}{%
+\subsection{Concluding Remarks}\label{concluding-remarks}}
 
-# extracting logit pscores
-pscores_pre <- apply(posterior_linpred(ps_fit_pre), 2, mean)
+Accountability, as a fundamental element in democratic systems, plays a
+pivotal role in ensuring the efficient provision of public services.
+Recent studies have brought to light the concept of ``bottom-up
+accountability,'' where citizens receive information about public
+policies and utilize it to exert social control.
 
-pscores_pos <- apply(posterior_linpred(ps_fit_pos), 2, mean)
+While tactical interventions aimed at providing information to citizens
+have shown limited impact, it would be a mistake to dismiss the
+potential of citizen voices in governance entirely. Our research has
+differentiated between information-led tactical interventions and active
+mobilization and monitoring by Civil Society Organizations (CSOs). We
+argue that organized CSOs, deeply rooted in society and politics, hold
+the capacity to bring about substantial policy change.
 
-# matching
-#matching without replacement, original formula
-matches_pre <- matching(z=df_balancing_aux_se$indicator_muni_ot, score=pscores_pre, replace=FALSE)
-matched_pre <- df_balancing_aux_se[matches_pre$match.ind,]
+This paper provides evidence in support of this argument. By assessing
+the effectiveness of the ``Obra Transparente'' project developed by
+Transparência Brasil, we illustrate the significant role that organized
+CSOs can play in shaping government behavior and improving public
+service delivery. Unlike interventions solely focused on providing
+information, this project aimed at creating a network of local CSOs,
+offering technical support, and providing training on monitoring public
+school and nursery construction projects.
 
-matches_pos <- matching(z=df_balancing_aux_post_se$indicator_muni_ot, score=pscores_pos, replace=FALSE)
-matched_pos <- df_balancing_aux_post_se[matches_pos$match.ind,]
+Our findings underscore the importance of sustained, concerted efforts
+by organized civil society, including direct engagement with municipal
+officials, persistent follow-ups, and on-site visits. These endeavors
+yield more substantial outcomes compared to interventions that merely
+deliver information and generate sporadic citizen actions.
 
-```
+In a world where accountability mechanisms continue to evolve, the role
+of organized civil society remains paramount. The ability to foster
+collective action, create informed oversight, and influence policy
+change is an essential aspect of accountable and effective democratic
+governance. The journey toward enhancing bottom-up accountability is
+ongoing, and our research contributes to a more comprehensive
+understanding of how it can be achieved through the mobilization of
+organized civil society.
 
-```{r fitting bayesian model, message=FALSE, echo=FALSE, cache = TRUE}
+Sample figure:
 
-df_balancing_aux_se <- df_balancing_aux_se %>%
-  dplyr::select(concluida_num , indicator_muni_ot, code_muni, log_rpc, ext_pobres, freq_escola_15_1,analfabetismo,
-                log_renda, p10_ricos_desigualdade, percentual_de_execucao, municipio)
+\begin{figure}
+Figure here.
 
-te_spec_nr <- update(ps_spec, concluida_num ~ indicator_muni_ot + (1 | code_muni) + .)
+\caption{Caption for figure below.}
+\begin{figurenotes}
+Figure notes without optional leadin.
+\end{figurenotes}
+\begin{figurenotes}[Source]
+Figure notes with optional leadin (Source, in this case).
+\end{figurenotes}
+\end{figure}
 
-#treatment effect without replacement
+Sample table:
 
-set.seed(120)
-reg_ps_pre <- stan_lmer(te_spec_nr, data=df_balancing_aux_se[matches_pre$match.ind,], iter = 4000, refresh=0)
+\begin{table}
+\caption{Caption for table above.}
 
-## After
-set.seed(120)
-reg_ps_pos <- stan_lmer(te_spec_nr, data=df_balancing_aux_post_se[matches_pos$match.ind,], iter = 4000, refresh=0)
+\begin{tabular}{lll}
+& Heading 1 & Heading 2 \\
+Row 1 & 1 & 2 \\
+Row 2 & 3 & 4%
+\end{tabular}
+\begin{tablenotes}
+Table notes environment without optional leadin.
+\end{tablenotes}
+\begin{tablenotes}[Source]
+Table notes environment with optional leadin (Source, in this case).
+\end{tablenotes}
+\end{table}
 
-```
+\hypertarget{references}{%
+\subsection{References}\label{references}}
 
-```{r processing bayes fit, echo=FALSE,  message=FALSE}
-# posterior draws
+\bibliographystyle{aea}
+\bibliography{references}
 
-##
-# Before
-##
+\% The appendix command is issued once, prior to all appendices, if any.
+\appendix
 
-b1_pre_sims <- as.matrix(reg_ps_pre, 
-                     pars = "indicator_muni_ot")
+\section{Mathematical Appendix}
 
-# Posterior mean and SD of treatment
-b1_mean_pre <- mean(b1_pre_sims) # posterior mean
-b1_sd_pre <- sd(b1_pre_sims)       # posterior SD
+\hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-ankamah_2019}{}}%
+Ankamah, Samuel Siebie. 2019. {``Why Do {`Teeth'} Need {`Voice'}? {The}
+Case of Anti-Corruption Agencies in Three {Australian} States.''}
+\emph{Australian Journal of Public Administration} 78 (4): 481--96.
 
-# Posterior median and 95% credible interval
-b1_quant_pre <- quantile(b1_pre_sims,   probs = c(0.025, 0.50, 0.975))
+\leavevmode\vadjust pre{\hypertarget{ref-bertelli_2020}{}}%
+Bertelli, Anthony M., and Gregg G. Van Ryzin. 2020. {``Heuristics and
+Political Accountability in Complex Governance: {An} Experimental
+Test.''} \emph{Research \& Politics} 7 (3): 2053168020950080.
+\url{https://doi.org/10.1177/2053168020950080}.
 
-b1_quant_pre <- data.frame(t(b1_quant_pre))
-names(b1_quant_pre) <- c("Q2.5", "Q50", "Q97.5")
+\leavevmode\vadjust pre{\hypertarget{ref-besley_2003}{}}%
+Besley, Timothy, and Maitreesh Ghatak. 2003. {``Incentives, Choice, and
+Accountability in the Provision of Public Services.''} \emph{Oxford
+Review of Economic Policy} 19 (2): 235--49.
 
-# Combine summary statistics of posterior simulation draws
-b1_df_pre_cred <- data.frame(variables = "ATT before project",
-                             post_mean = b1_mean_pre,
-                             post_sd = b1_sd_pre,
-                             b1_quant_pre[2], 
-                             b1_quant_pre[1],
-                             b1_quant_pre[3])
+\leavevmode\vadjust pre{\hypertarget{ref-bjorkman_2009}{}}%
+Björkman, Martina, and Jakob Svensson. 2009. {``Power to the People:
+Evidence from a Randomized Field Experiment on Community-Based
+Monitoring in {Uganda}.''} \emph{The Quarterly Journal of Economics} 124
+(2): 735--69.
 
-##
-# After
-##
-b1_sims_after <- as.matrix(reg_ps_pos, 
-                     pars = "indicator_muni_ot")
+\leavevmode\vadjust pre{\hypertarget{ref-cameron_2004}{}}%
+Cameron, Wayne. 2004. {``Public Accountability: {Effectiveness}, Equity,
+Ethics.''} \emph{Australian Journal of Public Administration} 63 (4):
+59--67.
 
-# Compute mean, SD, median, and 95% credible interval of treatment
+\leavevmode\vadjust pre{\hypertarget{ref-coelho_etal2021}{}}%
+Coelho, Jonas, Manoel Galdino, and Juliana Sakai. 2021.
+{``{Levantamento: Obras federais paralisadas de creches e escolas com
+maiores chances de serem concluídas}.''}
 
-# Posterior mean and SD of treatment
-b1_mean_after <- mean(b1_sims_after) # posterior mean
-b1_sd_after <- sd(b1_sims_after)       # posterior SD
+\leavevmode\vadjust pre{\hypertarget{ref-fairfield_2022}{}}%
+Fairfield, Tasha, and Andrew E. Charman. 2022. \emph{Social Inquiry and
+{Bayesian} Inference: {Rethinking} Qualitative Research}. {Cambridge
+University Press}.
 
-# Posterior median and 95% credible interval
-b1_quant_after <- quantile(b1_sims_after,   probs = c(0.025, 0.50, 0.975))
+\leavevmode\vadjust pre{\hypertarget{ref-fox_2015}{}}%
+Fox, Jonathan A. 2015. {``Social Accountability: What Does the Evidence
+Really Say?''} \emph{World Development} 72: 346--61.
 
-b1_quant_after <- data.frame(t(b1_quant_after))
-names(b1_quant_after) <- c("Q2.5", "Q50", "Q97.5")
+\leavevmode\vadjust pre{\hypertarget{ref-freire_etal2020}{}}%
+Freire, Danilo, Manoel Galdino, and Umberto Mignozzetti. 2020.
+{``Bottom-up Accountability and Public Service Provision: {Evidence}
+from a Field Experiment in {Brazil}.''} \emph{Research \& Politics} 7
+(2): 1--8. \url{https://doi.org/10.1177/2053168020914444}.
 
-# Combine summary statistics of posterior simulation draws
-b1_df_after_cred <- data.frame(variables = "ATT After project",
-                             post_mean = b1_mean_after,
-                             post_sd = b1_sd_after,
-                             b1_quant_after[2], 
-                             b1_quant_after[1],
-                             b1_quant_after[3])
-b1_df <- bind_rows(b1_df_pre_cred, b1_df_after_cred)
-```
+\leavevmode\vadjust pre{\hypertarget{ref-gelman_2006}{}}%
+Gelman, Andrew, and Jennifer Hill. 2006. \emph{Data Analysis Using
+Regression and Multilevel/Hierarchical Models}. {Cambridge university
+press}.
 
-```{r table2, echo=FALSE,  message=FALSE, results='asis'}
+\leavevmode\vadjust pre{\hypertarget{ref-gelman_etal2008}{}}%
+Gelman, Andrew, Aleks Jakulin, Maria Grazia Pittau, and Yu-Sung Su.
+2008. {``A Weakly Informative Default Prior Distribution for Logistic
+and Other Regression Models.''}
 
-b1_df %>% gt() %>%
-  tab_header(
-    title = "Effect of local OSB social monitoring on construction delivery rates",
-    subtitle = "Posterior probabilities") %>%
-  cols_label(
-    variables = "Variables",
-    post_mean = "Mean",
-    post_sd = "Sd",
-    Q50 = "Median",
-    Q2.5 = "2.5% CI",
-    Q97.5 = "97.5% CI"
-  ) %>%
-  fmt_number(
-    columns = c(post_mean, post_sd, Q50, Q2.5, Q97.5 ),
-    decimals = 3,
-    use_seps = FALSE
-  ) %>%
-  tab_source_note(
-    source_note = "452 observations for the pre-treatment period and 320 observations for the post-treatment period, resulting from the matching procedure, and encompassing municipalities in the same states as municipalities of Obra Transparente"
-  ) %>%
-  tab_options(., container.width = 500, container.height =     500)
-```
+\leavevmode\vadjust pre{\hypertarget{ref-gong_2017}{}}%
+Gong, Ting, and Hanyu Xiao. 2017. {``Socially Embedded Anti-Corruption
+Governance: {Evidence} from {Hong Kong}.''} \emph{Public Administration
+and Development} 37 (3): 176--90.
 
-## Discussion of Results
+\leavevmode\vadjust pre{\hypertarget{ref-goodrich_etal2023}{}}%
+Goodrich, Ben, Jonah Gabry, Imad Ali, and Sam Brilleman. 2023.
+{``Rstanarm: {Bayesian} Applied Regression Modeling via {Stan}.''}
+\emph{R Package Version} 2 (26.1).
 
-One of the reasons identified for some of the problems with the construction works is lack of qualified personnel from the government to monitor the contractor work.
-As a result, the local government does not properly oversight the work of contractors.
-And this is a task that requires technical expertise and is time consuming, involving going multiple times to the construction site, comparing the construction log with the schedule to assess if there is potential delay and what is specified in the contract, to assess if the materials used are correct, if everything demanded is being done etc.
+\leavevmode\vadjust pre{\hypertarget{ref-ho_etal2007}{}}%
+Ho, Daniel E., Kosuke Imai, Gary King, and Elizabeth A. Stuart. 2007.
+{``Matching as Nonparametric Preprocessing for Reducing Model Dependence
+in Parametric Causal Inference.''} \emph{Political Analysis} 15 (3):
+199--236.
 
-The fact that an intervention like Tá de Pé [@freire_etal2020], which provided information to citizens about construction work, but did not produce a meaningful impact does not mean that bottom up accountability does not have any effect.
-The evidence we gathered here, assessed with multiple methods, clearly shows that costly and consistent oversight by civil society can produce results that are quite impactful, be it increased rate of project completion, improved quality of the construction works or decreasing in governmental spending.
+\leavevmode\vadjust pre{\hypertarget{ref-humphreys_2023}{}}%
+Humphreys, Macartan, and Alan M. Jacobs. 2023. \emph{{INTEGRATED
+INFERENCES}: {Causal Models} for {Qualitative} and {Mixed-method
+Research}}. {CAMBRIDGE University Press}.
 
-The detection of evidence of procurement fraud cases also shows local administrations are not diligent enough in conducting procurement procedures, and the local partners of TB contributed to addressing that gap as well.
-Moreover, as federal audit agencies lack the capacity to adequately oversee and analyze the immense volume of contracting procedures conducted at the local level, the social monitoring resulted in the identification of high-risk cases that otherwise might not have been assessed by the competent bodies.
+\leavevmode\vadjust pre{\hypertarget{ref-imbens_2015}{}}%
+Imbens, Guido W., and Donald B. Rubin. 2015. \emph{Causal Inference in
+Statistics, Social, and Biomedical Sciences}. {Cambridge University
+Press}.
 
-## Concluding Remarks
+\leavevmode\vadjust pre{\hypertarget{ref-joshi_2012}{}}%
+Joshi, Anuradha, and Peter P. Houtzager. 2012. {``Widgets or Watchdogs?
+{Conceptual} Explorations in Social Accountability.''} \emph{Public
+Management Review} 14 (2): 145--62.
 
-Accountability, as a fundamental element in democratic systems, plays a pivotal role in ensuring the efficient provision of public services.
-Recent studies have brought to light the concept of "bottom-up accountability," where citizens receive information about public policies and utilize it to exert social control.
+\leavevmode\vadjust pre{\hypertarget{ref-kenney_2003}{}}%
+Kenney, Charles D. 2003. {``Horizontal Accountability: Concepts and
+Conflicts.''} In \emph{Democratic {Accountability} in {Latin America}},
+55--76. {Scott Mainwaring \& Christopher Welna}.
 
-While tactical interventions aimed at providing information to citizens have shown limited impact, it would be a mistake to dismiss the potential of citizen voices in governance entirely.
-Our research has differentiated between information-led tactical interventions and active mobilization and monitoring by Civil Society Organizations (CSOs).
-We argue that organized CSOs, deeply rooted in society and politics, hold the capacity to bring about substantial policy change.
+\leavevmode\vadjust pre{\hypertarget{ref-manski_2003}{}}%
+Manski, Charles F. 2003. \emph{Partial Identification of Probability
+Distributions}. Vol. 5. {Springer}.
 
-This paper provides evidence in support of this argument.
-By assessing the effectiveness of the "Obra Transparente" project developed by Transparência Brasil, we illustrate the significant role that organized CSOs can play in shaping government behavior and improving public service delivery.
-Unlike interventions solely focused on providing information, this project aimed at creating a network of local CSOs, offering technical support, and providing training on monitoring public school and nursery construction projects.
+\leavevmode\vadjust pre{\hypertarget{ref-mattoni_2021}{}}%
+Mattoni, Alice, and Fernanda Odilla. 2021. {``Digital {Media},
+{Activism}, and {Social Movements}' {Outcomes} in the {Policy Arena}.
+{The Case} of {Two Anti-Corruption Mobilizations} in {Brazil}.''}
+\emph{Partecipazione e Conflitto} 14 (3): 1127--50.
 
-Our findings underscore the importance of sustained, concerted efforts by organized civil society, including direct engagement with municipal officials, persistent follow-ups, and on-site visits.
-These endeavors yield more substantial outcomes compared to interventions that merely deliver information and generate sporadic citizen actions.
+\leavevmode\vadjust pre{\hypertarget{ref-mulgan_2000}{}}%
+Mulgan, Richard. 2000. {``{`{Accountability}'}: An Ever-Expanding
+Concept?''} \emph{Public Administration} 78 (3): 555--73.
 
-In a world where accountability mechanisms continue to evolve, the role of organized civil society remains paramount.
-The ability to foster collective action, create informed oversight, and influence policy change is an essential aspect of accountable and effective democratic governance.
-The journey toward enhancing bottom-up accountability is ongoing, and our research contributes to a more comprehensive understanding of how it can be achieved through the mobilization of organized civil society.
+\leavevmode\vadjust pre{\hypertarget{ref-odonnell_1998}{}}%
+O'donnell, Guillermo. 1998. {``Horizontal Accountability in New
+Democracies.''} \emph{J. Democracy} 9: 112.
 
-## References
+\leavevmode\vadjust pre{\hypertarget{ref-odonnell_2003}{}}%
+---------. 2003. {``Horizontal Accountability: {The} Legal
+{Institutionalization} of {Mistrust}.''} In \emph{Democratic
+{Accountability} in {Latin America}}, 34:34--54. {Scott Mainwaring \&
+Christopher Welna}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-oloughlin_1990}{}}%
+O'Loughlin, Michael G. 1990. {``What Is Bureaucratic Accountability and
+How Can We Measure It?''} \emph{Administration \& Society} 22 (3):
+275--302.
+
+\leavevmode\vadjust pre{\hypertarget{ref-odilla_2023}{}}%
+Odilla, Fernanda. 2023. {``Bots Against Corruption: {Exploring} the
+Benefits and Limitations of {AI-based} Anti-Corruption Technology.''}
+\emph{Crime, Law and Social Change}, 1--44.
+
+\leavevmode\vadjust pre{\hypertarget{ref-paul_1992}{}}%
+Paul, Samuel. 1992. {``Accountability in Public Services: Exit, Voice
+and Control.''} \emph{World Development} 20 (7): 1047--60.
+
+\leavevmode\vadjust pre{\hypertarget{ref-raffler_etal2019}{}}%
+Raffler, Pia, Daniel N. Posner, and Doug Parkerson. 2019. {``The
+Weakness of Bottom-up Accountability: Experimental Evidence from the
+{Ugandan} Health Sector.''} \emph{Los Angeles: Innovations for Poverty
+Action}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-relly_2012}{}}%
+Relly, Jeannine E. 2012. {``Examining a Model of Vertical
+Accountability: {A} Cross-National Study of the Influence of Information
+Access on the Control of Corruption.''} \emph{Government Information
+Quarterly} 29 (3): 335--45.
+
+\leavevmode\vadjust pre{\hypertarget{ref-rubin_1973}{}}%
+Rubin, Donald B. 1973. {``Matching to Remove Bias in Observational
+Studies.''} \emph{Biometrics}, 159--83.
+
+\leavevmode\vadjust pre{\hypertarget{ref-rubin_2005}{}}%
+---------. 2005. {``Causal Inference Using Potential Outcomes: {Design},
+Modeling, Decisions.''} \emph{Journal of the American Statistical
+Association} 100 (469): 322--31.
+
+\leavevmode\vadjust pre{\hypertarget{ref-serra_2012}{}}%
+Serra, Danila. 2012. {``Combining Top-down and Bottom-up Accountability:
+Evidence from a Bribery Experiment.''} \emph{The Journal of Law,
+Economics, \& Organization} 28 (3): 569--87.
+
+\end{CSLReferences}
+
+\end{document}

### 2023-11-06 Scripts/paper.Rmd
paper versão anterior

@@
 date: "2023-10-26"
-output: bookdown::pdf_document2
 sansfont: Sans Serif
@@
 author:
-  - name: Manoel Galdino
-    affiliation: Universidade de São Paulo - Brazil.
-  - names: Juliana Sakai
-    affiliation: Transparência Brasil - Brazil
-  - names: Bianca Vaz Mondo
-    affiliation: Transparência Brasil - Brazil
-  - names: Natália Paiva
-    affiliation: Alandar Consulting - Brazil
+- name: Manoel Galdino^[Universidade de São Paulo - Brazil, mgaldino@usp.br]
+- names: Juliana Sakai^[Transparência Brasil - Brazil]
+- names: Bianca Vaz Mondo^[Government Transparency Institute - Germany]
+- names: Natália Paiva^[Alandar Consulting - Brazil]
+
 abstract: "This paper examines the effect of bottom-up accountability on public service delivery.
@@
 bibliography: OT_paper.bib
+output:
+    bookdown::pdf_document2:
+      base_format: rticles::sage_article
+
 ---

### 2023-11-06 Research_and_Politics/Research_and_Politics.Rmd
Failed attempt R&P

---
title: The Civil Society Organizations effect: A mixed-Methods analysis of bottom-up approaches in Brazilian public policy
runninghead: Galdino_et al._.
author:
- name: Manoel Galdino*
  num: 1,2
- name: Juliana Sakai
  num: 2
- name: Bianca Vaz Mondo
  num: 3
- name: Natália Paiva
  num: 4
address:
- num: 1
  org: Department of Political Science, Universidade of São Paulo, Brazil
- num: 2
  org: Transparência Brasil, Brazil
- num: 3
  org: Herthie School, Germany
- num: 4
  org: Alandar Consulting, Brazil
corrauth: "Manoel Galdino, Avenida Luciano Gualberto, 315.Sala 2081. CEP 05508-090. São Paulo - SP, Brazil."
email: mgaldino@usp.br
abstract: "This paper examines the effect of bottom-up accountability on public service delivery. We differentiate between information-driven interventions and the mobilization and monitoring efforts of organized Civil Society Organizations (CSOs), and argue that the latter type of interventions can can drive significant policy change. The study evaluates the effectiveness of the Obra Transparente project by Brazilian NGO Transparência Brasil, engaging 21 local CSOs in South and Southeast Brazil.  Our findings emphasize the importance of sustained, coordinated efforts by socially embedded CSOS. These efforts, involving direct engagement with municipal officials and ensuring that their complains cannot be ignored lead to more substantial outcomes when compared with citizens information-driven"
keywords: Class file; \LaTeX; SMMR; Rmarkdown;
classoption:
  - Royal
  - times
bibliography: OT_paper.bib
bibliographystyle: sageh
output:
  rticles::sage_article:
    keep_tex: yes
---

# The Article Header Information

YAML header:

```
output:
  rticles::sim_article:
    keep_tex: TRUE
```

Configure the YAML header including the following elements:

* `title`: Title

* `runninghead`: Author last names, use _et al._ if there are three or more authors.

* `author`: List of author(s) containing `name` and `num`

* `corrauth`: Corresponding author's name and address.

* `email`: Correspondence email

* `abstract`: Limited to 200 words

* `keywords`: Keywords for the article

* `bibliography`: BibTeX `.bib` file

* `bibliographystyle`: sageh or sagev

* `classoption`: options of the `sagej` class

## Remarks

2. `bibliographystyle`

3. `classoption`

4. Keywords are separated by commas.

# The Body of the Article

## Mathematics

Use mathematics in Rmarkdown as usual.

## Figures and Tables

Figures are supported from R code:

```{r plot-ref, fig.cap = "Fancy Caption\\label{fig:plot}", out.width='100%'}
x = rnorm(10)
y = rnorm(10)
plot(x, y)
```

...and can be referenced (Figure \ref{fig:plot}) by including the `\\label{}` tag in the `fig.cap` attribute of the R chunk: `fig.cap = "Fancy Caption\\label{fig:plot}"`. It is a quirky hack at the moment, see [here](https://github.com/yihui/knitr/issues/323).

Analogously, use Rmarkdown to produce tables as usual:

```{r, results = "asis"}
if (!require("xtable")) install.packages("xtable")
xt <- xtable(head(cars), caption = "A table", label = "tab:table")
print(xt, comment = FALSE)
```

Referenced via \ref{tab:table}. @article{gelmanWeaklyInformativeDefault2008,
  title = {A Weakly Informative Default Prior Distribution for Logistic and Other Regression Models},
  author = {Gelman, Andrew and Jakulin, Aleks and Pittau, Maria Grazia and Su, Yu-Sung},
  date = {2008}
}
It is also possible to set the `YAML` option `longtable: true` and use markdown tables (or the `knitr::kable` function): `knitr::kable(head(cars))` produces the same table as the `xtable` example presented before.

## Cross-referencing

The use of the Rmarkdown equivalent of the \LaTeX cross-reference system
for figures, tables, equations, etc., is encouraged (using `[@<name>]`, equivalent of `\ref{<name>}` and `\label{<name>}`). That works well for citations in Rmarkdown, not so well for figures and tables. In that case, it is possible to revert to standard \LaTeX syntax.

## Double Spacing

If you need to double space your document for submission please use the `doublespace` option in the header.

# Bibliography

Link a `.bib` document via the YAML header, and bibliography will be printed at the very end (as usual). The default bibliography style is provided by Wiley as in `WileyNJD-AMA.bst`, do not delete that file.

Use the Rmarkdown equivalent of the \LaTeX citation system using `[@<name>]`. Example: [@Taylor1937], [@Knupp1999; @Kamm2000].

To include all citation from the `.bib` file, add `\nocite{*}` before the end of the document.

# Further information

All \LaTeX enviroments supported by the main template are supported here as well; see the `.tex` sample file [here](http://onlinelibrary.wiley.com/journal/10.1002/(ISSN)1097-0258/homepage/la_tex_class_file.htm) for more details and example.

### 2023-11-08 causal_query.R
causal query

@@ -59,8 +59,8 @@ model_taubate <- make_model("M -> C") %>% set_restrictions(non_decreasing("M", "
 # model_taubate1 <- make_model("M -> C; M <-> C") %>% 
 #   set_restrictions(labels = list(M = "M0"), keep = TRUE) # preciso rule out C.01_M.0 e C.01_M.1# i.e., não tem adverso.
 
-model_taubate1 <- make_model("M -> C; M <-> C") %>% 
-  set_restrictions(labels = list(C = list("00", "01", "11")), keep = TRUE) # rule out C.10_M.0 e C.10_M.1# i.e., não tem adverso.
+model_taubate1 <- make_model("O -> M -> C; M <-> C") %>%
+  set_restrictions(non_decreasing("M", "C"), keep=T) # rule out C.10_M.0 e C.10_M.1# i.e., não tem adverso.
 
 
 
@@ -106,7 +106,7 @@ model_taubate %>%
   query_model("C[M=1] - C[M=0]", n_draws = 10000, case_level = T) %>%
   kable
 
-data_taubate  <- data.frame(M = c(0,0,0,0, 1, 1, 1, 1), C = c(0, 0, 0, 0, 1, 1, 1, 1))
+data_taubate  <- data.frame(O = rep(1, 8), M = c(0,0,0,0, 1, 1, 1, 1), C = c(0, 0, 0, 0, 1, 1, 1, 1))
 compact_data <-  collapse_data(data_taubate, model_taubate) 
 
 compact_data1 <-  collapse_data(data_taubate, model_taubate1)
@@ -120,6 +120,35 @@ updated$causal_types %>% data.frame() %>% glimpse()
 updated1$posterior_distribution %>% 
   data.frame() %>%
   glimpse()
+
+mydf1 <- updated1$posterior_distribution %>% 
+  data.frame() 
+
+mydf1 %>%
+  mutate(ate = C.01_M.01*M.01 + C.01_M.10*M.10) %>%
+  summarise(mean_ate = mean(ate),
+            sd_ate = sd(ate),
+            q.025 = quantile(ate, .025),
+            q.975 = quantile(ate, .975))
+
+mydf1 %>%
+  mutate(ate = C.11_M.1*M.1 + C.11_M.0*M.0) %>%
+  summarise(mean_ate = mean(ate),
+            sd_ate = sd(ate),
+            q.025 = quantile(ate, .025),
[…]

### 2023-11-30 appendix.Rmd
appendix . Está com problema na reg bayesiana. Precisa entender o que é. Muito lento.

---
title: "Data Appendix"
author: "Manoel Galdino"
date: "2023-11-30"
output: 
  bookdown::pdf_document2:
    toc:false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)

```

```{r package loads}
library(data.table)
library(here)
library(janitor)
library(lubridate)
library(readxl)
library(tidyverse)
library(gt)
library(ipeadatar)
library(rstan)
library(arm)
library(rstanarm)
library(survey)
library(broom)
library(broom.mixed)
library(MetBrewer)
library(knitr)
library(ggplot2)
library(patchwork)

```

## R Markdown

We utilized several data sources in our analysis, with the primary dataset for the quantitative analysis, encompassing the outcome variable, originating from a single source.

The Fundo Nacional de Desenvolvimento da Educação (FNDE), operating under the Ministry of Education in Brazil, is responsible for implementing various policies, including the Proinfância Program. Launched in 2007, Proinfância supports the construction and renovation of schools and nurseries throughout Brazil. Municipalities and states seek funding from FNDE, and in certain cases, FNDE also offers a basic construction project that municipalities have the option to utilize. FNDE maintains a website, SIMEC (an acronym for 'Sistema Integrado de Monitoramento Execução e Controle'), which houses crucial information on all construction projects approved by FNDE. A public version of this data is available at: https://simec.mec.gov.br/painelObras/.

As the dataset undergoes periodic updates with new pieces of information, any alterations may lead to the loss of historical data. To maintain a comprehensive record, Transparência Brasil systematically downloaded spreadsheets from the SIMEC website. These spreadsheets serve as the foundation for the dataset used in our paper.

The initial spreadsheet was collected in May 2017, coinciding with the commencement of the Obra Transparente project. The subsequent spreadsheet was acquired post-project completion, in July 2019. The data set contains information about all construction works approved by FNDE over time. We restricted the analysis only to the kind of projects monitored by Obra Transparente.

## Construction completion

```{r loading data appendix}
load(here("Dados", "obras_inicio_projeto.Rdata"))
load(here("Dados", "obras_fim_seg_fase.Rdata"))

# simec23 <- fread(here("obra_transparente", "Dados", "simec 25-10-23 - simec.csv"), encoding = "UTF-8")
simec23 <- fread(here("Dados", "simec 25-10-23 - simec.csv"), encoding = "UTF-8")

# load(here("obra_transparente", "Dados", "obras_fim_seg_fase.Rdata"))

load(here("Dados", "obras_fim_seg_fase.Rdata"))

df_cidades_ot <- read_excel(here("Dados", "situacao obras_atual.xlsx"), 
                                           sheet = "SIMEC-Mai17", skip = 1) %>%
  clean_names() %>%
  filter(!is.na(id)) %>%
  dplyr::select(id, municipio, uf, situacao2, levant_os_jun_17) %>%
  mutate(indicator_ot = 1)

obras_inicio_projeto_ot <- obras_inicio_projeto %>%
  left_join(df_cidades_ot, by=join_by("municipio", "uf", "id"))

obras_inicio_projeto_ot <- obras_inicio_projeto_ot %>%
  mutate(concluida = grepl("Concluída", situacao))

aux_indicator_ot <- df_cidades_ot %>%
  distinct(municipio, uf) %>%
  mutate(indicator_muni_ot = 1)

obras_inicio_projeto_ot <- obras_inicio_projeto_ot %>%
  mutate(indicator_ot = ifelse(is.na(indicator_ot), 0, indicator_ot)) %>%
  left_join(aux_indicator_ot, by = join_by("municipio", "uf")) %>%
  mutate(indicator_muni_ot = ifelse(is.na(indicator_muni_ot), 0, indicator_muni_ot))

antes_projeto <- obras_inicio_projeto_ot %>%
  dplyr::filter(uf %in% c("SP", "PR", "SP", "SC", "RS", "MG")) %>%
  group_by(indicator_muni_ot, concluida) %>%
  summarise(contagem = n()) %>%
  mutate(total = sum(contagem),
         perc = round(contagem/total, 2))

antes_projeto <- antes_projeto %>%
  dplyr::filter(concluida == TRUE) %>%
  dplyr::select(-c(concluida, contagem, total)) %>%
  ungroup()

obras_fim_seg_fase <- obras_fim_seg_fase %>%
  mutate(concluida = as.numeric(grepl("Concluída", situacao)),
         id = as.numeric(id)) %>%
  left_join(df_cidades_ot, by=join_by("municipio", "uf", "id")) %>%
  mutate(indicator_ot = ifelse(is.na(indicator_ot), 0, indicator_ot)) %>%
  left_join(aux_indicator_ot, by = join_by("municipio", "uf")) %>%
  mutate(indicator_muni_ot = ifelse(is.na(indicator_muni_ot), 0, indicator_muni_ot))

depois_projeto <- obras_fim_seg_fase %>%
  dplyr::filter(uf %in% c("SP", "PR", "SP", "SC", "RS", "MG")) %>%
  group_by(indicator_muni_ot, concluida) %>%
  summarise(contagem = n()) %>%
  mutate(total = sum(contagem),
         perc = round(contagem/total, 2))

depois_projeto <- depois_projeto %>%
  dplyr::filter(concluida == TRUE) %>%
  dplyr::select(-c(concluida, contagem, total)) %>%
  ungroup()

```

Table \@ref(tab:basic-table) illustrates the changes in data before and after the project across the entire country. Notably, there is a significant increase in the completion rate, rising from 37% to 46%, representing an almost 10-percentage-point increase. This change aligns with expectations, considering that the denominator grows at a slower pace than the numerator. The numerator increases with each completion of a construction work, while the denominator expands only with a new funded project.

```{r basic-table}
df_before <- obras_inicio_projeto %>%
  mutate(concluida = as.numeric(grepl("Concluída", situacao))) %>%
  group_by(concluida) %>%
  summarise(num_works = n()) %>%
  mutate(total = sum(num_works)) %>%
  filter(concluida == 1)

df_after <- obras_fim_seg_fase %>%
  mutate(concluida = as.numeric(grepl("Concluída", situacao))) %>%
  group_by(concluida)%>%
  summarise(num_works = n()) %>%
  mutate(total = sum(num_works)) %>%
  filter(concluida == 1)

df1 <- bind_rows(df_before, df_after)

df1 %>%
  rename(date = concluida) %>%
  mutate(date = c("May 2017", "July 2019"),
         perc = scales::percent(round(num_works/total, 2))) %>%
  kable(col.names = c("Date", "Completed construction works", "Total works", "Completion percentage"),
        caption = "Summary of Data Collection Dates and Counts of Completed and Total Construction Works - Brazil")

```

In the main analysis, we restricted the sample to municipalities in the same states where the Obra Transparente project occurred. Table \@ref(tab:basic-table-s) presents a situation similar to that of the entire country, albeit with a higher baseline (11 percentage points above the whole country).

```{r basic-table-s}
obras_inicio_projeto_ot <- obras_inicio_projeto %>%
  left_join(df_cidades_ot, by=join_by("municipio", "uf", "id"))

df_before_s <- obras_inicio_projeto %>%
  dplyr::filter(uf %in% c("SP", "PR", "SP", "SC", "RS", "MG")) %>%
  mutate(concluida = as.numeric(grepl("Concluída", situacao))) %>%
  group_by(concluida) %>%
  summarise(num_works = n()) %>%
  mutate(total = sum(num_works)) %>%
  filter(concluida == 1)

df_after_s <- obras_fim_seg_fase %>%
  dplyr::filter(uf %in% c("SP", "PR", "SP", "SC", "RS", "MG")) %>%
  mutate(concluida = as.numeric(grepl("Concluída", situacao))) %>%
  group_by(concluida)%>%
  summarise(num_works = n()) %>%
  mutate(total = sum(num_works)) %>%
  filter(concluida == 1)

df2 <- bind_rows(df_before_s, df_after_s)

df2 %>%
  rename(date = concluida) %>%
  mutate(date = c("May 2017", "July 2019"),
         perc = scales::percent(round(num_works/total, 2))) %>%
  kable(col.names = c("Date", "Completed construction works", "Total works", "Completion percentage"),
        caption = "Summary of Data Collection Dates and Counts of Completed and Total Construction Works in Obra Transparente states")
```

Figure \@ref(fig:plot) presents a comparison of completion rates between restricted (municipalities in the Obra Transparente states operation) and unrestricted samples (the whole country), displayed across different dates (start and end of project).

```{r plot, echo=FALSE, fig.cap="Completion rates between Restricted and Unrestricted samples"}

df1 <- df1 %>%
  rename(date = concluida) %>%
  mutate(date = c("May 2017", "July 2019"),
         perc = scales::percent(round(num_works/total, 2)))

df2 <- df2 %>%
  rename(date = concluida) %>%
  mutate(date = c("May 2017", "July 2019"),
         perc = scales::percent(round(num_works/total, 2)))

combined_df <- bind_rows(
  mutate(df1, Sample = "Whole Country"),
  mutate(df2, Sample = "Restriced states")
)

library(ggplot2)

# Assuming combined_df is your dataframe
# You may need to install and load the tidyverse package if you haven't already: install.packages("tidyverse")

# Plotting
ggplot(combined_df, aes(x = date, y = perc, color = date)) +
  geom_point(position = position_dodge(width = 0.5), size = 3) +
  geom_linerange(
    aes(ymin = 0, ymax = perc, color = date),
    position = position_dodge(width = 0.5),
    linewidth = 1.2
  ) +
  facet_wrap(~Sample, ncol = 2, scales = "fixed") +
  labs(
    title = "Comparison of Completion Rates between Restricted and Unrestricted Samples",
    y = "Completion Rate (%)",
    x = NULL
  ) +
  theme_minimal() 
```

# Imbalance

The treatment is just a list of municipalities where the project occurred. To assess imbalance of treatment and control units, we used other metrics in the SIMEC data set (if a construction work is paralyzed or not, it it is in execution or not and percentage completed), since they are related to how hard it is to finish a construction.

Figure \@ref(fig:plot1) shows that there is indeed imbalance among construction works in the restricted sample when compared with the unrestricted sample. Although the rate of change seems to be similar from the beginning and end of project, the baseline is clearly different. It is also worthwhile to note that there are both more construction works in execution and paralyzed in the country as a whole than in the states of Obra Transparente. It is possible because we can also have planned construction (not started), cancelled and completed. Last, but not least, the mean execution rate is higher in the restricted sample, suggesting they were closer to completion in the beggining of the project. These data alone suggest systematic differences between samples.

```{r plot1, echo=FALSE, fig.cap="Completion rates between Restricted and Unrestricted samples"}

imb_before_s <- obras_inicio_projeto %>%
  dplyr::filter(uf %in% c("SP", "PR", "SP", "SC", "RS", "MG")) %>%
  mutate(paralyzed = as.numeric(grepl("Paralisada", situacao)),
         execution = as.numeric(grepl("Execução", situacao)),
         percentage_executed = percentual_de_execucao) %>%
  summarise(num_works = n(),
            num_paralyzed = sum(paralyzed),
            num_execution = sum(execution),
            perc_paralyzed = num_paralyzed/num_works,
            perc_execution = num_execution/num_works,
            mean_execution = mean(percentage_executed)/100) %>%
  mutate(date = "May 2017")

imb_before <- obras_inicio_projeto %>%
  mutate(paralyzed = as.numeric(grepl("Paralisada", situacao)),
         execution = as.numeric(grepl("Execução", situacao)),
         percentage_executed = percentual_de_execucao) %>%
  summarise(num_works = n(),
            num_paralyzed = sum(paralyzed),
            num_execution = sum(execution),
            perc_paralyzed = num_paralyzed/num_works,
            perc_execution = num_execution/num_works,
            mean_execution = mean(percentage_executed)/100) %>%
  mutate(date = "May 2017")

imb_after_s <- obras_fim_seg_fase %>%
  dplyr::filter(uf %in% c("SP", "PR", "SP", "SC", "RS", "MG")) %>%
  mutate(paralyzed = as.numeric(grepl("Paralisada", situacao)),
         execution = as.numeric(grepl("Execução", situacao)),
         percentage_executed = percentual_de_execucao) %>%
  summarise(num_works = n(),
            num_paralyzed = sum(paralyzed),
            num_execution = sum(execution),
            perc_paralyzed = num_paralyzed/num_works,
            perc_execution = num_execution/num_works,
            mean_execution = mean(percentage_executed)/100) %>%
  mutate(date = "July 2019")

imb_after <- obras_fim_seg_fase %>%
  mutate(paralyzed = as.numeric(grepl("Paralisada", situacao)),
         execution = as.numeric(grepl("Execução", situacao)),
         percentage_executed = percentual_de_execucao) %>%
  summarise(num_works = n(),
            num_paralyzed = sum(paralyzed),
            num_execution = sum(execution),
            perc_paralyzed = num_paralyzed/num_works,
            perc_execution = num_execution/num_works,
            mean_execution = mean(percentage_executed)/100) %>%
  mutate(date = "July 2019")

combined_df <- bind_rows(
  mutate(imb_before_s, Sample = "Restriced states"),
  mutate(imb_before, Sample = "Whole country"),
  mutate(imb_after_s, Sample = "Restriced states"),
  mutate(imb_after, Sample = "Whole country")
  )

df_combined <- combined_df
# Plotting

# Function to create a plot for each variable
create_plot <- function(data, y_variable, title, y_label) {
  ggplot(data, aes(x = date, color = date)) +
    geom_point(aes(y = !!sym(y_variable)), position = position_jitterdodge(jitter.width = 0.2, dodge.width = 0.75), size = 3) + scale_y_continuous(labels = scales::percent) +
    geom_linerange(
      aes(ymin = 0, ymax = !!sym(y_variable)),
      position = position_dodge(width = 0.75),
      linewidth = 1.2
    ) +
    facet_wrap(~Sample, scales = "fixed") +
    labs(
      title = title,
      y = y_label,
      x = NULL,
      caption = "Data source: Your Data Source"
    ) +
    theme_minimal() +
    theme(legend.position = "none")
}

# Create individual plots
plot_execution <- create_plot(df_combined, "perc_execution","", "Percentage of construction works in execution")
plot_paralyzed <- create_plot(df_combined, "perc_paralyzed", "", "Percentage of construction works paralyzed")
plot_mean_execution <- create_plot(df_combined, "mean_execution", "", "Mean Execution rate")

# Arrange the plots
combined_plots <- plot_execution + plot_paralyzed + plot_mean_execution

# Print the combined plots
print(combined_plots)

```

In any case, we also ran standard ols regression, adjusting for such variables, as a robustness check.

```{r loading-processing ipea data,  message=FALSE, echo=FALSE, cache=TRUE}
aux_muni <- geobr::lookup_muni(code_muni = "all") %>%
  dplyr::select(-c(name_state, name_intermediate))

ipea_idhm <- ipeadatar::ipeadata("ADH_IDHM") %>%
  dplyr::filter(date > "2001-01-1" & as.character(uname) == "Municipality") %>%
  rename(idhm = value)

ipea_pea18 <- ipeadatar::ipeadata("ADH_PEA18M")  %>%
  dplyr::filter(date > "2001-01-1" & as.character(uname) == "Municipality") %>%
  rename(pea18 = value)

ipea_ext_pobres <- ipeadatar::ipeadata("ADH_PIND")  %>%
  dplyr::filter(date > "2001-01-1" & as.character(uname) == "Municipality") %>%
  rename(ext_pobres = value)

ipea_ext_pobres_neg <- ipeadatar::ipeadata("ADH_PIND_NEG")  %>%
  dplyr::filter(date > "2001-01-1" & as.character(uname) == "Municipality") %>%
  rename(ext_pobres_negros = value)

ipea_rpc <- ipeadatar::ipeadata("ADH_RDPC")  %>%
  dplyr::filter(date > "2001-01-1" & as.character(uname) == "Municipality") %>%
  rename(rpc = value)

ipea_rpc_mulheres <- ipeadatar::ipeadata("ADH_RDPC_MUL")  %>%
  dplyr::filter(date > "2001-01-1" & as.character(uname) == "Municipality") %>%
  rename(rpc_mulheres = value)

ipea_rpc_negros <- ipeadatar::ipeadata("ADH_RDPC_NEG")  %>%
  dplyr::filter(date > "2001-01-1" & as.character(uname) == "Municipality") %>%
  rename(rpc_negros = value)

ipea_ext_prop_pobres <- ipeadatar::ipeadata("ADH_PMPOB")  %>%
  dplyr::filter(date > "2001-01-1" & as.character(uname) == "Municipality") %>%
  rename(ext_prop_pobres = value)

ipea_10p_ricos_desigualdade <- ipeadatar::ipeadata("ADH_PREN10RICOS")  %>%
  dplyr::filter(date > "2001-01-1" & as.character(uname) == "Municipality") %>%
  rename(p10_ricos_desigualdade = value)

ipea_freq_escola_15_17 <- ipeadatar::ipeadata("ADH_T_FREQ15A17")  %>%
  dplyr::filter(date > "2001-01-1" & as.character(uname) == "Municipality") %>%
  rename(freq_escola_15_1 = value)

ipea_analfabetismo <- ipeadatar::ipeadata("ADH_T_ANALF15M")  %>%
  dplyr::filter(date > "2001-01-1" & as.character(uname) == "Municipality") %>%
  rename(analfabetismo = value)

pop2010 <- ribge::habitantes2010 %>%
  mutate(tcode = as.integer(paste0(codigo_uf, codigo_munic)))

ipea_final <- ipea_idhm %>%
  inner_join(aux_muni, by = join_by(tcode == code_muni)) %>%
  inner_join(ipea_pea18, by = "tcode") %>%
  inner_join(ipea_ext_pobres, by = "tcode") %>%
  inner_join(ipea_rpc, by = "tcode") %>%
  inner_join(ipea_ext_prop_pobres, by = "tcode") %>%
  inner_join(ipea_10p_ricos_desigualdade, by = "tcode") %>%
  inner_join(ipea_freq_escola_15_17, by = "tcode") %>%
  inner_join(ipea_analfabetismo, by = "tcode") %>%
  inner_join(pop2010, by = "tcode") %>%
  dplyr::select(-contains("date")) %>%
  dplyr::select(-contains("uname")) %>%
  dplyr::select(-starts_with("code"))
```

```{r fitting bayesian model, message=FALSE, echo=FALSE, cache = TRUE}
aux_indicator_ot <- df_cidades_ot %>%
  distinct(municipio, uf) %>%
  mutate(indicator_muni_ot = 1)

obras_inicio_projeto_ot <- obras_inicio_projeto_ot %>%
  left_join(aux_indicator_ot, by = join_by("municipio", "uf")) %>%
  mutate(indicator_muni_ot = ifelse(is.na(indicator_muni_ot), 0, indicator_muni_ot))

aux_muni1 <- aux_muni %>%
  mutate(name_muni1 = tolower(iconv(name_muni, "UTF-8",  "ASCII//TRANSLIT")))

df_balancing_aux <- obras_inicio_projeto_ot %>%
  mutate(concluida = as.numeric(grepl("Concluída", situacao)))  %>%
  mutate(municipio1 = tolower(iconv(municipio, "UTF-8",  "ASCII//TRANSLIT"))) %>%
  inner_join(aux_muni1, by = join_by(municipio1  == name_muni1, uf == abbrev_state)) %>%
  inner_join(ipea_final, by = join_by(code_muni == tcode)) %>%
  mutate(perc_pea18 =pea18/populacao,
         log_pop = log(populacao),
         log_renda = log(rpc*populacao),
         log_rpc = log(rpc),
         tipo_do_projeto = ifelse(grepl("Bloco Estrutural" ,tipo_do_projeto),
                                  "Projeto Tipo B ou C - Bloco Estrutural", tipo_do_projeto))

df_balancing_aux1 <- df_balancing_aux %>%
  mutate(concluida_num = as.numeric(concluida))

pre_dados <- df_balancing_aux %>%
  dplyr::select(id, concluida) %>%
  rename(concluida_pre = concluida) %>%
  mutate(id = as.numeric(id))

obras_fim_seg_fase <- obras_fim_seg_fase %>%
  mutate(concluida = as.numeric(grepl("Concluída", situacao)),
         id = as.numeric(id))

data_pos <- obras_fim_seg_fase %>%
  mutate(municipio1 = tolower(iconv(municipio, "UTF-8",  "ASCII//TRANSLIT"))) %>%
  inner_join(aux_muni1, by = join_by(municipio1  == name_muni1, uf == abbrev_state)) %>%
  inner_join(ipea_final, by = join_by(code_muni == tcode)) %>%
  mutate(perc_pea18 =pea18/populacao,
         log_pop = log(populacao),
         log_renda = log(rpc*populacao),
         log_rpc = log(rpc)) %>%
  inner_join(pre_dados, by = "id") %>%
  dplyr::filter(concluida_pre == FALSE) %>%
  mutate(concluida_num = as.numeric(concluida))

df_balancing_aux1 <- df_balancing_aux1 %>%
  dplyr::select(concluida_num , indicator_muni_ot, code_muni, log_rpc, ext_pobres, freq_escola_15_1,analfabetismo,
                log_renda, p10_ricos_desigualdade, percentual_de_execucao, municipio) %>%
  mutate(code_muni = as.factor(code_muni))

te_spec_nr <- formula(concluida_num ~ log_rpc  + ext_pobres + freq_escola_15_1 + analfabetismo +
                     log_renda  +  p10_ricos_desigualdade + percentual_de_execucao + indicator_muni_ot + (1 | code_muni) + .)

#treatment effect without replacement

set.seed(120)
reg_ps_pre <- stan_lmer(te_spec_nr, data=df_balancing_aux1, iter = 100)

## After
set.seed(120)
reg_ps_pos <- stan_lmer(te_spec_nr, data=df_balancing_aux_post_se[matches_pos$match.ind,], iter = 4000, refresh=0)

```

```{r processing bayes fit, echo=FALSE,  message=FALSE}
# posterior draws

##
# Before
##

b1_pre_sims <- as.matrix(reg_ps_pre, 
                     pars = "indicator_muni_ot")

# Posterior mean and SD of treatment
b1_mean_pre <- mean(b1_pre_sims) # posterior mean
b1_sd_pre <- sd(b1_pre_sims)       # posterior SD

# Posterior median and 95% credible interval
b1_quant_pre <- quantile(b1_pre_sims,   probs = c(0.025, 0.50, 0.975))

b1_quant_pre <- data.frame(t(b1_quant_pre))
names(b1_quant_pre) <- c("Q2.5", "Q50", "Q97.5")

# Combine summary statistics of posterior simulation draws
b1_df_pre_cred <- data.frame(variables = "ATT before project",
                             post_mean = b1_mean_pre,
                             post_sd = b1_sd_pre,
                             b1_quant_pre[2], 
                             b1_quant_pre[1],
                             b1_quant_pre[3])

##
# After
##
b1_sims_after <- as.matrix(reg_ps_pos, 
                     pars = "indicator_muni_ot")

# Compute mean, SD, median, and 95% credible interval of treatment

# Posterior mean and SD of treatment
b1_mean_after <- mean(b1_sims_after) # posterior mean
b1_sd_after <- sd(b1_sims_after)       # posterior SD

# Posterior median and 95% credible interval
b1_quant_after <- quantile(b1_sims_after,   probs = c(0.025, 0.50, 0.975))

b1_quant_after <- data.frame(t(b1_quant_after))
names(b1_quant_after) <- c("Q2.5", "Q50", "Q97.5")

# Combine summary statistics of posterior simulation draws
b1_df_after_cred <- data.frame(variables = "ATT After project",
                             post_mean = b1_mean_after,
                             post_sd = b1_sd_after,
                             b1_quant_after[2], 
                             b1_quant_after[1],
                             b1_quant_after[3])
b1_df <- bind_rows(b1_df_pre_cred, b1_df_after_cred)
```

```{r table2, echo=FALSE,  message=FALSE, results='asis'}

b1_df %>% gt() %>%
  tab_header(
    title = "Effect of local OSB social monitoring on construction delivery rates",
    subtitle = "Posterior probabilities") %>%
  cols_label(
    variables = "Variables",
    post_mean = "Mean",
    post_sd = "Sd",
    Q50 = "Median",
    Q2.5 = "2.5% CI",
    Q97.5 = "97.5% CI"
  ) %>%
  fmt_number(
    columns = c(post_mean, post_sd, Q50, Q2.5, Q97.5 ),
    decimals = 3,
    use_seps = FALSE
  ) %>%
  tab_source_note(
    source_note = "452 observations for the pre-treatment period and 320 observations for the post-treatment period, resulting from the matching procedure, and encompassing municipalities in the same states as municipalities of Obra Transparente"
  ) %>%
  tab_options(., container.width = 500, container.height =     500)
```

### 2023-12-01 appendix.Rmd
Onde eu descubro que tem multiclonieraridade na aostra com todo mundo e ols não é significativo

@@
   bookdown::pdf_document2:
-    toc:false
+    figsintext : yes
 ---
@@
 library(data.table)
+library(stargazer)
+library(fixest)
 library(here)
@@
 library(rstanarm)
+library(brms)
 library(survey)
@@
 
-## R Markdown
+# Appendix
 
@@
 In the main analysis, we restricted the sample to municipalities in the same states where the Obra Transparente project occurred.
+The reason is that there is perfect multicolinearity between our treatment and seven other control variables (mesured at the municipality level) in the unrestricted sample (log of per capita income, school frequency, log of GDP, share of poor families, illiteracy rate, and an inequality measure).
+
+We present simple descriptive statistics and visualizations to show that the change is similar in our outcome variable considering the restricted and unrestricted sample.
+
 Table \@ref(tab:basic-table-s) presents a situation similar to that of the entire country, albeit with a higher baseline (11 percentage points above the whole country).
@@
   rename(date = concluida) %>%
-  mutate(date = c("May 2017", "July 2019"),
+  mutate(date = c("05-17", "07-19"),
          perc = scales::percent(round(num_works/total, 2)))
@@
 
-# Imbalance
+## Imbalance
 
@@
             mean_execution = mean(percentage_executed)/100) %>%
-  mutate(date = "May 2017")
+  mutate(date = "05-17")
 
@@
             mean_execution = mean(percentage_executed)/100) %>%
-  mutate(date = "May 2017")
+  mutate(date = "05-17")
 
 imb_after_s <- obras_fim_seg_fase %>%
-  dplyr::filter(uf %in% c("SP", "PR", "SP", "SC", "RS", "MG")) %>%
+  dplyr::filter(uf %in% c("SP", "PR", "SC", "RS", "MG")) %>%
   mutate(paralyzed = as.numeric(grepl("Paralisada", situacao)),
@@
             mean_execution = mean(percentage_executed)/100) %>%
-  mutate(date = "July 2019")
+  mutate(date = "07-19")
 
@@
 print(combined_plots)
-
 ```
@@
 
-```{r fitting bayesian model, message=FALSE, echo=FALSE, cache = TRUE}
+```{r processing reg, message=FALSE, echo=FALSE}
 aux_indicator_ot <- df_cidades_ot %>%
@@
          tipo_do_projeto = ifelse(grepl("Bloco Estrutural" ,tipo_do_projeto),
-                                  "Projeto Tipo B ou C - Bloco Estrutural", tipo_do_projeto))
+                                  "Projeto Tipo B ou C - Bloco Estrutural", tipo_do_projeto)) %>%
+  mutate(concluida_num = as.numeric(concluida))
 
 df_balancing_aux1 <- df_balancing_aux  %>%
-  mutate(concluida_num = as.numeric(concluida))
+  dplyr::filter(uf.x %in% c("SP", "MG", "RS", "PR", "SC"))
 
@@
 
-#treatment effect without replacement
+```
+
+Tables below presents results from standard, frequentist regression (ols, fixed effects, both with clustered standard errors) and Bayesian regression (linear model with varying intercept).
+
+```{r fitting, echo=FALSE, message=FALSE, results="asis"}
+
+# Simple linear regression
+fit_ols <- feols(concluida_num ~ indicator_muni_ot + log_rpc +
+                   ext_pobres + freq_escola_15_1 + analfabetismo + log_renda + p10_ricos_desigualdade + percentual_de_execucao, data = df_balancing_aux1, cluster = "code_muni" )
+
+fit_fixed <- feols(concluida_num ~ indicator_muni_ot + log_rpc + ext_pobres + freq_escola_15_1 + analfabetismo + log_renda + p10_ricos_desigualdade + percentual_de_execucao |code_muni, data = df_balancing_aux1, cluster = "code_muni")
+
+etable(list(fit_ols, fit_fixed), tex=TRUE)
 
 set.seed(120)
-reg_ps_pre <- stan_lmer(te_spec_nr, data=df_balancing_aux1, iter = 100)
+rstan_options(auto_write = TRUE)
+options(mc.cores = parallel::detectCores())
+# system.time(reg_ps_pre <- brm(te_spec_nr, data=df_balancing_aux1, iter = 100, cores = 4, chains = 4))
+# reg_ps_pre <- stan_lmer(te_spec_nr, data=df_balancing_aux1, iter = 100)
 
 ## After
-set.seed(120)
-reg_ps_pos <- stan_lmer(te_spec_nr, data=df_balancing_aux_post_se[matches_pos$match.ind,], iter = 4000, refresh=0)
+# set.seed(120)
+# reg_ps_pos <- stan_lmer(te_spec_nr, data=df_balancing_aux_post_se[matches_pos$match.ind,], iter = 4000, refresh=0)
 
@@
 
-b1_pre_sims <- as.matrix(reg_ps_pre, 
-                     pars = "indicator_muni_ot")
+# b1_pre_sims <- as.matrix(reg_ps_pre, 
+#                      pars = "indicator_muni_ot")
 
 # Posterior mean and SD of treatment
-b1_mean_pre <- mean(b1_pre_sims) # posterior mean
-b1_sd_pre <- sd(b1_pre_sims)       # posterior SD
+# b1_mean_pre <- mean(b1_pre_sims) # posterior mean
+# b1_sd_pre <- sd(b1_pre_sims)       # posterior SD
+#
 
 # Posterior median and 95% credible interval
-b1_quant_pre <- quantile(b1_pre_sims,   probs = c(0.025, 0.50, 0.975))
-
-b1_quant_pre <- data.frame(t(b1_quant_pre))
-names(b1_quant_pre) <- c("Q2.5", "Q50", "Q97.5")
+# b1_quant_pre <- quantile(b1_pre_sims,   probs = c(0.025, 0.50, 0.975))
+# 
+# b1_quant_pre <- data.frame(t(b1_quant_pre))
+# names(b1_quant_pre) <- c("Q2.5", "Q50", "Q97.5")
 
 # Combine summary statistics of posterior simulation draws
-b1_df_pre_cred <- data.frame(variables = "ATT before project",
-                             post_mean = b1_mean_pre,
-                             post_sd = b1_sd_pre,
-                             b1_quant_pre[2], 
-                             b1_quant_pre[1],
-                             b1_quant_pre[3])
+# b1_df_pre_cred <- data.frame(variables = "ATT before project",
+#                              post_mean = b1_mean_pre,
+#                              post_sd = b1_sd_pre,
+#                              b1_quant_pre[2], 
+#                              b1_quant_pre[1],
+#                              b1_quant_pre[3])
+#
 
@@
 ##
-b1_sims_after <- as.matrix(reg_ps_pos, 
-                     pars = "indicator_muni_ot")
-
+# b1_sims_after <- as.matrix(reg_ps_pos, 
+#                      pars = "indicator_muni_ot")
+#   
 # Compute mean, SD, median, and 95% credible interval of treatment
@@
 # Posterior mean and SD of treatment
-b1_mean_after <- mean(b1_sims_after) # posterior mean
-b1_sd_after <- sd(b1_sims_after)       # posterior SD
-
-# Posterior median and 95% credible interval
-b1_quant_after <- quantile(b1_sims_after,   probs = c(0.025, 0.50, 0.975))
-
-b1_quant_after <- data.frame(t(b1_quant_after))
-names(b1_quant_after) <- c("Q2.5", "Q50", "Q97.5")
+# b1_mean_after <- mean(b1_sims_after) # posterior mean
+# b1_sd_after <- sd(b1_sims_after)       # posterior SD
+# 
+# # Posterior median and 95% credible interval
+# b1_quant_after <- quantile(b1_sims_after,   probs = c(0.025, 0.50, 0.975))
+# 
+# b1_quant_after <- data.frame(t(b1_quant_after))
+# names(b1_quant_after) <- c("Q2.5", "Q50", "Q97.5")
 
 # Combine summary statistics of posterior simulation draws
-b1_df_after_cred <- data.frame(variables = "ATT After project",
-                             post_mean = b1_mean_after,
-                             post_sd = b1_sd_after,
-                             b1_quant_after[2], 
-                             b1_quant_after[1],
-                             b1_quant_after[3])
-b1_df <- bind_rows(b1_df_pre_cred, b1_df_after_cred)
+# b1_df_after_cred <- data.frame(variables = "ATT After project",
+#                              post_mean = b1_mean_after,
+#                              post_sd = b1_sd_after,
+#                              b1_quant_after[2], 
+#                              b1_quant_after[1],
+#                              b1_quant_after[3])
+# b1_df <- bind_rows(b1_df_pre_cred, b1_df_after_cred)
 ```
@@
 
-b1_df %>% gt() %>%
-  tab_header(
-    title = "Effect of local OSB social monitoring on construction delivery rates",
-    subtitle = "Posterior probabilities") %>%
-  cols_label(
-    variables = "Variables",
-    post_mean = "Mean",
-    post_sd = "Sd",
-    Q50 = "Median",
-    Q2.5 = "2.5% CI",
-    Q97.5 = "97.5% CI"
-  ) %>%
-  fmt_number(
-    columns = c(post_mean, post_sd, Q50, Q2.5, Q97.5 ),
-    decimals = 3,
-    use_seps = FALSE
-  ) %>%
-  tab_source_note(
-    source_note = "452 observations for the pre-treatment period and 320 observations for the post-treatment period, resulting from the matching procedure, and encompassing municipalities in the same states as municipalities of Obra Transparente"
-  ) %>%
-  tab_options(., container.width = 500, container.height =     500)
+# b1_df %>% gt() %>%
+#   tab_header(
+#     title = "Effect of local OSB social monitoring on construction delivery rates",
+#     subtitle = "Posterior probabilities") %>%
+#   cols_label(
+#     variables = "Variables",
+#     post_mean = "Mean",
+#     post_sd = "Sd",
+#     Q50 = "Median",
+#     Q2.5 = "2.5% CI",
+#     Q97.5 = "97.5% CI"
+#   ) %>%
+#   fmt_number(
+#     columns = c(post_mean, post_sd, Q50, Q2.5, Q97.5 ),
+#     decimals = 3,
+#     use_seps = FALSE
+#   ) %>%
+#   tab_source_note(
+#     source_note = "452 observations for the pre-treatment period and 320 observations for the post-treatment period, resulting from the matching procedure, and encompassing municipalities in the same states as municipalities of Obra Transparente"
+#   ) %>%
+#   tab_options(., container.width = 500, container.height =     500)
+
 ```

### 2023-12-04 Untitled/Untitled.Rmd
did em, vez de matching

@@
     surname: Paiva
-    affiliation: Alandar Consulting - Germany
+    affiliation: Alandar Consulting - Brazil
 acknowledgements: |
@@
 output: rticles::aea_article
+
 ---
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = FALSE, warning=FALSE)
+```
 
@@
 library(ipeadatar)
-library(rstan)
-library(arm)
-library(rstanarm)
-library(survey)
-library(broom)
-library(broom.mixed)
-library(MetBrewer)
+library(fixest)
+library(knitr)
 ```
@@
 obras_inicio_projeto_ot <- obras_inicio_projeto_ot %>%
-  mutate(concluida = grepl("Concluída", situacao))
-
-aux_indicator_ot <- df_cidades_ot %>%
-  distinct(municipio, uf) %>%
-  mutate(indicator_muni_ot = 1)
-
-obras_inicio_projeto_ot <- obras_inicio_projeto_ot %>%
-  mutate(indicator_ot = ifelse(is.na(indicator_ot), 0, indicator_ot)) %>%
-  left_join(aux_indicator_ot, by = join_by("municipio", "uf")) %>%
-  mutate(indicator_muni_ot = ifelse(is.na(indicator_muni_ot), 0, indicator_muni_ot))
+  mutate(concluida = grepl("Concluída", situacao),
+         indicator_ot = ifelse(is.na(indicator_ot), 0, indicator_ot)) %>%
+  group_by(municipio) %>%
+  mutate(indicator_muni_ot = max(indicator_ot)) %>%
+  ungroup()
 
@@
   mutate(indicator_ot = ifelse(is.na(indicator_ot), 0, indicator_ot)) %>%
-  left_join(aux_indicator_ot, by = join_by("municipio", "uf")) %>%
-  mutate(indicator_muni_ot = ifelse(is.na(indicator_muni_ot), 0, indicator_muni_ot))
+  group_by(municipio) %>%
+  mutate(indicator_muni_ot = max(indicator_ot)) %>%
+  ungroup()
 
@@
 For the quantitative analysis, we use administrative data about construction works data by municipalities and socio-demographic data on municipalities.
-The questions asked in the survey as well the aggregate answered are presented in annex B.
+A detailed description of the data is provided in the appendix.
 
@@
 To do so, we collected data on school and nursery construction projects across the entire country, encompassing over two thousand municipalities and more than 14 thousand construction projects, spanning all phases from planning to execution and completion.
-The @ref(tab:table1) below provides descriptive statistics for these construction projects.
+The table 1 below provides descriptive statistics for these construction projects.
 
+Our ideal objective would be to compare the project's effects on the rate of delivery across all units.
 When comparing "treated" and "untreated" units, there is difference between the groups, as show below by the percentage of construction works within both groups before the project started.
+As a result, we can't simply fit a regression comparing before and after to estimate the Average Treatment Effect (ATE).
 
@@
   cols_label(
-    indicator_muni_ot = "# of participating cities",
+    indicator_muni_ot = "Participating cities",
     perc.x = "% (Before Project)",
@@
 
-Our primary objective is to compare the project's effects on the rate of delivery.
-To estimate the Average Treatment Effect on the Treated (ATT), we employed a matching strategy [@ho_etal2007; @rubin_1973] with a Bayesian logistic regression to create the propensity scores.
-Balance was successful after matching.
-We also applied the same procedure to pre-project data to ensure that there were no substantial differences between the treated and control groups.
-
-We estimate all models using the a varying-intercept regression equation [@gelman_2006]:
+However, it is possible to estimate the Average Treatment Effect on the Treated (ATT), by employing a difference-in-difference (DiD) identification strategy.
+Our main specification model used the following regression equation:
 
 $$
-Y_i = \alpha + \beta_1 T_i + \gamma X_i + \theta Z_i + \epsilon_i
+Y_{it} = \alpha + \beta_1 treatment_{it} + \beta_2 time_{it} + \beta_3treatment_{it} \cdot time_{it} + \theta Z_{it} + \epsilon_{it}
 $$
 
-Where $i$ indexes the construction units, $Y_i$ is $1$ if a construction work is finished and $0$ otherwise.
-$\alpha$ represents the intercept, $\beta$ denotes the average treatment effect on the treated (ATT), and $T_i$ is a binary treatment indicator (whether the municipality is part of Obra Transparent or not).
-Symbol $\gamma$ is a vector of varying intercepts, $X_i$ is a matrix of random effects for Brazilian municipalities, $\theta$ is a vector of control variables, and $Z_i$ is an array of control variables for case $i$.
-The error term is represented by $\epsilon_i$.
-We employed a Bayesian model with rstanarm [@goodrich_etal2023] with default weakly informative priors on the parameters [@gelman_etal2008].
+Where $i$ indexes the construction units and $t$ the time (before or after the project), $Y_it$ is $1$ if a construction work is finished at time $t$ and $0$ otherwise.
+$\alpha$ represents the intercept, $\beta3$ estimates the average treatment effect on the treated (ATT), and $treatment_{it}$ is a binary treatment indicator (whether the municipality is part of Obra Transparent or not).
+The $\theta$ is a vector of control variables, and $Z_i$ is an array of control variables for case $it$.
+The error term is represented by $\epsilon_{it}$.
 
-The table below presents estimates for the causal effect on the treated units regarding the change in completion rates before and after the project.
-
-```{r prep data matching,  message=FALSE, echo=FALSE, cache=TRUE}
+```{r prep data,  message=FALSE, echo=FALSE, cache=TRUE}
 
@@
 
-Table (insert ref number) summarizes the main results of the regression.
-The first row presents the results for the regression before the project started, where we expect the effect of the project to be zero, since it didn't exist.
-The second row shows the effect after the end of the project, when we expect the impact to be positive.
-The first column is an estimate of the posterior mean of the impact of the project and the second one is the posterior standard deviation of the estimate.
-We also present posterior median and $2.5%$ and $97.5%$ quantiles, in order to quantify the uncertainty around the estimates with a 95% credibility interval.
-
-The hypothesis are corroborated, and we did not find an effect before the starting of the project, but found an effect aftet the end of the project.
-On average, a city that received the project Obra Transparente increases its delivery rate by almost 10%.
+Table \@ref(tab:table2) summarizes the main results of the regression.
+.All models (with and without clustered standard errors) shows a positive treatment effect.
+In our preferred specification, with controls, the effect of the project on the treated units is 10 percentage points, i.e, a municipality with monitoring by project Obra Transparente had on average 10pp more constructions completed than what we would observe in absence of the treatment.
 These results support our argument and the qualitative evidence we presented that sustained and costly bottom-up accountability improve public policies.
 
-```{r pscore, message=FALSE, echo=FALSE}
+```{r prep did, message=FALSE, echo=FALSE}
+df_balancing_aux_se <- df_balancing_aux_se %>%
+  mutate(time = 0) %>%
+  dplyr::select(-cep)
 
-# these are the no redundancy covariates
-covs.nr <- c('perc_pea18', 'ext_pobres', 'log_rpc', 'p10_ricos_desigualdade', 'freq_escola_15_1', 'analfabetismo',
-             'log_renda', 'log_pop', 'percentual_de_execucao')
+df_balancing_aux_post_se <- df_balancing_aux_post_se %>%
+  mutate(time = 1) %>%
+  dplyr::select(-cep)
 
-# pscore estimation formula with original covariates
-
-ps_spec <- formula(indicator_muni_ot ~ log_rpc  + ext_pobres + freq_escola_15_1 + analfabetismo +
-                     log_renda   +  p10_ricos_desigualdade + percentual_de_execucao)
-
-# Estimation of pscores using stan_glm
-set.seed(1234)
-ps_fit_pre <- stan_glm(ps_spec, family=binomial(link='logit'), 
-                     data=df_balancing_aux_se, algorithm='optimizing', refresh=0, iter = 2000)
-
-set.seed(1234)
-ps_fit_pos <- stan_glm(ps_spec, family=binomial(link='logit'), 
-                     data=df_balancing_aux_post_se, algorithm='optimizing', refresh=0, iter = 2000)
-
-# extracting logit pscores
-pscores_pre <- apply(posterior_linpred(ps_fit_pre), 2, mean)
-
-pscores_pos <- apply(posterior_linpred(ps_fit_pos), 2, mean)
-
-# matching
-#matching without replacement, original formula
-matches_pre <- matching(z=df_balancing_aux_se$indicator_muni_ot, score=pscores_pre, replace=FALSE)
-matched_pre <- df_balancing_aux_se[matches_pre$match.ind,]
-
-matches_pos <- matching(z=df_balancing_aux_post_se$indicator_muni_ot, score=pscores_pos, replace=FALSE)
-matched_pos <- df_balancing_aux_post_se[matches_pos$match.ind,]
+df_did <- bind_rows(df_balancing_aux_se,df_balancing_aux_post_se )
 
@@
 
-```{r fitting bayesian model, message=FALSE, echo=FALSE, cache = TRUE}
+```{r did model, message=FALSE, echo=FALSE, cache = TRUE}
+library(fixest)
+set.seed(120)
 
-df_balancing_aux_se <- df_balancing_aux_se %>%
-  dplyr::select(concluida_num , indicator_muni_ot, code_muni, log_rpc, ext_pobres, freq_escola_15_1,analfabetismo,
-                log_renda, p10_ricos_desigualdade, percentual_de_execucao, municipio)
+did_model1 <- feols(concluida_num  ~ time + indicator_muni_ot + time:indicator_muni_ot + log_rpc  + ext_pobres + freq_escola_15_1 + analfabetismo + log_renda   +  p10_ricos_desigualdade + percentual_de_execucao, data = df_did, cluster = "code_muni")
 
-te_spec_nr <- update(ps_spec, concluida_num ~ indicator_muni_ot + (1 | code_muni) + .)
+did_model2 <- feols(concluida_num  ~ time + indicator_muni_ot + time:indicator_muni_ot + log_rpc  + ext_pobres + freq_escola_15_1 + analfabetismo + log_renda   +  p10_ricos_desigualdade + percentual_de_execucao, data = df_did)
 
-#treatment effect without replacement
+did_model0 <- feols(concluida_num  ~ time + indicator_muni_ot + time:indicator_muni_ot, data = df_did)
 
-set.seed(120)
-reg_ps_pre <- stan_lmer(te_spec_nr, data=df_balancing_aux_se[matches_pre$match.ind,], iter = 4000, refresh=0)
-
-## After
-set.seed(120)
-reg_ps_pos <- stan_lmer(te_spec_nr, data=df_balancing_aux_post_se[matches_pos$match.ind,], iter = 4000, refresh=0)
-
-```
-
-```{r processing bayes fit, echo=FALSE,  message=FALSE}
-# posterior draws
-
-##
-# Before
-##
-
-b1_pre_sims <- as.matrix(reg_ps_pre, 
-                     pars = "indicator_muni_ot")
-
-# Posterior mean and SD of treatment
-b1_mean_pre <- mean(b1_pre_sims) # posterior mean
-b1_sd_pre <- sd(b1_pre_sims)       # posterior SD
-
-# Posterior median and 95% credible interval
-b1_quant_pre <- quantile(b1_pre_sims,   probs = c(0.025, 0.50, 0.975))
-
-b1_quant_pre <- data.frame(t(b1_quant_pre))
-names(b1_quant_pre) <- c("Q2.5", "Q50", "Q97.5")
-
-# Combine summary statistics of posterior simulation draws
-b1_df_pre_cred <- data.frame(variables = "ATT before project",
-                             post_mean = b1_mean_pre,
-                             post_sd = b1_sd_pre,
-                             b1_quant_pre[2], 
-                             b1_quant_pre[1],
-                             b1_quant_pre[3])
-
-##
-# After
-##
-b1_sims_after <- as.matrix(reg_ps_pos, 
-                     pars = "indicator_muni_ot")
-
-# Compute mean, SD, median, and 95% credible interval of treatment
-
-# Posterior mean and SD of treatment
-b1_mean_after <- mean(b1_sims_after) # posterior mean
-b1_sd_after <- sd(b1_sims_after)       # posterior SD
-
-# Posterior median and 95% credible interval
-b1_quant_after <- quantile(b1_sims_after,   probs = c(0.025, 0.50, 0.975))
-
-b1_quant_after <- data.frame(t(b1_quant_after))
-names(b1_quant_after) <- c("Q2.5", "Q50", "Q97.5")
-
-# Combine summary statistics of posterior simulation draws
-b1_df_after_cred <- data.frame(variables = "ATT After project",
-                             post_mean = b1_mean_after,
-                             post_sd = b1_sd_after,
-                             b1_quant_after[2], 
-                             b1_quant_after[1],
-                             b1_quant_after[3])
-b1_df <- bind_rows(b1_df_pre_cred, b1_df_after_cred)
 ```
@@
 
-b1_df %>% gt() %>%
-  tab_header(
-    title = "Effect of local OSB social monitoring on construction delivery rates",
-    subtitle = "Posterior probabilities") %>%
-  cols_label(
-    variables = "Variables",
-    post_mean = "Mean",
-    post_sd = "Sd",
-    Q50 = "Median",
-    Q2.5 = "2.5% CI",
-    Q97.5 = "97.5% CI"
-  ) %>%
-  fmt_number(
-    columns = c(post_mean, post_sd, Q50, Q2.5, Q97.5 ),
-    decimals = 3,
-    use_seps = FALSE
-  ) %>%
-  tab_source_note(
-    source_note = "452 observations for the pre-treatment period and 320 observations for the post-treatment period, resulting from the matching procedure, and encompassing municipalities in the same states as municipalities of Obra Transparente"
-  ) %>%
-  tab_options(., container.width = 500, container.height =     500)
+etable(did_model0, did_model2, did_model1, dict = c(concluida_num = "construction completed",
+                                                    indicator_muni_ot ="treatment",
+                                                    log_rpc = "log of per capita income",
+                                                    ext_pobres = "share of poor people",
+                                                    freq_escola_15_1 = "average school frequency",
+                                                    analfabetismo = "iliteracy rate",
+                                                    log_renda = "log of GDP",
+                                                    p10_ricos_desigualdade = "share of income of 10p richest",
+                                                    percentual_de_execucao = "construction execution percentual")) %>%
+  kable(aption = "DiD regression results")
 ```
@@
 
-The fact that an intervention like Tá de Pé [@freire_etal2020], which provided information to citizens about construction work, but did not produce a meaningful impact does not mean that bottom up accountability does not have any effect.
-The evidence we gathered here, assessed with multiple methods, clearly shows that costly and consistent oversight by civil society can produce results that are quite impactful, be it increased rate of project completion, improved quality of the construction works or decreasing in governmental spending.
+The fact that an intervention like Tá de Pé [@freire_etal2020], which provided information to citizens about construction work, did not produce a meaningful impact does not mean that bottom up accountability does not have any effect.
+The evidence we gathered here, assessed with multiple methods, clearly shows that costly and consistent oversight by civil society can produce results that are quite impactful, be it increased rate of project completion, improved quality of the construction works or reduction in governmental spending.
+
+The qualitative evidence gathered is important to elucidate the mechanism.
+It is important to contact local authorities multiple times.
+This way, it is harder for them no not listen to citizens.
+Another key aspect is to have a deep knowledge of the policy in question.
+In our case, we are talking about understanding a construction time table, knowing what the law and the contract mandates, be able to confidently estimate if the number of employees in a construction site will be enough to deliver at the due date and monitoring repeatedly over time to check if things are going well or not.
 
@@
 Accountability, as a fundamental element in democratic systems, plays a pivotal role in ensuring the efficient provision of public services.
-Recent studies have brought to light the concept of "bottom-up accountability," where citizens receive information about public policies and utilize it to exert social control.
-
-While tactical interventions aimed at providing information to citizens have shown limited impact, it would be a mistake to dismiss the potential of citizen voices in governance entirely.
+Recent studies that have investigated tactical interventions aimed at providing information to citizens have shown limited impact of such treatments.
+However,it would be a mistake to dismiss the potential of citizen voices in governance entirely.
 Our research has differentiated between information-led tactical interventions and active mobilization and monitoring by Civil Society Organizations (CSOs).
@@
 This paper provides evidence in support of this argument.
-By assessing the effectiveness of the "Obra Transparente" project developed by Transparência Brasil, we illustrate the significant role that organized CSOs can play in shaping government behavior and improving public service delivery.
+By assessing the effectiveness of the "Obra Transparente" project developed by Transparência Brasil in Brazil, we illustrate the significant role that an organized CSOs can play in shaping government behavior and improving public service delivery.
 Unlike interventions solely focused on providing information, this project aimed at creating a network of local CSOs, offering technical support, and providing training on monitoring public school and nursery construction projects.
@@
 These endeavors yield more substantial outcomes compared to interventions that merely deliver information and generate sporadic citizen actions.
-
-In a world where accountability mechanisms continue to evolve, the role of organized civil society remains paramount.
-The ability to foster collective action, create informed oversight, and influence policy change is an essential aspect of accountable and effective democratic governance.
-The journey toward enhancing bottom-up accountability is ongoing, and our research contributes to a more comprehensive understanding of how it can be achieved through the mobilization of organized civil society.
+our research contributes to a more comprehensive understanding of how bottom up accountability can be achieved through the mobilization of organized civil society.
 
